---
title: "Supplemental Figure S10 - Browsers: Loss of Bistability"
author: "Shayna A. Sura"
date: "07/13/2024 - July 13, 2024"
output: pdf_document
---

```{r setup, echo=FALSE}

library(deSolve)
library(reshape2)
library(viridis)
library(gridExtra)
library(purrr)
library(tidyverse) # includes and loads the packages listed below
# library(readr)
# library(tidyr)
# library(dplyr)
# library(ggplot2)
# library(lubridate)

library(here) # helps with paths for files

```


# Our Model Set up

```{r Phase 2 Model}


#These were the initial conditions for the van de Leemput et al. (2016) basic model.
# H0<-0.9
# C0<-0.75
# M0<-0.1


# Initial Conditions - for 'collapsed' model
G0<-0.45
R0<-0
B0<-0.45
C0<-0.75
T0<-0.05
M0<-0.05
S0 <- 1 - T0 - C0 - M0


P2_state_vars<-c(GG=G0, RR=R0, BB=B0, CC=C0, TT=T0, MM=M0, SS=S0)

#generate a series of times at which you want the ODE solver to output population sizes
P2_tseq<-seq(0,1000,by=0.1)

#Generate a vector of parameter values - for 'collapsed' model
P2_pars<-c(bc<-0.3,
           bt<-0.8,      #use the same value as bm from basic model
           bm<-0.8,      #use the same value as bm from basic model
           ic<-0.05,
           it<-0.025,    #need two of these, one for turf and one for macroalgae
           im<-0.025,    #need two of these, one for turf and one for macroalgae
           dc<-0.1,
           r<-1,
           # gt<-1,       #need two of these, one for turf and one for macroalgae
           # gm<-1,       #need two of these, one for turf and one for macroalgae
           gt<-2,       #need two of these, one for turf and one for macroalgae
           gm<-2,       #need two of these, one for turf and one for macroalgae
           etaT<-1,     #need two of these, one for turf and one for macroalgae
           etaM<-1,     #need two of these, one for turf and one for macroalgae
           alphaT<-0.5,
           alphaM<-0.5,
           sigma<-0.6,
           f<-0.1,
           gamma<-0)


# Our Model Setup - for 'collapsed' model
P2_Model<-function(P2_tseq,P2_state_vars,P2_pars){
  GG <- P2_state_vars[1]
  RR <- P2_state_vars[2]
  BB <- P2_state_vars[3]
  CC <- P2_state_vars[4]
  TT <- P2_state_vars[5]
  MM <- P2_state_vars[6]
  SS <- 1 - CC - TT - MM
  
  bc <- P2_pars[1]
  bt <- P2_pars[2]
  bm <- P2_pars[3]
  ic <- P2_pars[4]
  it <- P2_pars[5]
  im <- P2_pars[6]
  dc <- P2_pars[7]
  r <- P2_pars[8]
  gt <- P2_pars[9]
  gm <- P2_pars[10]
  etaT <- P2_pars[11]
  etaM <- P2_pars[12]
  alphaT <- P2_pars[13]
  alphaM <- P2_pars[14]
  sigma <- P2_pars[15]
  f <- P2_pars[16]
  gamma <- P2_pars[17]
  
  dG_dt <-r*GG*(1 - ((GG+RR+BB) / ((1-sigma) + sigma*CC))) - f*GG
  dR_dt <-r*RR*(1 - ((GG+RR+BB) / ((1-sigma) + sigma*CC))) - f*RR
  dB_dt <-r*BB*(1 - ((GG+RR+BB) / ((1-sigma) + sigma*CC))) - f*BB
  dC_dt <- (ic + bc*CC)*SS*(1-(alphaT*TT+alphaM*MM)) - dc*CC
  dT_dt <- (it + bt*TT)*(SS) - (gamma*TT) - (((gt*GG*TT) / (gt*etaT*TT+1)) + ((gt*RR*TT)/(gt*etaT*TT+gm*etaM*MM+1)))
  dM_dt <- (im + bm*MM)*(SS) + (gamma*TT) - (((gm*BB*MM) / (gm*etaM*MM+1)) + ((gm*RR*MM)/(gt*etaT*TT+gm*etaM*MM+1)))


  return(list(c(dG <- dG_dt,
                dR <- dR_dt,
                dB <- dB_dt,
                dC <- dC_dt,
                dT <- dT_dt,
                dM <- dM_dt)))
}

```


## hh_pars   Parameter values actually used for our expanded model

```{r, eval=FALSE, echo=FALSE}

#Generate a vector of parameter values - for our model
hh_pars<-c(bc<-0.3, bt<-0.8,bm<-0.5,      #expansion of current benthic cover
           ic<-0.05, it<-0.05, im<-0,     #import of propagules
           dc<-0.1,                       #coral mortality
           r<-1,                          #herbivore growth rate
           # gt<-1, gm<-0.5,                #algae mortality
           gt<-2, gm<-1,                #algae mortality
           etaT<-0, etaM<-1,              #algae handling time
           alphaT<-0.25, alphaM<-0.5,     #competitive effect on coral
           sigma<-0.6,                    #relationship between coral & herbivores
           f<-0.5,                        #fishing pressure
           gamma<-0.1)                    #transition from turf to macroalgae


```



### Bistability Analyses - Browser-Dominated Scenarios
Is there an initial abundance/condition for browsers that allows bistability to disappear completely?

```{r}

P2_tseq<-seq(0,1000,by=0.1)

## High Browsers - 0.7

f_values<-seq(0,1,by=0.01)
# coral_initials<-seq(0,1,0.01)
coral_initials<-seq(0,0.85,0.01)

high_browsers_2<-expand.grid(coral_initials,f_values)
colnames(high_browsers_2)<-c("Initial_Coral","Fishing_Pressure")


for(i in 1:length(high_browsers_2$Initial_Coral)){
    C0<-high_browsers_2$Initial_Coral[i]
    B0<-0.7
    R0<-0.10
    G0<-0.10
#    C0<-0.75
    S0<-0.15
    M0<-(1-C0-S0)/2
    T0<-(1-C0-S0)/2
    hh_pars[16]<-high_browsers_2$Fishing_Pressure[i]   #set the fishing pressure
    zz_output<-lsoda(c(Grazers =G0, Generalists =R0, Browsers =B0,
                   Coral = C0,Turf = T0,Macroalgae=M0),
                 P2_tseq, P2_Model, hh_pars)
    zz_output_new<-as.data.frame(zz_output)
    high_browsers_2$Final_Coral[i]<-tail(zz_output_new$Coral,1)
}




## High Browsers - 0.65

f_values<-seq(0,1,by=0.01)
# coral_initials<-seq(0,1,0.01)
coral_initials<-seq(0,0.85,0.01)

high_browsers_3<-expand.grid(coral_initials,f_values)
colnames(high_browsers_3)<-c("Initial_Coral","Fishing_Pressure")


for(i in 1:length(high_browsers_3$Initial_Coral)){
    C0<-high_browsers_3$Initial_Coral[i]
    B0<-0.65
    R0<-0.125
    G0<-0.125
#    C0<-0.75
    S0<-0.15
    M0<-(1-C0-S0)/2
    T0<-(1-C0-S0)/2
    hh_pars[16]<-high_browsers_3$Fishing_Pressure[i]   #set the fishing pressure
    zz_output<-lsoda(c(Grazers =G0, Generalists =R0, Browsers =B0,
                   Coral = C0,Turf = T0,Macroalgae=M0),
                 P2_tseq, P2_Model, hh_pars)
    zz_output_new<-as.data.frame(zz_output)
    high_browsers_3$Final_Coral[i]<-tail(zz_output_new$Coral,1)
}




## High Browsers - 0.66

f_values<-seq(0,1,by=0.01)
# coral_initials<-seq(0,1,0.01)
coral_initials<-seq(0,0.85,0.01)

high_browsers_4<-expand.grid(coral_initials,f_values)
colnames(high_browsers_4)<-c("Initial_Coral","Fishing_Pressure")


for(i in 1:length(high_browsers_4$Initial_Coral)){
    C0<-high_browsers_4$Initial_Coral[i]
    B0<-0.66
    R0<-0.12
    G0<-0.12
#    C0<-0.75
    S0<-0.15
    M0<-(1-C0-S0)/2
    T0<-(1-C0-S0)/2
    hh_pars[16]<-high_browsers_4$Fishing_Pressure[i]   #set the fishing pressure
    zz_output<-lsoda(c(Grazers =G0, Generalists =R0, Browsers =B0,
                   Coral = C0,Turf = T0,Macroalgae=M0),
                 P2_tseq, P2_Model, hh_pars)
    zz_output_new<-as.data.frame(zz_output)
    high_browsers_4$Final_Coral[i]<-tail(zz_output_new$Coral,1)
}





## High Browsers - 0.67

f_values<-seq(0,1,by=0.01)
# coral_initials<-seq(0,1,0.01)
coral_initials<-seq(0,0.85,0.01)

high_browsers_5<-expand.grid(coral_initials,f_values)
colnames(high_browsers_5)<-c("Initial_Coral","Fishing_Pressure")


for(i in 1:length(high_browsers_5$Initial_Coral)){
    C0<-high_browsers_5$Initial_Coral[i]
    B0<-0.67
    R0<-0.115
    G0<-0.115
#    C0<-0.75
    S0<-0.15
    M0<-(1-C0-S0)/2
    T0<-(1-C0-S0)/2
    hh_pars[16]<-high_browsers_5$Fishing_Pressure[i]   #set the fishing pressure
    zz_output<-lsoda(c(Grazers =G0, Generalists =R0, Browsers =B0,
                   Coral = C0,Turf = T0,Macroalgae=M0),
                 P2_tseq, P2_Model, hh_pars)
    zz_output_new<-as.data.frame(zz_output)
    high_browsers_5$Final_Coral[i]<-tail(zz_output_new$Coral,1)
}




## High Browsers - 0.68

f_values<-seq(0,1,by=0.01)
# coral_initials<-seq(0,1,0.01)
coral_initials<-seq(0,0.85,0.01)

high_browsers_6<-expand.grid(coral_initials,f_values)
colnames(high_browsers_6)<-c("Initial_Coral","Fishing_Pressure")


for(i in 1:length(high_browsers_6$Initial_Coral)){
    C0<-high_browsers_6$Initial_Coral[i]
    B0<-0.68
    R0<-0.11
    G0<-0.11
#    C0<-0.75
    S0<-0.15
    M0<-(1-C0-S0)/2
    T0<-(1-C0-S0)/2
    hh_pars[16]<-high_browsers_6$Fishing_Pressure[i]   #set the fishing pressure
    zz_output<-lsoda(c(Grazers =G0, Generalists =R0, Browsers =B0,
                   Coral = C0,Turf = T0,Macroalgae=M0),
                 P2_tseq, P2_Model, hh_pars)
    zz_output_new<-as.data.frame(zz_output)
    high_browsers_6$Final_Coral[i]<-tail(zz_output_new$Coral,1)
}



## High Browsers - 0.69

f_values<-seq(0,1,by=0.01)
# coral_initials<-seq(0,1,0.01)
coral_initials<-seq(0,0.85,0.01)

high_browsers_7<-expand.grid(coral_initials,f_values)
colnames(high_browsers_7)<-c("Initial_Coral","Fishing_Pressure")


for(i in 1:length(high_browsers_7$Initial_Coral)){
    C0<-high_browsers_7$Initial_Coral[i]
    B0<-0.69
    R0<-0.105
    G0<-0.105
#    C0<-0.75
    S0<-0.15
    M0<-(1-C0-S0)/2
    T0<-(1-C0-S0)/2
    hh_pars[16]<-high_browsers_7$Fishing_Pressure[i]   #set the fishing pressure
    zz_output<-lsoda(c(Grazers =G0, Generalists =R0, Browsers =B0,
                   Coral = C0,Turf = T0,Macroalgae=M0),
                 P2_tseq, P2_Model, hh_pars)
    zz_output_new<-as.data.frame(zz_output)
    high_browsers_7$Final_Coral[i]<-tail(zz_output_new$Coral,1)
}



## High Browsers - 0.75

f_values<-seq(0,1,by=0.01)
# coral_initials<-seq(0,1,0.01)
coral_initials<-seq(0,0.85,0.01)

high_browsers_8<-expand.grid(coral_initials,f_values)
colnames(high_browsers_8)<-c("Initial_Coral","Fishing_Pressure")


for(i in 1:length(high_browsers_8$Initial_Coral)){
    C0<-high_browsers_8$Initial_Coral[i]
    B0<-0.75
    R0<-0.075
    G0<-0.075
#    C0<-0.75
    S0<-0.15
    M0<-(1-C0-S0)/2
    T0<-(1-C0-S0)/2
    hh_pars[16]<-high_browsers_8$Fishing_Pressure[i]   #set the fishing pressure
    zz_output<-lsoda(c(Grazers =G0, Generalists =R0, Browsers =B0,
                   Coral = C0,Turf = T0,Macroalgae=M0),
                 P2_tseq, P2_Model, hh_pars)
    zz_output_new<-as.data.frame(zz_output)
    high_browsers_8$Final_Coral[i]<-tail(zz_output_new$Coral,1)
}


```

# Combine output together from various browser scenarios.
```{r}


high_browsers_3$Id<-"B0 = 0.65"
high_browsers_4$Id<-"B0 = 0.66"
high_browsers_5$Id<-"B0 = 0.67"
high_browsers_6$Id<-"B0 = 0.68"
high_browsers_7$Id<-"B0 = 0.69"
high_browsers_2$Id<-"B0 = 0.70"
high_browsers_8$Id<-"B0 = 0.75"

  
browser_bistability=rbind(high_browsers_3, high_browsers_4, high_browsers_5, high_browsers_6, high_browsers_7, high_browsers_2, high_browsers_8)
browser_bistability$Id <- factor(browser_bistability$Id, levels=c("B0 = 0.65","B0 = 0.66","B0 = 0.67","B0 = 0.68", "B0 = 0.69", "B0 = 0.70","B0 = 0.75"))


```



# export simulation results to .csv file
```{r}

write_csv(browser_bistability, file = "../../output/analyses/supplement/browser_bistability-all.csv")

```





### Read in .csv file containing results from model simulation (to avoid having to rerun the above analysis).
```{r}

browser_bistability_all <- read_csv(file = "../../output/analyses/supplement/browser_bistability-all.csv")

```



### Make figures of the results.

```{r}

## Figure with initial browsers at 0.7
# pdf("Browsers_Bistability_07.pdf",width=4,height=3)
pdf("Browsers_Bistability_07_v2.pdf",width=4,height=3)

#quartz()
ggplot(high_browsers_2, aes(Fishing_Pressure, Initial_Coral)) +
  geom_tile(aes(fill = Final_Coral)) +
  theme_classic(base_size=14,base_family = "Times") + 
  theme(axis.title=element_text(size=16,face="bold")) +
  labs(fill = "Final\nCoral\nCover") +
  scale_fill_viridis(option = "viridis",limits=c(0,0.8)) +
  scale_colour_viridis(option = "viridis",limits=c(0,0.8)) +
  scale_x_continuous("Fishing Pressure",expand = c(0, 0), breaks = c(0,0.25,0.5,0.75,1),
                         labels = c(0,0.25,0.5,0.75,1),limits = c(0,1)) +
  scale_y_continuous("Initial Coral Cover", expand = c(0, 0), breaks = c(0,0.2,0.4,0.6,0.8),
                         labels = c(0,0.2,0.4,0.6,0.8), limits = c(0,0.85))

dev.off()


## Figure with initial browsers at 0.65
# pdf("Browsers_Bistability_065.pdf",width=4,height=3)
pdf("Browsers_Bistability_065_v2.pdf",width=4,height=3)

#quartz()
ggplot(high_browsers_3, aes(Fishing_Pressure, Initial_Coral)) +
  geom_tile(aes(fill = Final_Coral)) +
  theme_classic(base_size=14,base_family = "Times") + 
  theme(axis.title=element_text(size=16,face="bold")) +
  labs(fill = "Final\nCoral\nCover") +
  scale_fill_viridis(option = "viridis",limits=c(0,0.8)) +
  scale_colour_viridis(option = "viridis",limits=c(0,0.8)) +
  scale_x_continuous("Fishing Pressure",expand = c(0, 0), breaks = c(0,0.25,0.5,0.75,1),
                         labels = c(0,0.25,0.5,0.75,1),limits = c(0,1)) +
  scale_y_continuous("Initial Coral Cover", expand = c(0, 0), breaks = c(0,0.2,0.4,0.6,0.8),
                         labels = c(0,0.2,0.4,0.6,0.8), limits = c(0,0.85))

dev.off()



## Figure with initial browsers at 0.66
# pdf("Browsers_Bistability_066.pdf",width=4,height=3)
pdf("Browsers_Bistability_066_v2.pdf",width=4,height=3)

#quartz()
ggplot(high_browsers_4, aes(Fishing_Pressure, Initial_Coral)) +
  geom_tile(aes(fill = Final_Coral)) +
  theme_classic(base_size=14,base_family = "Times") + 
  theme(axis.title=element_text(size=16,face="bold")) +
  labs(fill = "Final\nCoral\nCover") +
  scale_fill_viridis(option = "viridis",limits=c(0,0.8)) +
  scale_colour_viridis(option = "viridis",limits=c(0,0.8)) +
  scale_x_continuous("Fishing Pressure",expand = c(0, 0), breaks = c(0,0.25,0.5,0.75,1),
                         labels = c(0,0.25,0.5,0.75,1),limits = c(0,1)) +
  scale_y_continuous("Initial Coral Cover", expand = c(0, 0), breaks = c(0,0.2,0.4,0.6,0.8),
                         labels = c(0,0.2,0.4,0.6,0.8), limits = c(0,0.85))

dev.off()


## Figure with initial browsers at 0.67
# pdf("Browsers_Bistability_067.pdf",width=4,height=3)
pdf("Browsers_Bistability_067_v2.pdf",width=4,height=3)

#quartz()
ggplot(high_browsers_5, aes(Fishing_Pressure, Initial_Coral)) +
  geom_tile(aes(fill = Final_Coral)) +
  theme_classic(base_size=14,base_family = "Times") + 
  theme(axis.title=element_text(size=16,face="bold")) +
  labs(fill = "Final\nCoral\nCover") +
  scale_fill_viridis(option = "viridis",limits=c(0,0.8)) +
  scale_colour_viridis(option = "viridis",limits=c(0,0.8)) +
  scale_x_continuous("Fishing Pressure",expand = c(0, 0), breaks = c(0,0.25,0.5,0.75,1),
                         labels = c(0,0.25,0.5,0.75,1),limits = c(0,1)) +
  scale_y_continuous("Initial Coral Cover", expand = c(0, 0), breaks = c(0,0.2,0.4,0.6,0.8),
                         labels = c(0,0.2,0.4,0.6,0.8), limits = c(0,0.85))

dev.off()



## Figure with initial browsers at 0.68
# pdf("Browsers_Bistability_068.pdf",width=4,height=3)
pdf("Browsers_Bistability_068_v2.pdf",width=4,height=3)

#quartz()
ggplot(high_browsers_6, aes(Fishing_Pressure, Initial_Coral)) +
  geom_tile(aes(fill = Final_Coral)) +
  theme_classic(base_size=14,base_family = "Times") + 
  theme(axis.title=element_text(size=16,face="bold")) +
  labs(fill = "Final\nCoral\nCover") +
  scale_fill_viridis(option = "viridis",limits=c(0,0.8)) +
  scale_colour_viridis(option = "viridis",limits=c(0,0.8)) +
  scale_x_continuous("Fishing Pressure",expand = c(0, 0), breaks = c(0,0.25,0.5,0.75,1),
                         labels = c(0,0.25,0.5,0.75,1),limits = c(0,1)) +
  scale_y_continuous("Initial Coral Cover", expand = c(0, 0), breaks = c(0,0.2,0.4,0.6,0.8),
                         labels = c(0,0.2,0.4,0.6,0.8), limits = c(0,0.85))

dev.off()



## Figure with initial browsers at 0.69
# pdf("Browsers_Bistability_069.pdf",width=4,height=3)
pdf("Browsers_Bistability_069_v2.pdf",width=4,height=3)

#quartz()
ggplot(high_browsers_7, aes(Fishing_Pressure, Initial_Coral)) +
  geom_tile(aes(fill = Final_Coral)) +
  theme_classic(base_size=14,base_family = "Times") + 
  theme(axis.title=element_text(size=16,face="bold")) +
  labs(fill = "Final\nCoral\nCover") +
  scale_fill_viridis(option = "viridis",limits=c(0,0.8)) +
  scale_colour_viridis(option = "viridis",limits=c(0,0.8)) +
  scale_x_continuous("Fishing Pressure",expand = c(0, 0), breaks = c(0,0.25,0.5,0.75,1),
                         labels = c(0,0.25,0.5,0.75,1),limits = c(0,1)) +
  scale_y_continuous("Initial Coral Cover", expand = c(0, 0), breaks = c(0,0.2,0.4,0.6,0.8),
                         labels = c(0,0.2,0.4,0.6,0.8), limits = c(0,0.85))

dev.off()


## Figure with initial browsers at 0.75
# pdf("Browsers_Bistability_075.pdf",width=4,height=3)
pdf("Browsers_Bistability_075_v2.pdf",width=4,height=3)

#quartz()
ggplot(high_browsers_8, aes(Fishing_Pressure, Initial_Coral)) +
  geom_tile(aes(fill = Final_Coral)) +
  theme_classic(base_size=14,base_family = "Times") + 
  theme(axis.title=element_text(size=16,face="bold")) +
  labs(fill = "Final\nCoral\nCover") +
  scale_fill_viridis(option = "viridis",limits=c(0,0.8)) +
  scale_colour_viridis(option = "viridis",limits=c(0,0.8)) +
  scale_x_continuous("Fishing Pressure",expand = c(0, 0), breaks = c(0,0.25,0.5,0.75,1),
                         labels = c(0,0.25,0.5,0.75,1),limits = c(0,1)) +
  scale_y_continuous("Initial Coral Cover", expand = c(0, 0), breaks = c(0,0.2,0.4,0.6,0.8),
                         labels = c(0,0.2,0.4,0.6,0.8), limits = c(0,0.85))

dev.off()

```




## Plotting all the browser scenarios together!
```{r}

# 
# high_browsers_3$Id<-"B0 = 0.65"
# high_browsers_4$Id<-"B0 = 0.66"
# high_browsers_5$Id<-"B0 = 0.67"
# high_browsers_6$Id<-"B0 = 0.68"
# high_browsers_7$Id<-"B0 = 0.69"
# high_browsers_2$Id<-"B0 = 0.70"
# high_browsers_8$Id<-"B0 = 0.75"
# 
#   
# browser_bistability=rbind(high_browsers_3, high_browsers_4, high_browsers_5, high_browsers_6, high_browsers_7, high_browsers_2, high_browsers_8)
# browser_bistability$Id <- factor(browser_bistability$Id, levels=c("B0 = 0.65","B0 = 0.66","B0 = 0.67","B0 = 0.68", "B0 = 0.69", "B0 = 0.70","B0 = 0.75"))


# pdf("Browsers_Bistability_All.pdf",width=5,height=9)
pdf("Browsers_Bistability_All_v2.pdf",width=5,height=9)

#quartz()
ggplot(browser_bistability, aes(Fishing_Pressure, Initial_Coral)) +
  geom_tile(aes(fill = Final_Coral)) +
  theme_classic(base_size=14,base_family = "Times") + 
  theme(axis.title=element_text(size=16,face="bold")) +
  labs(fill = "Final\nCoral\nCover") +
  scale_fill_viridis(option = "viridis",limits=c(0,0.8)) +
  scale_colour_viridis(option = "viridis",limits=c(0,0.8)) +
  scale_x_continuous("Fishing Pressure",expand = c(0, 0), breaks = c(0,0.25,0.5,0.75,1),
                         labels = c(0,0.25,0.5,0.75,1),limits = c(0,1)) +
  scale_y_continuous("Initial Coral Cover", expand = c(0, 0), breaks = c(0,0.2,0.4,0.6,0.8),
                         labels = c(0,0.2,0.4,0.6,0.8), limits = c(0,0.85)) +
  facet_wrap(~Id,nrow = 4, ncol = 2) +
  theme(strip.text.x = element_text(size = 11))

dev.off()


```








