---
title: "01_Fig1_figS4"
author: "Shayna A. Sura"
date: "2024-07-16"
output: pdf_document
---


```{r setup, include=FALSE}

library(deSolve)
library(reshape2)
library(viridis)
library(viridisLite)
library(gridExtra)
library(tidyverse) # includes and loads the packages listed below
# library(readr)
# library(tidyr)
# library(dplyr)
# library(ggplot2)
# library(lubridate)

library(here) # helps with paths for files
library(purrr) # vectorized coding approaches for faster analyses
library(scales)
library(ggtext)
library(lemon)
library(cowplot)
library(grid)

```



```{r source model code and parameters}

source("0.1_basic_model.R")
source("0.2_full_model.R")

```


# Our Full Model
## Initial Conditions & Parameters
```{r}

# Initial Conditions for our full/expanded model:
G0<-0.3
R0<-0.3
B0<-0.3
C0<-0.75
T0<-0.1
M0<-0.0
S0 <- 1 - T0 - C0 - M0


# # Reminder of parameter values (hh_pars) used for our full/expanded model:
# hh_pars<-c(bc<-0.3, bt<-0.8,bm<-0.5,      #expansion of current benthic cover
#            ic<-0.05, it<-0.05, im<-0,     #import of propagules
#            dc<-0.1,                       #coral mortality
#            r<-1,                          #herbivore growth rate
#            gt<-2, gm<-1,                #algae mortality
#            etaT<-0, etaM<-1,              #algae handling time
#            alphaT<-0.25, alphaM<-0.5,     #competitive effect on coral
#            sigma<-0.6,                    #relationship between coral & herbivores
#            f<-0.5,                        #fishing pressure
#            gamma<-0.1)                    #transition from turf to macroalgae

```


# Model Simulations - varying Fishing Pressure scenarios
```{r}

#set fishing pressure to 0.1 for initial run
hh_pars[16] = 0.1
Exp_output<-lsoda(c(Grazers =G0, Generalists =R0, Browsers =B0,
                   Coral = C0,Turf = T0,Macroalgae=M0),
                 P2_tseq, P2_Model, hh_pars)
Exp_output=as.data.frame(Exp_output)
Exp_output$Space= 1 - Exp_output$Coral - Exp_output$Turf - Exp_output$Macroalgae
Exp_output$Herbivores = Exp_output$Grazers+Exp_output$Generalists+Exp_output$Browsers
Exp_output$Algae = Exp_output$Turf+Exp_output$Macroalgae


## set a higher fishing pressure f = 0.5
hh_pars[16]=0.5
Exp_output_2<-lsoda(c(Grazers =G0, Generalists =R0, Browsers =B0,
                   Coral = C0,Turf = T0,Macroalgae=M0),
                 P2_tseq, P2_Model, hh_pars)
Exp_output_2=as.data.frame(Exp_output_2)
Exp_output_2$Space= 1 - Exp_output_2$Coral - Exp_output_2$Turf - Exp_output_2$Macroalgae
Exp_output_2$Herbivores = Exp_output_2$Grazers+Exp_output_2$Generalists+Exp_output_2$Browsers
Exp_output_2$Algae = Exp_output_2$Turf+Exp_output_2$Macroalgae


## set an even higher fishing pressure f = 0.9
hh_pars[16]=0.9
Exp_output_3<-lsoda(c(Grazers =G0, Generalists =R0, Browsers =B0,
                   Coral = C0,Turf = T0,Macroalgae=M0),
                 P2_tseq, P2_Model, hh_pars)
Exp_output_3=as.data.frame(Exp_output_3)
Exp_output_3$Space= 1 - Exp_output_3$Coral - Exp_output_3$Turf - Exp_output_3$Macroalgae
Exp_output_3$Herbivores = Exp_output_3$Grazers+Exp_output_3$Generalists+Exp_output_3$Browsers
Exp_output_3$Algae = Exp_output_3$Turf+Exp_output_3$Macroalgae

```


# Model Simulations - varying Herbivore Dominance scenarios

```{r}

# Scenario 1: Generalist-Dominated Community (coral remains high)
#herbivore initial abundances
G0<-0.15
R0<-0.6
B0<-0.15

#set fishing pressure to 0.5
hh_pars[16] = 0.5

# run model simulations
sc_1<-lsoda(c(Grazers =G0, Generalists =R0, Browsers =B0,
                   Coral = C0, Turf = T0, Macroalgae=M0),
                   P2_tseq, P2_Model, hh_pars)
sc_1=as.data.frame(sc_1)
sc_1$Space= 1 - sc_1$Coral - sc_1$Turf - sc_1$Macroalgae
sc_1$Herbivores = sc_1$Grazers+sc_1$Generalists+sc_1$Browsers
sc_1$Algae = sc_1$Turf+sc_1$Macroalgae



# Scenario 2: Grazer-Dominated Community (macroalgal cover becomes high)
#herbivore initial abundances
G0<-0.6
R0<-0.15
B0<-0.15

#set fishing pressure to 0.5
hh_pars[16] = 0.5

# run model simulations
sc_2<-lsoda(c(Grazers =G0, Generalists =R0, Browsers =B0,
                   Coral = C0, Turf = T0, Macroalgae=M0),
                   P2_tseq, P2_Model, hh_pars)
sc_2=as.data.frame(sc_2)
sc_2$Space= 1 - sc_2$Coral - sc_2$Turf - sc_2$Macroalgae
sc_2$Herbivores = sc_2$Grazers+sc_2$Generalists+sc_2$Browsers
sc_2$Algae = sc_2$Turf+sc_2$Macroalgae



# Scenario 3: Browser-Dominated Community (turf ends up higher than macroalgae, but coral still dominant)
#herbivore initial abundances
G0<-0.15
R0<-0.15
B0<-0.6

#set fishing pressure to 0.5
hh_pars[16] = 0.5

# run model simulations
sc_3<-lsoda(c(Grazers =G0, Generalists =R0, Browsers =B0,
                   Coral = C0, Turf = T0, Macroalgae=M0),
                   P2_tseq, P2_Model, hh_pars)
sc_3=as.data.frame(sc_3)
sc_3$Space= 1 - sc_3$Coral - sc_3$Turf - sc_3$Macroalgae
sc_3$Herbivores = sc_3$Grazers+sc_3$Generalists+sc_3$Browsers
sc_3$Algae = sc_3$Turf+sc_3$Macroalgae


```




# PLOTTING FIGURES
## Fishing Pressure Scenarios - appropriate time steps for an appealing visualization
## identify groups of variables to plot at different time point intervals - to prevent direct overlap of multiple variables
```{r}

# Group 1 - Coral
# group1_times<-c(0, seq(0,1000, by=10)) # for out to 400 yrs
group1_times<-c(0, seq(1,1000, by=5)) # for out to 200 yrs
group1_1<-subset(Exp_output,Exp_output$time %in% group1_times)
group1_2<-subset(Exp_output_2,Exp_output$time %in% group1_times)
group1_3<-subset(Exp_output_3,Exp_output$time %in% group1_times)


# Group 2 - Algae, Turf
# group2_times<-c(0, seq(7,1000,by=10)) # for out to 400 yrs
group2_times<-c(0, seq(1,1000, by=5)) # for out to 200 yrs
group2_1<-subset(Exp_output,Exp_output$time %in% group2_times)
group2_2<-subset(Exp_output_2,Exp_output$time %in% group2_times)
group2_3<-subset(Exp_output_3,Exp_output$time %in% group2_times)


# Group 3 - Macroalgae
# group3_times<-c(0, seq(3,1000,by=10)) # for out to 400 yrs
group3_times<-c(0, seq(3,1000, by=5)) # for out to 200 yrs
group3_1<-subset(Exp_output,Exp_output$time %in% group3_times)
group3_2<-subset(Exp_output_2,Exp_output$time %in% group3_times)
group3_3<-subset(Exp_output_3,Exp_output$time %in% group3_times)


#Different times for the 3 different types of herbivores

# Group 4 - Generalists
# group4_times<-c(0, seq(0,1000,by=22)) # for out to 400 yrs
group4_times<-c(0, seq(0,1000, by=11)) # for out to 200 yrs
group4_1<-subset(Exp_output,Exp_output$time %in% group4_times)
group4_2<-subset(Exp_output_2,Exp_output$time %in% group4_times)
group4_3<-subset(Exp_output_3,Exp_output$time %in% group4_times)

# Group 5 - Browsers
# group5_times<-c(0, seq(7,1000,by=22)) # for out to 400 yrs
group5_times<-c(0, seq(4,1000, by=11)) # for out to 200 yrs
group5_1<-subset(Exp_output,Exp_output$time %in% group5_times)
group5_2<-subset(Exp_output_2,Exp_output$time %in% group5_times)
group5_3<-subset(Exp_output_3,Exp_output$time %in% group5_times)

# Group 6 - Grazers
# group6_times<-c(0, seq(14,1000,by=22)) # for out to 400 yrs
group6_times<-c(0, seq(8,1000, by=11)) # for out to 200 yrs
group6_1<-subset(Exp_output,Exp_output$time %in% group6_times)
group6_2<-subset(Exp_output_2,Exp_output$time %in% group6_times)
group6_3<-subset(Exp_output_3,Exp_output$time %in% group6_times)


## List of times from above for easier referencing and copying...
# group1_times<-c(0, seq(1,1000, by=5))      # Coral
# group2_times<-c(0, seq(1,1000, by=5))       # Algae, Turf
# group3_times<-c(0, seq(3,1000, by=5))       # Macroalgae
# group4_times<-c(0, seq(0,1000, by=11))       # Generalists
# group5_times<-c(0, seq(4,1000, by=11))       # Browsers
# group6_times<-c(0, seq(8,1000, by=11))      # Grazers


```




## Herbivore Community Scenarios - appropriate time steps for an appealing visualization
## identify groups of variables to plot at different time point intervals - to prevent direct overlap of multiple variables
```{r}

# group1_times<-seq(0,1000,by=10)
# group2_times<-seq(7,1000,by=10)
# group3_times<-seq(3,1000,by=10)
# group4_times<-seq(0,1000,by=22)
# group5_times<-seq(7,1000,by=22)
# group6_times<-seq(14,1000,by=22)

## List of times to subset to match above scenarios.
group1_times<-c(0, seq(1,1000, by=5))        # Coral
group2_times<-c(0, seq(1,1000, by=5))        # Algae, Turf
group3_times<-c(0, seq(3,1000, by=5))        # Macroalgae
group4_times<-c(0, seq(0,1000, by=11))       # Generalists
group5_times<-c(0, seq(4,1000, by=11))       # Browsers
group6_times<-c(0, seq(8,1000, by=11))       # Grazers


#Panel A response variables
panelA_1<-subset(sc_1,sc_1$time %in% group1_times) #coral, algae
panelA_2<-subset(sc_1,sc_1$time %in% group2_times) #herbivores, turf
panelA_3<-subset(sc_1,sc_1$time %in% group3_times) #macroalgae
panelA_4<-subset(sc_1,sc_1$time %in% group4_times) #generalists
panelA_5<-subset(sc_1,sc_1$time %in% group5_times) #browsers
panelA_6<-subset(sc_1,sc_1$time %in% group6_times) #grazers


#Panel B response variables
panelB_1<-subset(sc_2,sc_2$time %in% group1_times) #coral, algae
panelB_2<-subset(sc_2,sc_2$time %in% group2_times) #herbivores, turf
panelB_3<-subset(sc_2,sc_2$time %in% group3_times) #macroalgae
panelB_4<-subset(sc_2,sc_2$time %in% group4_times) #generalists
panelB_5<-subset(sc_2,sc_2$time %in% group5_times) #browsers
panelB_6<-subset(sc_2,sc_2$time %in% group6_times) #grazers


#Panel C response variables
panelC_1<-subset(sc_3,sc_3$time %in% group1_times) #coral, algae
panelC_2<-subset(sc_3,sc_3$time %in% group2_times) #herbivores, turf
panelC_3<-subset(sc_3,sc_3$time %in% group3_times) #macroalgae
panelC_4<-subset(sc_3,sc_3$time %in% group4_times) #generalists
panelC_5<-subset(sc_3,sc_3$time %in% group5_times) #browsers
panelC_6<-subset(sc_3,sc_3$time %in% group6_times) #grazers

```




```{r color hexcodes}

# Grazer: DCE6F2
# Generalist: 95B3D7
# Browser: 376092
# Herbivores: 4A7EFF
# Coral: B5179E
# Turf: CA6030
# Macroalgae: 3C5941
# Algae: 9BBB59

```



# Figure 1C & 1D
```{r}

pdf("../../output/figures/Fig_1C_1D.pdf", width=7.5, height=7)

par(mfrow=c(3,2),
      mar=c(4,5,2.5,2),
      family = "Times")


# first panel: fishing pressure = 0.1
plot(group2_1$time, group2_1$Herbivores,
     type = "l",
     lwd = 4,
     col = "#4A7EFF",
     xlab="Time",
     ylab="Cover / Abundance",
     ylim=c(0,1),
     xlim=c(0,200),
     cex.lab=1.5,
     cex.axis=1.3,
     main = "Fishing Pressure = 0.1",
     cex.main=1.6)
lines(group2_1$time, group2_1$Algae, col="#9BBB59", lty = 1, lwd = 6)
lines(group1_1$time, group1_1$Coral, col="#B5179E", lty = 1, lwd = 4)
points(group4_1$time, group4_1$Generalists, col="#4A7EFF", bg="#95B3D7", pch=21, lwd = 1, cex=1.1)
points(group5_1$time, group5_1$Browsers, col="#4A7EFF", bg="#376092", pch=21, lwd = 1, cex=1.1)
points(group6_1$time, group6_1$Grazers, col="#4A7EFF", bg="#DCE6F2", pch=21, lwd = 1, cex=1.1)
points(group2_1$time, group2_1$Turf, col="#CA6030", bg="#CA6030", pch=24, lwd = 1, cex=0.9)
points(group3_1$time, group3_1$Macroalgae, col="#3C5941", bg="#3C5941", pch=25, lwd = 1, cex=0.9)
legend(x=35, y=1.06,
       # c("Herbivores","Algae","Coral", "Generalists","Browsers","Grazers","Turf","Macroalgae"),
       c("Herbivores","Algae","Coral","Grazers","Generalists","Browsers","Turf","Macroalgae"),
       pch=c(NA, NA, NA, 21, 21, 21, 24, 25),
       lty = c(1,1,1,0,0,0,0,0),
       lwd = c(2,2,2,1,1,1,1,1),
       col=c("#4A7EFF","#9BBB59","#B5179E","#4A7EFF","#4A7EFF","#4A7EFF","#CA6030","#3C5941"),
       pt.bg=c("#4A7EFF","#9BBB59","#B5179E","#DCE6F2","#95B3D7","#376092","#CA6030","#3C5941"),
       ncol=3,
       cex=0.85,
       bty = "n",   ## remove box around legend
       pt.cex = c(1,1,1,1.2,1.2,1.2,1.2,1.2))


# third panel: fishing pressure = 0.9
plot(group2_3$time, group2_3$Herbivores,
     type = "l",
     lwd = 4,
     col = "#4A7EFF",
     xlab="Time",
     ylab="Cover / Abundance",
     ylim=c(0,1),
     xlim=c(0,200),
     cex.lab=1.5,
     cex.axis=1.3,
     main = "Fishing Pressure = 0.9",
     cex.main=1.6)
lines(group2_3$time, group2_3$Algae, col="#9BBB59", lty = 1, lwd = 6)
lines(group1_3$time, group1_3$Coral, col="#B5179E", lty = 1, lwd = 4)
points(group4_3$time, group4_3$Generalists, col="#4A7EFF", bg="#95B3D7", pch=21, lwd = 1, cex=1.1)
points(group5_3$time, group5_3$Browsers, col="#4A7EFF", bg="#376092", pch=21, lwd = 1, cex=1.1)
points(group6_3$time, group6_3$Grazers, col="#4A7EFF", bg="#DCE6F2", pch=21, lwd = 1, cex=1.1)
points(group2_3$time, group2_3$Turf, col="#CA6030", bg="#CA6030", pch=24, lwd = 1, cex=0.9)
points(group3_3$time, group3_3$Macroalgae, col="#3C5941", bg="#3C5941", pch=25, lwd = 1, cex=0.9)


# first panel: generalist-dominated community
plot(panelA_2$time, panelA_2$Herbivores,
     type = "l",
     lwd = 4,
     col = "#4A7EFF",
     xlab="Time",
     ylab="Cover / Abundance",
     ylim=c(0,1),
     xlim=c(0,200),
     cex.lab=1.5,
     cex.axis=1.3,
     main = "Generalist-dominated community",
     cex.main=1.6)
lines(panelA_1$time, panelA_1$Algae, col="#9BBB59", lty = 1, lwd = 6)
lines(panelA_1$time, panelA_1$Coral, col="#B5179E", lty = 1, lwd = 4)
points(panelA_4$time, panelA_4$Generalists, col="#4A7EFF", bg="#95B3D7", pch=21, lwd = 1, cex=1.1)
points(panelA_5$time, panelA_5$Browsers, col="#4A7EFF", bg="#376092", pch=21, lwd = 1, cex=1.1)
points(panelA_6$time, panelA_6$Grazers, col="#4A7EFF", bg="#DCE6F2", pch=21, lwd = 1, cex=1.1)
points(panelA_2$time, panelA_2$Turf, col="#CA6030", bg="#CA6030", pch=24, lwd = 1, cex=0.9)
points(panelA_3$time, panelA_3$Macroalgae, col="#3C5941", bg="#3C5941", pch=25, lwd = 1, cex=0.9)
legend(x=35, y=1.06,
       # c("Herbivores","Algae","Coral", "Generalists","Browsers","Grazers","Turf","Macroalgae"),
       c("Herbivores","Algae","Coral","Grazers","Generalists","Browsers","Turf","Macroalgae"),
       pch=c(NA, NA, NA, 21, 21, 21, 24, 25),
       lty = c(1,1,1,0,0,0,0,0),
       lwd = c(2,2,2,1,1,1,1,1),
       col=c("#4A7EFF","#9BBB59","#B5179E","#4A7EFF","#4A7EFF","#4A7EFF","#CA6030","#3C5941"),
       pt.bg=c("#4A7EFF","#9BBB59","#B5179E","#DCE6F2","#95B3D7","#376092","#CA6030","#3C5941"),
       ncol=3,
       cex=0.85,
       bty = "n",   ## remove box around legend
       pt.cex = c(1,1,1,1.2,1.2,1.2,1.2,1.2))



# second panel: grazer-dominated community
plot(panelB_2$time, panelB_2$Herbivores,
     type = "l",
     lwd = 4,
     col = "#4A7EFF",
     xlab="Time",
     ylab="Cover / Abundance",
     ylim=c(0,1),
     xlim=c(0,200),
     cex.lab=1.5,
     cex.axis=1.3,
     main = "Grazer-dominated community",
     cex.main=1.6)
lines(panelB_1$time, panelB_1$Algae, col="#9BBB59", lty = 1, lwd = 6)
lines(panelB_1$time, panelB_1$Coral, col="#B5179E", lty = 1, lwd = 4)
points(panelB_4$time, panelB_4$Generalists, col="#4A7EFF", bg="#95B3D7", pch=21, lwd = 1, cex=1.1)
points(panelB_5$time, panelB_5$Browsers, col="#4A7EFF", bg="#376092", pch=21, lwd = 1, cex=1.1)
points(panelB_6$time, panelB_6$Grazers, col="#4A7EFF", bg="#DCE6F2", pch=21, lwd = 1, cex=1.1)
points(panelB_2$time, panelB_2$Turf, col="#CA6030", bg="#CA6030", pch=24, lwd = 1, cex=0.9)
points(panelB_3$time, panelB_3$Macroalgae, col="#3C5941", bg="#3C5941", pch=25, lwd = 1, cex=0.9)

# have it plot two empty plots to maintain the same sizing as Figure S4 - otherwise weird scaling things happens with the labels, lines, points, etc.
plot.new()
plot.new()

dev.off()


```




# Figure S4 Plot
```{r}

# Save as PDF file
pdf("../../output/figures/fig_S4.pdf", width=7.5, height=7)

par(mfcol=c(3,2),
      mar=c(4,5,2.5,2),
      family = "Times")
  
# first panel
plot(group2_1$time, group2_1$Herbivores,
     type = "l",
     lwd = 4,
     col = "#4A7EFF",
     xlab="Time",
     ylab="Cover / Abundance",
     ylim=c(0,1),
     xlim=c(0,200),
     cex.lab=1.5,
     cex.axis=1.3,
     main = "Fishing Pressure = 0.1",
     cex.main=1.6)
lines(group2_1$time, group2_1$Algae, col="#9BBB59", lty = 1, lwd = 6)
lines(group1_1$time, group1_1$Coral, col="#B5179E", lty = 1, lwd = 4)
points(group4_1$time, group4_1$Generalists, col="#4A7EFF", bg="#95B3D7", pch=21, lwd = 1, cex=1.1)
points(group5_1$time, group5_1$Browsers, col="#4A7EFF", bg="#376092", pch=21, lwd = 1, cex=1.1)
points(group6_1$time, group6_1$Grazers, col="#4A7EFF", bg="#DCE6F2", pch=21, lwd = 1, cex=1.1)
points(group2_1$time, group2_1$Turf, col="#CA6030", bg="#CA6030", pch=24, lwd = 1, cex=0.9)
points(group3_1$time, group3_1$Macroalgae, col="#3C5941", bg="#3C5941", pch=25, lwd = 1, cex=0.9)
legend(x=35, y=1.06,
       # c("Herbivores","Algae","Coral", "Generalists","Browsers","Grazers","Turf","Macroalgae"),
       c("Herbivores","Algae","Coral","Grazers","Generalists","Browsers","Turf","Macroalgae"),
       pch=c(NA, NA, NA, 21, 21, 21, 24, 25),
       lty = c(1,1,1,0,0,0,0,0),
       lwd = c(2,2,2,1,1,1,1,1),
       col=c("#4A7EFF","#9BBB59","#B5179E","#4A7EFF","#4A7EFF","#4A7EFF","#CA6030","#3C5941"),
       pt.bg=c("#4A7EFF","#9BBB59","#B5179E","#DCE6F2","#95B3D7","#376092","#CA6030","#3C5941"),
       ncol=3,
       cex=0.85,
       bty = "n",   ## remove box around legend
       pt.cex = c(1,1,1,1.2,1.2,1.2,1.2,1.2))



# second panel
plot(group2_2$time, group2_2$Herbivores,
     type = "l",
     lwd = 4,
     col = "#4A7EFF",
     xlab="Time",
     ylab="Cover / Abundance",
     ylim=c(0,1),
     xlim=c(0,200),
     cex.lab=1.5,
     cex.axis=1.3,
     main = "Fishing Pressure = 0.5",
     cex.main=1.6)
lines(group2_2$time, group2_2$Algae, col="#9BBB59", lty = 1, lwd = 6)
lines(group1_2$time, group1_2$Coral, col="#B5179E", lty = 1, lwd = 4)
points(group4_2$time, group4_2$Generalists, col="#4A7EFF", bg="#95B3D7", pch=21, lwd = 1, cex=1.1)
points(group5_2$time, group5_2$Browsers, col="#4A7EFF", bg="#376092", pch=21, lwd = 1, cex=1.1)
points(group6_2$time, group6_2$Grazers, col="#4A7EFF", bg="#DCE6F2", pch=21, lwd = 1, cex=1.1)
points(group2_2$time, group2_2$Turf, col="#CA6030", bg="#CA6030", pch=24, lwd = 1, cex=0.9)
points(group3_2$time, group3_2$Macroalgae, col="#3C5941", bg="#3C5941", pch=25, lwd = 1, cex=0.9)


# third panel
plot(group2_3$time, group2_3$Herbivores,
     type = "l",
     lwd = 4,
     col = "#4A7EFF",
     xlab="Time",
     ylab="Cover / Abundance",
     ylim=c(0,1),
     xlim=c(0,200),
     cex.lab=1.5,
     cex.axis=1.3,
     main = "Fishing Pressure = 0.9",
     cex.main=1.6)
lines(group2_3$time, group2_3$Algae, col="#9BBB59", lty = 1, lwd = 6)
lines(group1_3$time, group1_3$Coral, col="#B5179E", lty = 1, lwd = 4)
points(group4_3$time, group4_3$Generalists, col="#4A7EFF", bg="#95B3D7", pch=21, lwd = 1, cex=1.1)
points(group5_3$time, group5_3$Browsers, col="#4A7EFF", bg="#376092", pch=21, lwd = 1, cex=1.1)
points(group6_3$time, group6_3$Grazers, col="#4A7EFF", bg="#DCE6F2", pch=21, lwd = 1, cex=1.1)
points(group2_3$time, group2_3$Turf, col="#CA6030", bg="#CA6030", pch=24, lwd = 1, cex=0.9)
points(group3_3$time, group3_3$Macroalgae, col="#3C5941", bg="#3C5941", pch=25, lwd = 1, cex=0.9)



# first panel: generalist-dominated community
plot(panelA_2$time, panelA_2$Herbivores,
     type = "l",
     lwd = 4,
     col = "#4A7EFF",
     xlab="Time",
     ylab="Cover / Abundance",
     ylim=c(0,1),
     xlim=c(0,200),
     cex.lab=1.5,
     cex.axis=1.3,
     main = "Generalist-dominated community",
     cex.main=1.6)
lines(panelA_1$time, panelA_1$Algae, col="#9BBB59", lty = 1, lwd = 6)
lines(panelA_1$time, panelA_1$Coral, col="#B5179E", lty = 1, lwd = 4)
points(panelA_4$time, panelA_4$Generalists, col="#4A7EFF", bg="#95B3D7", pch=21, lwd = 1, cex=1.1)
points(panelA_5$time, panelA_5$Browsers, col="#4A7EFF", bg="#376092", pch=21, lwd = 1, cex=1.1)
points(panelA_6$time, panelA_6$Grazers, col="#4A7EFF", bg="#DCE6F2", pch=21, lwd = 1, cex=1.1)
points(panelA_2$time, panelA_2$Turf, col="#CA6030", bg="#CA6030", pch=24, lwd = 1, cex=0.9)
points(panelA_3$time, panelA_3$Macroalgae, col="#3C5941", bg="#3C5941", pch=25, lwd = 1, cex=0.9)
legend(x=35, y=1.06,
       # c("Herbivores","Algae","Coral", "Generalists","Browsers","Grazers","Turf","Macroalgae"),
       c("Herbivores","Algae","Coral","Grazers","Generalists","Browsers","Turf","Macroalgae"),
       pch=c(NA, NA, NA, 21, 21, 21, 24, 25),
       lty = c(1,1,1,0,0,0,0,0),
       lwd = c(2,2,2,1,1,1,1,1),
       col=c("#4A7EFF","#9BBB59","#B5179E","#4A7EFF","#4A7EFF","#4A7EFF","#CA6030","#3C5941"),
       pt.bg=c("#4A7EFF","#9BBB59","#B5179E","#DCE6F2","#95B3D7","#376092","#CA6030","#3C5941"),
       ncol=3,
       cex=0.85,
       bty = "n",   ## remove box around legend
       pt.cex = c(1,1,1,1.2,1.2,1.2,1.2,1.2))



# second panel: grazer-dominated community
plot(panelB_2$time, panelB_2$Herbivores,
     type = "l",
     lwd = 4,
     col = "#4A7EFF",
     xlab="Time",
     ylab="Cover / Abundance",
     ylim=c(0,1),
     xlim=c(0,200),
     cex.lab=1.5,
     cex.axis=1.3,
     main = "Grazer-dominated community",
     cex.main=1.6)
lines(panelB_1$time, panelB_1$Algae, col="#9BBB59", lty = 1, lwd = 6)
lines(panelB_1$time, panelB_1$Coral, col="#B5179E", lty = 1, lwd = 4)
points(panelB_4$time, panelB_4$Generalists, col="#4A7EFF", bg="#95B3D7", pch=21, lwd = 1, cex=1.1)
points(panelB_5$time, panelB_5$Browsers, col="#4A7EFF", bg="#376092", pch=21, lwd = 1, cex=1.1)
points(panelB_6$time, panelB_6$Grazers, col="#4A7EFF", bg="#DCE6F2", pch=21, lwd = 1, cex=1.1)
points(panelB_2$time, panelB_2$Turf, col="#CA6030", bg="#CA6030", pch=24, lwd = 1, cex=0.9)
points(panelB_3$time, panelB_3$Macroalgae, col="#3C5941", bg="#3C5941", pch=25, lwd = 1, cex=0.9)



# third panel: browser-dominated community
plot(panelC_2$time, panelC_2$Herbivores,
     type = "l",
     lwd = 4,
     col = "#4A7EFF",
     xlab="Time",
     ylab="Cover / Abundance",
     ylim=c(0,1),
     xlim=c(0,200),
     cex.lab=1.5,
     cex.axis=1.3,
     main = "Browser-dominated community",
     cex.main=1.6)
lines(panelC_1$time, panelC_1$Algae, col="#9BBB59", lty = 1, lwd = 6)
lines(panelC_1$time, panelC_1$Coral, col="#B5179E", lty = 1, lwd = 4)
points(panelC_4$time, panelC_4$Generalists, col="#4A7EFF", bg="#95B3D7", pch=21, lwd = 1, cex=1.1)
points(panelC_5$time, panelC_5$Browsers, col="#4A7EFF", bg="#376092", pch=21, lwd = 1, cex=1.1)
points(panelC_6$time, panelC_6$Grazers, col="#4A7EFF", bg="#DCE6F2", pch=21, lwd = 1, cex=1.1)
points(panelC_2$time, panelC_2$Turf, col="#CA6030", bg="#CA6030", pch=24, lwd = 1, cex=0.9)
points(panelC_3$time, panelC_3$Macroalgae, col="#3C5941", bg="#3C5941", pch=25, lwd = 1, cex=0.9)




dev.off()


```




# Panel Figures for Fishing Pressure Scenarios
```{r}

# Create the plot - fig. S4A


# Save as PDF file
pdf("../../output/figures/fig_S4_A.pdf", width=3.75, height=7)

par(mfrow=c(3,1),
    mar=c(4,5,2.5,2),
    family = "Times")

# first panel
plot(group2_1$time, group2_1$Herbivores,
     type = "l",
     lwd = 4,
     col = "#4A7EFF",
     xlab="Time",
     ylab="Cover / Abundance",
     ylim=c(0,1),
     xlim=c(0,200),
     cex.lab=1.5,
     cex.axis=1.3,
     main = "Fishing Pressure = 0.1",
     cex.main=1.6)
lines(group2_1$time, group2_1$Algae, col="#9BBB59", lty = 1, lwd = 6)
lines(group1_1$time, group1_1$Coral, col="#B5179E", lty = 1, lwd = 4)
points(group4_1$time, group4_1$Generalists, col="#4A7EFF", bg="#95B3D7", pch=21, lwd = 1, cex=1.1)
points(group5_1$time, group5_1$Browsers, col="#4A7EFF", bg="#376092", pch=21, lwd = 1, cex=1.1)
points(group6_1$time, group6_1$Grazers, col="#4A7EFF", bg="#DCE6F2", pch=21, lwd = 1, cex=1.1)
points(group2_1$time, group2_1$Turf, col="#CA6030", bg="#CA6030", pch=24, lwd = 1, cex=0.9)
points(group3_1$time, group3_1$Macroalgae, col="#3C5941", bg="#3C5941", pch=25, lwd = 1, cex=0.9)
legend(x=35, y=1.06,
       # c("Herbivores","Algae","Coral", "Generalists","Browsers","Grazers","Turf","Macroalgae"),
       c("Herbivores","Algae","Coral","Grazers","Generalists","Browsers","Turf","Macroalgae"),
       pch=c(NA, NA, NA, 21, 21, 21, 24, 25),
       lty = c(1,1,1,0,0,0,0,0),
       lwd = c(2,2,2,1,1,1,1,1),
       col=c("#4A7EFF","#9BBB59","#B5179E","#4A7EFF","#4A7EFF","#4A7EFF","#CA6030","#3C5941"),
       pt.bg=c("#4A7EFF","#9BBB59","#B5179E","#DCE6F2","#95B3D7","#376092","#CA6030","#3C5941"),
       ncol=3,
       cex=0.85,
       bty = "n",   ## remove box around legend
       pt.cex = c(1,1,1,1.2,1.2,1.2,1.2,1.2))



# second panel
plot(group2_2$time, group2_2$Herbivores,
     type = "l",
     lwd = 4,
     col = "#4A7EFF",
     xlab="Time",
     ylab="Cover / Abundance",
     ylim=c(0,1),
     xlim=c(0,200),
     cex.lab=1.5,
     cex.axis=1.3,
     main = "Fishing Pressure = 0.5",
     cex.main=1.6)
lines(group2_2$time, group2_2$Algae, col="#9BBB59", lty = 1, lwd = 6)
lines(group1_2$time, group1_2$Coral, col="#B5179E", lty = 1, lwd = 4)
points(group4_2$time, group4_2$Generalists, col="#4A7EFF", bg="#95B3D7", pch=21, lwd = 1, cex=1.1)
points(group5_2$time, group5_2$Browsers, col="#4A7EFF", bg="#376092", pch=21, lwd = 1, cex=1.1)
points(group6_2$time, group6_2$Grazers, col="#4A7EFF", bg="#DCE6F2", pch=21, lwd = 1, cex=1.1)
points(group2_2$time, group2_2$Turf, col="#CA6030", bg="#CA6030", pch=24, lwd = 1, cex=0.9)
points(group3_2$time, group3_2$Macroalgae, col="#3C5941", bg="#3C5941", pch=25, lwd = 1, cex=0.9)


# third panel
plot(group2_3$time, group2_3$Herbivores,
     type = "l",
     lwd = 4,
     col = "#4A7EFF",
     xlab="Time",
     ylab="Cover / Abundance",
     ylim=c(0,1),
     xlim=c(0,200),
     cex.lab=1.5,
     cex.axis=1.3,
     main = "Fishing Pressure = 0.9",
     cex.main=1.6)
lines(group2_3$time, group2_3$Algae, col="#9BBB59", lty = 1, lwd = 6)
lines(group1_3$time, group1_3$Coral, col="#B5179E", lty = 1, lwd = 4)
points(group4_3$time, group4_3$Generalists, col="#4A7EFF", bg="#95B3D7", pch=21, lwd = 1, cex=1.1)
points(group5_3$time, group5_3$Browsers, col="#4A7EFF", bg="#376092", pch=21, lwd = 1, cex=1.1)
points(group6_3$time, group6_3$Grazers, col="#4A7EFF", bg="#DCE6F2", pch=21, lwd = 1, cex=1.1)
points(group2_3$time, group2_3$Turf, col="#CA6030", bg="#CA6030", pch=24, lwd = 1, cex=0.9)
points(group3_3$time, group3_3$Macroalgae, col="#3C5941", bg="#3C5941", pch=25, lwd = 1, cex=0.9)



dev.off()

```



# Panel Figures for Herbivore Community Scenarios
```{r}


# Save as PDF file
pdf("../../output/figures/fig_S4_B.pdf", width=3.75, height=7)


par(mfrow=c(3,1),
    mar=c(4,5,2.5,2),
    family = "Times")


# first panel: generalist-dominated community
plot(panelA_2$time, panelA_2$Herbivores,
     type = "l",
     lwd = 4,
     col = "#4A7EFF",
     xlab="Time",
     ylab="Cover / Abundance",
     ylim=c(0,1),
     xlim=c(0,200),
     cex.lab=1.5,
     cex.axis=1.3,
     main = "Generalist-dominated community",
     cex.main=1.6)
lines(panelA_1$time, panelA_1$Algae, col="#9BBB59", lty = 1, lwd = 6)
lines(panelA_1$time, panelA_1$Coral, col="#B5179E", lty = 1, lwd = 4)
points(panelA_4$time, panelA_4$Generalists, col="#4A7EFF", bg="#95B3D7", pch=21, lwd = 1, cex=1.1)
points(panelA_5$time, panelA_5$Browsers, col="#4A7EFF", bg="#376092", pch=21, lwd = 1, cex=1.1)
points(panelA_6$time, panelA_6$Grazers, col="#4A7EFF", bg="#DCE6F2", pch=21, lwd = 1, cex=1.1)
points(panelA_2$time, panelA_2$Turf, col="#CA6030", bg="#CA6030", pch=24, lwd = 1, cex=0.9)
points(panelA_3$time, panelA_3$Macroalgae, col="#3C5941", bg="#3C5941", pch=25, lwd = 1, cex=0.9)
legend(x=35, y=1.06,
       # c("Herbivores","Algae","Coral", "Generalists","Browsers","Grazers","Turf","Macroalgae"),
       c("Herbivores","Algae","Coral","Grazers","Generalists","Browsers","Turf","Macroalgae"),
       pch=c(NA, NA, NA, 21, 21, 21, 24, 25),
       lty = c(1,1,1,0,0,0,0,0),
       lwd = c(2,2,2,1,1,1,1,1),
       col=c("#4A7EFF","#9BBB59","#B5179E","#4A7EFF","#4A7EFF","#4A7EFF","#CA6030","#3C5941"),
       pt.bg=c("#4A7EFF","#9BBB59","#B5179E","#DCE6F2","#95B3D7","#376092","#CA6030","#3C5941"),
       ncol=3,
       cex=0.85,
       bty = "n",   ## remove box around legend
       pt.cex = c(1,1,1,1.2,1.2,1.2,1.2,1.2))



# second panel: grazer-dominated community
plot(panelB_2$time, panelB_2$Herbivores,
     type = "l",
     lwd = 4,
     col = "#4A7EFF",
     xlab="Time",
     ylab="Cover / Abundance",
     ylim=c(0,1),
     xlim=c(0,200),
     cex.lab=1.5,
     cex.axis=1.3,
     main = "Grazer-dominated community",
     cex.main=1.6)
lines(panelB_1$time, panelB_1$Algae, col="#9BBB59", lty = 1, lwd = 6)
lines(panelB_1$time, panelB_1$Coral, col="#B5179E", lty = 1, lwd = 4)
points(panelB_4$time, panelB_4$Generalists, col="#4A7EFF", bg="#95B3D7", pch=21, lwd = 1, cex=1.1)
points(panelB_5$time, panelB_5$Browsers, col="#4A7EFF", bg="#376092", pch=21, lwd = 1, cex=1.1)
points(panelB_6$time, panelB_6$Grazers, col="#4A7EFF", bg="#DCE6F2", pch=21, lwd = 1, cex=1.1)
points(panelB_2$time, panelB_2$Turf, col="#CA6030", bg="#CA6030", pch=24, lwd = 1, cex=0.9)
points(panelB_3$time, panelB_3$Macroalgae, col="#3C5941", bg="#3C5941", pch=25, lwd = 1, cex=0.9)



# third panel: browser-dominated community
plot(panelC_2$time, panelC_2$Herbivores,
     type = "l",
     lwd = 4,
     col = "#4A7EFF",
     xlab="Time",
     ylab="Cover / Abundance",
     ylim=c(0,1),
     xlim=c(0,200),
     cex.lab=1.5,
     cex.axis=1.3,
     main = "Browser-dominated community",
     cex.main=1.6)
lines(panelC_1$time, panelC_1$Algae, col="#9BBB59", lty = 1, lwd = 6)
lines(panelC_1$time, panelC_1$Coral, col="#B5179E", lty = 1, lwd = 4)
points(panelC_4$time, panelC_4$Generalists, col="#4A7EFF", bg="#95B3D7", pch=21, lwd = 1, cex=1.1)
points(panelC_5$time, panelC_5$Browsers, col="#4A7EFF", bg="#376092", pch=21, lwd = 1, cex=1.1)
points(panelC_6$time, panelC_6$Grazers, col="#4A7EFF", bg="#DCE6F2", pch=21, lwd = 1, cex=1.1)
points(panelC_2$time, panelC_2$Turf, col="#CA6030", bg="#CA6030", pch=24, lwd = 1, cex=0.9)
points(panelC_3$time, panelC_3$Macroalgae, col="#3C5941", bg="#3C5941", pch=25, lwd = 1, cex=0.9)


dev.off()

```




