---
title: "Question 1 Analyses - produces Fig. 2, Fig. 3, and Supplemental Fig. S5"
author: "Shayna A. Sura"
date: "2024-07-14"
output: pdf_document
---


```{r setup, include=FALSE}

library(deSolve)
library(reshape2)
library(viridis)
library(viridisLite)
library(gridExtra)
library(tidyverse) # includes and loads the packages listed below
# library(readr)
# library(tidyr)
# library(dplyr)
# library(ggplot2)
# library(lubridate)

library(here) # helps with paths for files
library(purrr) # vectorized coding approaches for faster analyses
library(scales)
library(ggtext)
library(lemon)
library(cowplot)
library(grid)

```



```{r source model code and parameters}

# source("0.1_basic_model.R")
source("0.2_full_model.R")

```


# Question 1:
How does the functional composition of the herbivorous fish community and total herbivory pressure (set by fishing pressure) affect reef recovery from disturbance?

```{r}

# Define the initial conditions for which to evaluate
GG_values <- seq(0, 0.9, by = 0.025)
BB_values <- seq(0, 0.9, by = 0.025)
f_values <- seq(0, 0.7, by = 0.1)


# Create a function to run the model for different initial conditions
run_model <- function(GG_values, BB_values, f_values, R0_value) {
  initials <- expand.grid(GG_values, BB_values, f_values)
  initials$RR_values <- R0_value
  final_qq <- subset(initials, rowSums(initials[, c(1, 2, 4)]) <= 0.9)
  colnames(final_qq) <- c("Grazers", "Browsers", "Fishing_Pressure", "Generalists")

  # Function to compute the model for given parameters
  compute_model <- function(G0, B0, R0, Fishing_Pressure, P2_tseq, P2_Model, hh_pars) {
    C0 <- 0.15
    M0 <- 0.0
    T0 <- 0.7
    S0 <- 1 - C0 - M0 - T0
    hh_pars[16] <- Fishing_Pressure
    
    zz_output <- lsoda(c(Grazers = G0, Generalists = R0, Browsers = B0,
                         Coral = C0, Turf = T0, Macroalgae = M0),
                       P2_tseq, P2_Model, hh_pars)
    
    zz_output_new <- as.data.frame(zz_output)
    
    list(
      Final_Coral = tail(zz_output_new$Coral, 1),
      Final_Turf = tail(zz_output_new$Turf, 1),
      Final_Macroalgae = tail(zz_output_new$Macroalgae, 1),
      Final_Grazers = tail(zz_output_new$Grazers, 1),
      Final_Browsers = tail(zz_output_new$Browsers, 1),
      Final_Generalists = tail(zz_output_new$Generalists, 1)
    )
  }

  # Apply the model computation in a vectorized way using mapply
  results <- mapply(compute_model,
                    G0 = final_qq$Grazers,
                    B0 = final_qq$Browsers,
                    R0 = final_qq$Generalists,
                    Fishing_Pressure = final_qq$Fishing_Pressure,
                    MoreArgs = list(P2_tseq = P2_tseq, P2_Model = P2_Model, hh_pars = hh_pars),
                    SIMPLIFY = FALSE)

  # Combine results back into the data frame
  results_df <- do.call(rbind, lapply(results, as.data.frame))
  final_qq <- cbind(final_qq, results_df)
  
  return(final_qq)
}

# Run the model for R0 = 0, 0.2, and 0.4
final_qq_0 <- run_model(GG_values, BB_values, f_values, 0)
final_qq_2 <- run_model(GG_values, BB_values, f_values, 0.2)
final_qq_4 <- run_model(GG_values, BB_values, f_values, 0.4)

# Give an Id for each scenario
final_qq_0$Id="Generalists = 0"
final_qq_2$Id="Generalists = 0.2"
final_qq_4$Id="Generalists = 0.4"

# Combine all results into one data frame
qq_all <- bind_rows(final_qq_0, final_qq_2, final_qq_4)

# View the updated data frame
view(qq_all)


```


# Write simulation results to .csv file
```{r}

# export simulation results to .csv file
write_csv(qq_all, file = "../../output/analyses/Q1/question_1_all_results.csv")

```


## Read in .csv file produced from above code (to avoid having to rerun analyses)
```{r}

qq_all <- read_csv(file = "../../output/analyses/Q1/question_1_all_results.csv")

```



# Making figure of all results - supplemental figure S5.
```{r}

# Streamlined version for setting Fishing_ID labels
fishing_labels <- paste0("Fishing\nPressure\n= ", f_values)
names(fishing_labels) <- f_values

qq_all <- qq_all %>%
  mutate(Fishing_ID = factor(Fishing_Pressure, levels = f_values, labels = fishing_labels))


# Define the custom color scale
custom_colors <- colorRampPalette(c("#FCF0D1", "#FAE8B7", "#FAC8AF", "#F9A7A6", "#F9879E", "#F86696", "#F8468D", "#f20089", "#e500a4", "#db00b6", "#b5179e", "#7209b7"))



# Create a custom function to generate alphabetical tags
generate_tags <- function(n) {
  LETTERS[1:n]
}

# Add a column with facet tags
facet_tags <- generate_tags(nrow(unique(qq_all[, c("Fishing_ID", "Id")])))


# Assign facet tags uniquely to each combination of Fishing_ID and Id
qq_all <- qq_all %>%
  arrange(Id, Fishing_ID) %>%
  group_by(Id, Fishing_ID) %>%
  mutate(Facet_Tag = facet_tags[cur_group_id()]) %>%
  ungroup()


# Create the plot
pdf("../../output/figures/fig_S5.pdf", width = 6, height = 12)

ggplot(data = qq_all, aes(Grazers, Browsers)) +
  geom_tile(aes(fill = Final_Coral)) +
  scale_x_continuous("Initial Grazer Abundance",
                     breaks = c(0, 0.3, 0.6, 0.9), 
                     labels = c(0, 0.3, 0.6, 0.9)) +
  scale_y_continuous("Initial Browser Abundance",
                     breaks = c(0, 0.3, 0.6, 0.9), 
                     labels = c(0, 0.3, 0.6, 0.9)) +
  labs(fill = "Final\nCoral\nCover") +
  scale_fill_gradientn(colors = custom_colors(50), limits=c(0,0.9)) +
  scale_colour_gradientn(colors = custom_colors(50), limits=c(0,0.9)) +
  facet_rep_grid(Fishing_ID ~ Id) +
  coord_capped_cart(bottom = 'both', left = 'both') +
  theme_classic(base_size = 10, base_family = "Times") +
  theme(axis.title = element_text(size = 11, face = "bold")) +
  theme(strip.text.x = element_text(size = 11)) +
  theme(strip.text.y = element_text(size = 11, angle = 0)) +
  theme(panel.spacing = unit(1, "lines")) +  # Adds space for facet tags
  geom_richtext(aes(label = Facet_Tag, family = "Times"), 
                x = Inf, y = Inf, 
                hjust = 1.1, vjust = 1.1, 
                size = 4,
                fill = NA, label.color = NA)

dev.off()

```



# Figure 2
## Subset the data to only show some scenarios in the main text figure - Figure 2 Final Coral Cover

```{r}

# reminder of f_values
f_values <- seq(0, 0.7, by = 0.1)

# Set Fishing_ID labels
fishing_labels <- paste0("Fishing\nPressure\n= ", f_values)
names(fishing_labels) <- f_values

# identify those fishing pressure levels to show in main text figure
main_fishing <- c(0, 0.2, 0.4)

# filter qq_all for just the fishing pressures we want to show in the main text figure
qq_small <- qq_all %>% 
  filter(Fishing_Pressure %in% main_fishing) %>% 
  mutate(Fishing_ID = factor(Fishing_Pressure, levels = f_values, labels = fishing_labels))


# Define the custom color scale
custom_colors <- colorRampPalette(c("#FCF0D1", "#FAE8B7", "#FAC8AF", "#F9A7A6", "#F9879E", "#F86696", "#F8468D", "#f20089", "#e500a4", "#db00b6", "#b5179e", "#7209b7"))



# Create a custom function to generate alphabetical tags
generate_tags <- function(n) {
  LETTERS[1:n]
}

# Add a column with facet tags
facet_tags <- generate_tags(nrow(unique(qq_small[, c("Fishing_ID", "Id")])))


# Assign facet tags uniquely to each combination of Fishing_ID and Id
qq_small <- qq_small %>%
  arrange(Id, Fishing_ID) %>%
  group_by(Id, Fishing_ID) %>%
  mutate(Facet_Tag = facet_tags[cur_group_id()]) %>%
  ungroup()





# Create the plot
pdf("../../output/figures/Fig_2.pdf", width = 7, height = 5.7)

ggplot(data = qq_small, aes(Grazers, Browsers)) +
  geom_tile(aes(fill = Final_Coral)) +
  scale_x_continuous("Initial Grazer Abundance",
                     breaks = c(0, 0.3, 0.6, 0.9), 
                     labels = c(0, 0.3, 0.6, 0.9)) +
  scale_y_continuous("Initial Browser Abundance",
                     breaks = c(0, 0.3, 0.6, 0.9), 
                     labels = c(0, 0.3, 0.6, 0.9)) +
  labs(fill = "Final\nCoral\nCover") +
  scale_fill_gradientn(colors = custom_colors(50), limits=c(0,0.9)) +
  scale_colour_gradientn(colors = custom_colors(50), limits=c(0,0.9)) +
  facet_rep_grid(Fishing_ID ~ Id) +
  coord_capped_cart(bottom = 'both', left = 'both') +
  theme_classic(base_size = 10, base_family = "Times") +
  theme(axis.title = element_text(size = 11, face = "bold")) +
  theme(strip.text.x = element_text(size = 11)) +
  theme(strip.text.y = element_text(size = 11, angle = 0)) +
  theme(panel.spacing = unit(1, "lines")) +  # Adds space for facet tags
  geom_richtext(aes(label = Facet_Tag, family = "Times"), 
                x = Inf, y = Inf, 
                hjust = 1.1, vjust = 1.1, 
                size = 4,
                fill = NA, label.color = NA)

dev.off()

```




# Figure 3
## Using the subset of data from figure 2 - show the final cover of turf versus macroalgae - Figure 3
```{r}

#qq_small

# calculate one variable to show either the final cover of turf or macroalgae, depending on which had higher cover
qq_small$Turf_or_Macro<-ifelse(qq_small$Final_Turf > qq_small$Final_Macroalgae,
                                qq_small$Final_Turf,
                                -qq_small$Final_Macroalgae)



# Create the plot
main_plot <- ggplot(data = qq_small, aes(Grazers, Browsers)) +
  geom_tile(aes(fill = Turf_or_Macro)) +
  scale_x_continuous("Initial Grazer Abundance", breaks = c(0, 0.3, 0.6, 0.9), labels = c(0, 0.3, 0.6, 0.9)) +
  scale_y_continuous("Initial Browser Abundance", breaks = c(0, 0.3, 0.6, 0.9), labels = c(0, 0.3, 0.6, 0.9)) +
  labs(fill = "") +
  scale_fill_continuous_divergingx(palette = "Fall",
                                   limits=c(-1,1),
                                   breaks = c(-1, -0.5, 0, 0.5, 1),
                                   labels = c("1.0", "0.5", "0", "0.5", "1.0")) +
  guides(fill = guide_colorbar(title.position = "top",
                               title.hjust = 0.5,
                               label.hjust = 0.5,
                               barheight = unit(6, "lines"),
                               barwidth = unit(1, "lines"),
                               draw.ulim = FALSE,
                               draw.llim = FALSE,
                               frame.colour = "black",
                               ticks.colour = "black",
                               label.position = "right",
                               label.theme = element_text(size = 8),
                               title = "Cover of\nTurf",
                               title.theme = element_text(size = 11))) +
  scale_colour_continuous_divergingx(palette = "Fall",
                                     limits=c(-1,1)) +
  facet_rep_grid(Fishing_ID ~ Id) +
  coord_capped_cart(bottom = 'both', left = 'both') +
  theme_classic(base_size = 10, base_family = "Times") +
  theme(axis.title = element_text(size = 11, face = "bold")) +
  theme(strip.text.x = element_text(size = 11)) +
  theme(strip.text.y = element_text(size = 11, angle = 0)) +
  theme(panel.spacing = unit(1, "lines")) +  # Adds space for facet tags
  geom_richtext(aes(label = Facet_Tag, family = "Times"), 
                x = Inf, y = Inf, 
                hjust = 1.1, vjust = 1.1, 
                size = 4,
                fill = NA, label.color = NA)


final_plot <- ggdraw(main_plot) +
  draw_label("Cover of\nMacroalgae", x = 0.94, y = 0.33, hjust = 0.5, size = 11, angle = 0, fontfamily = "Times")

final_plot

# Save the plot
pdf("../../output/figures/Fig_3.pdf", width = 7, height = 5.7)
print(final_plot)
dev.off()

```










