---
title: "Question 2 Analyses - produces Fig. 4, and Supplemental Fig. S7 and Fig. S8"
author: "Shayna A. Sura"
date: "2024-07-14"
output: pdf_document
---


```{r setup, include=FALSE}

library(deSolve)
library(reshape2)
library(viridis)
library(viridisLite)
library(gridExtra)
library(tidyverse) # includes and loads the packages listed below
# library(readr)
# library(tidyr)
# library(dplyr)
# library(ggplot2)
# library(lubridate)

library(here) # helps with paths for files
library(purrr) # vectorized coding approaches for faster analyses
library(scales)
library(ggtext)
library(lemon)

```



```{r source model code and parameters}

# source("0.1_basic_model.R")
source("0.2_full_model.R")

```


# Question 2: 
How does dominance by different herbivore groups under different fishing pressures interact with abundance of their targeted resources to affect reef recovery after a disturbance?

```{r}



# Define the initial conditions for which to evaluate
turf_values<-seq(0, 0.7, by=0.01)
macro_values<-seq(0, 0.7, by=0.01)
f_values<-seq(0, 0.7, by=0.1)


algae_initials <- expand.grid(turf_values, macro_values, f_values)
colnames(algae_initials) <- c("Turf", "Macroalgae", "Fishing_Pressure")

# Filter rows where the total initial algae is less than or equal to 0.7
final_algae <- subset(algae_initials, rowSums(algae_initials[, c("Turf", "Macroalgae")]) <= 0.7)

# Define a function to run the model for a given set of initial conditions and herbivore abundances
run_model <- function(initial_conditions, G0, B0, R0) {
  C0 <- 0.15
  T0 <- initial_conditions["Turf"]
  M0 <- initial_conditions["Macroalgae"]
  S0 <- 1 - C0 - T0 - M0
  
  initial_state <- c(Grazers = G0, Generalists = R0, Browsers = B0, Coral = C0, Turf = T0, Macroalgae = M0)
  hh_pars[16] <- initial_conditions["Fishing_Pressure"] # set the fishing pressure
  
  zz_output <- lsoda(initial_state, P2_tseq, P2_Model, hh_pars)
  zz_output_new <- as.data.frame(zz_output)
  
  final_values <- c(
    Initial_Turf = T0,
    Initial_Macroalgae = M0,
    Fishing_Pressure = initial_conditions["Fishing_Pressure"],
    Final_Coral = tail(zz_output_new$Coral, 1),
    Final_Turf = tail(zz_output_new$Turf, 1),
    Final_Macroalgae = tail(zz_output_new$Macroalgae, 1)
  )
  
  return(final_values)
}

# Define initial herbivore abundances for different scenarios
herbivore_scenarios <- list(
  Grazer_dominated = c(Grazers = 0.6, Browsers = 0.15, Generalists = 0.15),
  Browser_dominated = c(Grazers = 0.15, Browsers = 0.6, Generalists = 0.15),
  Generalist_dominated = c(Grazers = 0.15, Browsers = 0.15, Generalists = 0.6)
)


# Run simulations for each herbivore scenario
results <- lapply(names(herbivore_scenarios), function(scenario) {
  initial_conditions <- cbind(final_algae, scenario)
  final_values <- apply(final_algae, 1, run_model,
                        G0 = herbivore_scenarios[[scenario]]["Grazers"],
                        B0 = herbivore_scenarios[[scenario]]["Browsers"],
                        R0 = herbivore_scenarios[[scenario]]["Generalists"])

  final_values_df <- as.data.frame(t(final_values))
  colnames(final_values_df) <- c("Initial_Turf", "Initial_Macroalgae", "Fishing_Pressure",
                                 "Final_Coral", "Final_Turf", "Final_Macroalgae")
  final_values_df$Id <- scenario
  return(final_values_df)
})



# Combine results into one data frame
algae_all <- do.call(rbind, results)

# Reorder levels of herbivores for plotting
herbivore_labels <- c("Generalist\ndominated", "Browser\ndominated", "Grazer\ndominated")
names(herbivore_labels) <- c("Generalist_dominated", "Browser_dominated", "Grazer_dominated")

# Getting names for Fishing Pressure for plotting
fishing_labels <- paste0("Fishing\nPressure\n= ", f_values)
names(fishing_labels) <- f_values

# Set Fishing_Pressure and Herbivore_Scenario ID levels
algae_all <- algae_all %>% 
  mutate(Id = factor(Id, levels = names(herbivore_labels), labels = herbivore_labels)) %>% 
  mutate(Fishing_ID = factor(Fishing_Pressure, levels = f_values, labels = fishing_labels))


# levels(algae_all_test$Id)


```





# Write simulation results to .csv file
```{r}

# export simulation results to .csv file
write_csv(algae_all, file = "../../output/analyses/Q2/question_2_all_results.csv")

```


## Read in .csv file produced from above code (to avoid having to rerun analyses)
```{r}

algae_all <- read_csv(file = "../../output/analyses/Q2/question_2_all_results.csv")


```



# Making figure of all results - supplemental figure S7.
```{r}


# Define the custom color scale
custom_colors <- colorRampPalette(c("#FCF0D1", "#FAE8B7", "#FAC8AF", "#F9A7A6", "#F9879E", "#F86696", "#F8468D", "#f20089", "#e500a4", "#db00b6", "#b5179e", "#7209b7"))


# Reorder factor levels
algae_all$Id <- factor(algae_all$Id, levels = c("Browser\ndominated", "Grazer\ndominated", "Generalist\ndominated"))

# Verify the new order
levels(algae_all$Id)


# Create the plot
pdf("../../output/figures/fig_S7.pdf", width = 6, height = 12)

ggplot(data = algae_all, aes(Initial_Turf, Initial_Macroalgae)) +
  geom_tile(aes(fill = Final_Coral)) +
  scale_x_continuous("Initial Turf Abundance",
                     # expand = c(0,0),                     # remove padding between axis line and data
                     breaks = c(0,0.2,0.4,0.6,0.8),
                     labels = c(0,0.2,0.4,0.6,0.8)) +          
  scale_y_continuous("Initial Macroalgal Abundance",
                     # expand = c(0,0),                     # remove padding between axis line and data
                     breaks = c(0,0.2,0.4,0.6,0.8),
                     labels = c(0,0.2,0.4,0.6,0.8)) +       
  labs(fill = "Final\nCoral\nCover") +
  scale_fill_gradientn(colors = custom_colors(50), limits=c(0,0.8)) +
  scale_colour_gradientn(colors = custom_colors(50), limits=c(0,0.8)) +
  facet_rep_grid(Fishing_ID ~ Id) +
  coord_capped_cart(ylim = c(0,0.8), xlim = c(0,0.8),      # set axes limits here to avoid warnings about rows being removed.
                    bottom = 'both', left = 'both') +      # this caps the axes lines at the outer tick marks.
  theme_classic(base_size = 10, base_family = "Times") +
  theme(axis.title = element_text(size = 11, face = "bold")) +
  theme(strip.text.x = element_text(size = 11)) +
  theme(strip.text.y = element_text(size = 11, angle = 0)) 


dev.off()


```



# Figure 4
## Subset the data to only show some scenarios in the main text figure - Figure 2 Final Coral Cover

```{r}

# reminder of f_values
f_values <- seq(0, 0.7, by = 0.1)

# # Set Fishing_ID labels
# fishing_labels <- paste0("Fishing\nPressure\n= ", f_values)
# names(fishing_labels) <- f_values

# identify those fishing pressure levels to show in main text figure
main_fishing <- c(0, 0.3, 0.6)

# Define a tolerance for floating-point comparison
tolerance <- 1e-8

# Filter algae_all for just the fishing pressures we want to show in the main text figure
algae_small <- algae_all %>%
  filter(sapply(Fishing_Pressure, function(fp) any(abs(fp - main_fishing) < tolerance)))

# Check unique values in the filtered data frame
unique(algae_small$Fishing_Pressure)



# Reorder factor levels
algae_small$Id <- factor(algae_small$Id, levels = c("Browser\ndominated", "Grazer\ndominated", "Generalist\ndominated"))
# algae_small$Id <- factor(algae_small$Id, levels = c("Browser-dominated", "Grazer-dominated", "Generalist-dominated"))         # this messes things up for some reason

# Verify the new order
levels(algae_small$Id)



# Define the custom color scale
custom_colors <- colorRampPalette(c("#FCF0D1", "#FAE8B7", "#FAC8AF", "#F9A7A6", "#F9879E", "#F86696", "#F8468D", "#f20089", "#e500a4", "#db00b6", "#b5179e", "#7209b7"))



# Create a custom function to generate alphabetical tags
generate_tags <- function(n) {
  LETTERS[1:n]
}

# Add a column with facet tags
facet_tags <- generate_tags(nrow(unique(algae_small[, c("Fishing_ID", "Id")])))


# Assign facet tags uniquely to each combination of Fishing_ID and Id
algae_small <- algae_small %>%
  arrange(Id, Fishing_ID) %>%
  group_by(Id, Fishing_ID) %>%
  mutate(Facet_Tag = facet_tags[cur_group_id()]) %>%
  ungroup()


# Create the plot
pdf("../../output/figures/Fig_4.pdf", width = 7, height = 5.7)

ggplot(data = algae_small, aes(Initial_Turf, Initial_Macroalgae)) +
  geom_tile(aes(fill = Final_Coral)) +
  scale_x_continuous("Initial Turf Abundance") +
  scale_y_continuous("Initial Macroalgal Abundance") +
  # labs(fill = "Final\nCoral\nCover") +
  scale_fill_gradientn(colors = custom_colors(50), limits=c(0,0.8)) +
  scale_colour_gradientn(colors = custom_colors(50), limits=c(0,0.8)) +
  guides(fill = guide_colorbar(title.position = "top",
                               title.hjust = 0.5,
                               label.hjust = 0.5,
                               barheight = unit(6, "lines"),
                               barwidth = unit(1, "lines"),
                               draw.ulim = FALSE,
                               draw.llim = FALSE,
                               frame.colour = "black",
                               ticks.colour = "black",
                               label.position = "right",
                               label.theme = element_text(size = 8),
                               title = "Final\nCoral\nCover",
                               title.theme = element_text(size = 11))) +
  facet_rep_grid(Fishing_ID ~ Id) +
  coord_capped_cart(ylim = c(0,0.8), xlim = c(0,0.8),      # set axes limits here to avoid warnings about rows being removed.
                    bottom = 'both', left = 'both') +      # this caps the axes lines at the outer tick marks.
  theme_classic(base_size = 10, base_family = "Times") +
  theme(axis.title = element_text(size = 11, face = "bold")) +
  theme(strip.text.x = element_text(size = 11)) +
  theme(strip.text.y = element_text(size = 11, angle = 0)) +
  theme(panel.spacing = unit(1, "lines")) +  # Adds space for facet tags
  geom_richtext(aes(label = Facet_Tag, family = "Times"), 
                x = Inf, y = Inf, 
                hjust = 1.1, vjust = 1.1, 
                size = 4,
                fill = NA, label.color = NA)

dev.off()

```


```{r echo=false, eval=false}

## Trying to get a solution to add the panel labels (A-I) the appropriate panels without them being printed repeatedly on each panel. I haven't got this to work yet.


# # Create a custom function to generate alphabetical tags
# generate_tags <- function(n) {
#   LETTERS[1:n]
# }
# 
# # Add a column with facet tags
# facet_tags <- generate_tags(nrow(unique(algae_small[, c("Fishing_ID", "Id")])))
# 
# 
# # Assign facet tags uniquely to each combination of Fishing_ID and Id
# algae_small <- algae_small %>%
#   arrange(Id, Fishing_ID) %>%
#   group_by(Id, Fishing_ID) %>%
#   mutate(Facet_Tag = facet_tags[cur_group_id()]) %>%
#   ungroup()
# 
# 
# # Create a data frame with the unique facet combinations and their tags
# facet_label_positions <- algae_small %>%
# 
# 
# # Modify the plot to use the custom labels
# pdf("../../output/figures/Fig_4_v2.pdf", width = 7, height = 5.7)
# 
# 
# p <- ggplot(data = algae_small, aes(Initial_Turf, Initial_Macroalgae)) +
#   geom_tile(aes(fill = Final_Coral)) +
#   scale_x_continuous("Initial Turf Abundance") +
#   scale_y_continuous("Initial Macroalgal Abundance") +
#   labs(fill = "Final\nCoral\nCover") +
#   scale_fill_gradientn(colors = custom_colors(50), limits = c(0, 0.8)) +
#   scale_colour_gradientn(colors = custom_colors(50), limits = c(0, 0.8)) +
#   facet_rep_grid(Fishing_ID ~ Id) +
#   coord_capped_cart(ylim = c(0, 0.8), xlim = c(0, 0.8), bottom = 'both', left = 'both') +
#   theme_classic(base_size = 10, base_family = "Times") +
#   theme(axis.title = element_text(size = 11, face = "bold"),
#         strip.text.x = element_text(size = 11),
#         strip.text.y = element_text(size = 11, angle = 0),
#         panel.spacing = unit(1, "lines"))
# 
# # Add the facet tags as annotations
# for (i in 1:nrow(facet_label_positions)) {
#   p <- p + annotate("text", label = facet_label_positions$Facet_Tag[i], 
#                     x = 0.1, y = 0.75, hjust = 0, vjust = 1, 
#                     data = subset(algae_small, 
#                                   Id == facet_label_positions$Id[i] & 
#                                   Fishing_ID == facet_label_positions$Fishing_ID[i]))
# }
# 
# print(p)
# 
# dev.off()


```




# Figure S8
## Using the subset of data from figure 4 - show the final cover of turf versus macroalgae - Figure S8

```{r}

# calculate one variable to show either the final cover of turf or macroalgae, depending on which had higher cover
algae_small$Turf_or_Macro<-ifelse(algae_small$Final_Turf > algae_small$Final_Macroalgae,
                                  algae_small$Final_Turf,
                                  -algae_small$Final_Macroalgae)



# Create the plot
S8_main_plot <- ggplot(data = algae_small, aes(Initial_Turf, Initial_Macroalgae)) +
  geom_tile(aes(fill = Turf_or_Macro)) +
  scale_x_continuous("Initial Turf Abundance") +
  scale_y_continuous("Initial Macroalgal Abundance") +
  # labs(fill = "") +
  scale_fill_continuous_divergingx(palette = "Fall",
                                   limits=c(-1,1),
                                   breaks = c(-1, -0.5, 0, 0.5, 1),
                                   labels = c("1.0", "0.5", "0", "0.5", "1.0")) +
  guides(fill = guide_colorbar(title.position = "top",
                               title.hjust = 0.5,
                               label.hjust = 0.5,
                               barheight = unit(6, "lines"),
                               barwidth = unit(1, "lines"),
                               draw.ulim = FALSE,
                               draw.llim = FALSE,
                               frame.colour = "black",
                               ticks.colour = "black",
                               label.position = "right",
                               label.theme = element_text(size = 8),
                               title = "Cover of\nTurf",
                               title.theme = element_text(size = 11))) +
  scale_colour_continuous_divergingx(palette = "Fall",
                                     limits=c(-1,1)) +
  facet_rep_grid(Fishing_ID ~ Id) +
  coord_capped_cart(ylim = c(0,0.8), xlim = c(0,0.8),      # set axes limits here to avoid warnings about rows being removed.
                    bottom = 'both', left = 'both') +      # this caps the axes lines at the outer tick marks.
  theme_classic(base_size = 10, base_family = "Times") +
  theme(axis.title = element_text(size = 11, face = "bold")) +
  theme(strip.text.x = element_text(size = 11)) +
  theme(strip.text.y = element_text(size = 11, angle = 0)) +
  theme(panel.spacing = unit(1, "lines")) +  # Adds space for facet tags
  geom_richtext(aes(label = Facet_Tag, family = "Times"), 
                x = Inf, y = Inf, 
                hjust = 1.1, vjust = 1.1, 
                size = 4,
                fill = NA, label.color = NA)


S8_final_plot <- ggdraw(S8_main_plot) +
  draw_label("Cover of\nMacroalgae", x = 0.94, y = 0.325, hjust = 0.5, size = 11, angle = 0, fontfamily = "Times")

S8_final_plot

# Save the plot
pdf("../../output/figures/fig_S8.pdf", width = 7, height = 5.7)
print(S8_final_plot)
dev.off()



```




