---
title: "Figure 5 - Bistability"
author: "Shayna A. Sura"
date: "07/13/2024 - July 13, 2024"
output: pdf_document
---

```{r setup, echo=FALSE}

library(deSolve)
library(reshape2)
library(viridis)
library(gridExtra)
library(tidyverse) # includes and loads the packages listed below
# library(readr)
# library(tidyr)
# library(dplyr)
# library(ggplot2)
# library(lubridate)

library(here) # helps with paths for files
library(purrr) # vectorized coding approaches for faster analyses
library(scales)


```


# Our Model Set up
```{r source model code and parameters}

source("0.2_full_model.R")

```



# Question 3:
How does variation in the dominant herbivore functional group influence the occurrence of alternative stable states in response to fishing pressure?


## Expanded Model - aka 'Herbivores Even' Scenario
```{r}

### For loops over different initial coral cover for various levels of fishing pressure using the expanded model but with the more realistic parameters (hh_pars). The initial conditions are the same though.

f_values<-seq(0,1,by=0.01)
# coral_initials<-seq(0,1,0.01)
coral_initials<-seq(0,0.85,0.01)

expanded_1<-expand.grid(coral_initials,f_values)
colnames(expanded_1)<-c("Initial_Coral","Fishing_Pressure")


for(i in 1:length(expanded_1$Initial_Coral)){
    C0<-expanded_1$Initial_Coral[i]
    B0<-0.3
    R0<-0.3
    G0<-0.3
#    C0<-0.75
    S0<-0.15
    M0<-(1-C0-S0)/2
    T0<-(1-C0-S0)/2
    hh_pars[16]<-expanded_1$Fishing_Pressure[i]   #set the fishing pressure
    zz_output<-lsoda(c(Grazers =G0, Generalists =R0, Browsers =B0,
                   Coral = C0,Turf = T0,Macroalgae=M0),
                 P2_tseq, P2_Model, hh_pars)
    zz_output_new<-as.data.frame(zz_output)
    expanded_1$Final_Coral[i]<-tail(zz_output_new$Coral,1)
}


# export simulation results to .csv file
write_csv(expanded_1, file = "../../output/analyses/fig5/bistability-expanded_1.csv")


## Trying to figure out precisely which fishing pressure values the coral reef system exhibits bistability depending upon the initial coral cover conditions.
exp_C0_0<-subset(expanded_1,subset = expanded_1$Initial_Coral == 0)
exp_C0_0.85<-subset(expanded_1,subset = expanded_1$Initial_Coral == 0.85)

for(i in 1:nrow(exp_C0_0)){
  exp_C0_0$bistability[i]<-format(round(exp_C0_0[i,3], 7), nsmall = 7) != 
                     format(round(exp_C0_0.85[i,3], 7), nsmall = 7)
}


## Find the fishing pressure values where the system can exhibit bistability
min(exp_C0_0$Fishing_Pressure[which(exp_C0_0$bistability==TRUE)])
max(exp_C0_0$Fishing_Pressure[which(exp_C0_0$bistability==TRUE)])
exp_C0_0$Fishing_Pressure[which(exp_C0_0$bistability==TRUE)]
## bistability between 0.42 - 0.58


```


# Herbivore Community Dominance Scenarios

## High Browsers - vectorized approach for evaluating

```{r}

## High Browsers


P2_tseq <- seq(0, 1000, by = 0.1)

f_values <- seq(0, 1, by = 0.01)
coral_initials <- seq(0, 0.85, 0.01)

high_browsers_1 <- expand.grid(coral_initials, f_values)
colnames(high_browsers_1) <- c("Initial_Coral", "Fishing_Pressure")

# Function to run the model and extract the final coral value
run_model <- function(initial_coral, fishing_pressure) {
  C0 <- initial_coral
  B0 <- 0.6
  R0 <- 0.15
  G0 <- 0.15
  S0 <- 0.15
  M0 <- (1 - C0 - S0) / 2
  T0 <- (1 - C0 - S0) / 2
  
  # Update fishing pressure in parameters
  hh_pars[16] <- fishing_pressure
  
  # Run the model
  zz_output <- lsoda(c(Grazers = G0, Generalists = R0, Browsers = B0, Coral = C0, Turf = T0, Macroalgae = M0),
                     P2_tseq, P2_Model, hh_pars)
  
  # Extract the final coral value
  final_coral <- tail(as.data.frame(zz_output)$Coral, 1)
  return(final_coral)
}

high_browsers_1 <- high_browsers_1 %>%
  mutate(Final_Coral = pmap_dbl(list(Initial_Coral, Fishing_Pressure), run_model))

# high_browsers_1


# export simulation results to .csv file
write_csv(high_browsers_1, file = "../../output/analyses/fig5/bistability-high_browsers_1.csv")

```




## High Grazers - vectorized approach for evaluating

```{r}

## High Grazers


P2_tseq <- seq(0, 1000, by = 0.1)

f_values <- seq(0, 1, by = 0.01)
coral_initials <- seq(0, 0.85, 0.01)

high_grazers_1 <- expand.grid(coral_initials, f_values)
colnames(high_grazers_1) <- c("Initial_Coral", "Fishing_Pressure")

# Function to run the model and extract the final coral value
run_model <- function(initial_coral, fishing_pressure) {
  C0 <- initial_coral
  B0 <- 0.15
  R0 <- 0.15
  G0 <- 0.6
  S0 <- 0.15
  M0 <- (1 - C0 - S0) / 2
  T0 <- (1 - C0 - S0) / 2
  
  # Update fishing pressure in parameters
  hh_pars[16] <- fishing_pressure
  
  # Run the model
  zz_output <- lsoda(c(Grazers = G0, Generalists = R0, Browsers = B0, Coral = C0, Turf = T0, Macroalgae = M0),
                     P2_tseq, P2_Model, hh_pars)
  
  # Extract the final coral value
  final_coral <- tail(as.data.frame(zz_output)$Coral, 1)
  return(final_coral)
}

high_grazers_1 <- high_grazers_1 %>%
  mutate(Final_Coral = pmap_dbl(list(Initial_Coral, Fishing_Pressure), run_model))

# high_grazers_1


# export simulation results to .csv file
write_csv(high_grazers_1, file = "../../output/analyses/fig5/bistability-high_grazers_1.csv")

```



## High Generalists - vectorized approach for evaluating

```{r}

## High Generalists

P2_tseq <- seq(0, 1000, by = 0.1)

f_values <- seq(0, 1, by = 0.01)
coral_initials <- seq(0, 0.85, 0.01)

high_generalists_1<-expand.grid(coral_initials,f_values)
colnames(high_generalists_1)<-c("Initial_Coral","Fishing_Pressure")

# Function to run the model and extract the final coral value
run_model <- function(initial_coral, fishing_pressure) {
  C0 <- initial_coral
  B0 <- 0.15
  R0 <- 0.6
  G0 <- 0.15
  S0 <- 0.15
  M0 <- (1 - C0 - S0) / 2
  T0 <- (1 - C0 - S0) / 2
  
  # Update fishing pressure in parameters
  hh_pars[16] <- fishing_pressure
  
  # Run the model
  zz_output <- lsoda(c(Grazers = G0, Generalists = R0, Browsers = B0, Coral = C0, Turf = T0, Macroalgae = M0),
                     P2_tseq, P2_Model, hh_pars)
  
  # Extract the final coral value
  final_coral <- tail(as.data.frame(zz_output)$Coral, 1)
  return(final_coral)
}

high_generalists_1 <- high_generalists_1 %>%
  mutate(Final_Coral = pmap_dbl(list(Initial_Coral, Fishing_Pressure), run_model))

# high_generalists_1


# export simulation results to .csv file
write_csv(high_generalists_1, file = "../../output/analyses/fig5/bistability-high_generalists_1.csv")

```



## Read in all .csv files produced from above code (to avoid having to rerun analyses)
```{r}

expanded_1 <- read_csv(file = "../../output/analyses/fig5/bistability-expanded_1.csv")
high_grazers_1 <- read_csv(file = "../../output/analyses/fig5/bistability-high_grazers_1.csv")
high_generalists_1 <- read_csv(file = "../../output/analyses/fig5/bistability-high_generalists_1.csv")
high_browsers_1 <- read_csv(file = "../../output/analyses/fig5/bistability-high_browsers_1.csv")

```




## Heat map of output

```{r Fig. 5A Main Text}

## Combine output of all 4 so I can plot them all easily with ggplot

# Row bind the various data frames in order to plot by them
expanded_1$Id <- "A) Herbivore groups even"
high_browsers_1$Id <- "C) Browser-dominated"
high_grazers_1$Id <-  "D) Grazer-dominated"
high_generalists_1$Id <- "B) Generalist-dominated"
bistability_all <-  rbind(expanded_1, high_generalists_1, high_browsers_1, high_grazers_1)


# assign order of factor levels
bistability_all$Id <- factor(bistability_all$Id, levels=c("A) Herbivore groups even","B) Generalist-dominated","C) Browser-dominated","D) Grazer-dominated"))


# Define the custom color scale
custom_colors <- colorRampPalette(c("#FCF0D1", "#FAE8B7", "#FAC8AF", "#F9A7A6", "#F9879E", "#F86696", "#F8468D", "#f20089", "#e500a4", "#db00b6", "#b5179e", "#7209b7"))


pdf("../../output/figures/Fig_5A_v2.pdf",width=3.5,height=8.5) #this version has S0 = 0.15, and coral initials only going as high as 0.85


#quartz()
ggplot(bistability_all, aes(Fishing_Pressure, Initial_Coral)) +
  geom_tile(aes(fill = Final_Coral)) +
  theme_classic(base_size=14,base_family = "Times") + 
  theme(axis.title=element_text(size=16,face="bold")) +
  labs(fill = "Final\nCoral\nCover") +
  scale_fill_gradientn(colors = custom_colors(50), limits=c(0,0.9)) +
  scale_colour_gradientn(colors = custom_colors(50), limits=c(0,0.9)) +
  scale_x_continuous("Fishing Pressure",
                     expand = c(0, 0),
                     breaks = c(0,0.25,0.5,0.75,1),
                     labels = c(0,0.25,0.5,0.75,1)) +
  scale_y_continuous("Initial Coral Cover",
                     expand = c(0, 0),
                     breaks = c(0,0.2,0.4,0.6,0.8),
                     labels = c(0,0.2,0.4,0.6,0.8)) +
  facet_wrap(~Id,nrow = 4) +
  theme(strip.text.x = element_text(size = 11))

# dev.off()



```


