---
title: "5.2_hysteresis"
author: "Shayna A. Sura"
date: "2024-07-13"
output: html_document
---

```{r setup, include=FALSE}

# library(gtable)
# library(grid)


library(deSolve)
library(reshape2)
library(viridis)
library(gridExtra)
library(tidyverse) # includes and loads the packages listed below
# library(readr)
# library(tidyr)
# library(dplyr)
# library(ggplot2)
# library(lubridate)

library(here) # helps with paths for files
library(purrr) # vectorized coding approaches for faster analyses
library(scales)


```


# Our Model Set up
```{r source model code and parameters}

source("0.2_full_model.R")

```


# Question 3:
How does variation in the dominant herbivore functional group influence the occurrence of alternative stable states in response to fishing pressure?


## Expanded Model Hysteresis Plot
### Part 1: Herbivores with equal abundances (Herbivores Even Scenario)
```{r}

# Set up a for loop to run lsoda for each fishing pressure
# Need to start each new run with where the system ENDED after the last run / loop

f_values<-seq(0,1,by=0.005)
P2_tseq<-seq(0,1000,by=0.1)

#tseq<-seq(0,100,by=0.1)

## set up a data frame to store the results I want
Exp_Hysteresis_output_real<-data.frame(f_values)

# Set up for loop to run lsoda with different initial conditions & different fishing pressures
for(i in 1:length(f_values)){
  if(i==1){
    G0<-0.3
    R0<-0.3
    B0<-0.3
    C0<-0.75
    T0<-0.05
    M0<-0.05
    S0 <- 1 - T0 - C0 - M0
    }
  else{
    G0<-tail(P2_output_new$Grazers,1)
    R0<-tail(P2_output_new$Generalists,1)
    B0<-tail(P2_output_new$Browsers,1)
    C0<-tail(P2_output_new$Coral,1)
    T0<-tail(P2_output_new$Turf,1)
    M0<-tail(P2_output_new$Macroalgae,1)
    S0<-tail(P2_output_new$Space,1)
  }
  P2_state_vars<-c(GG=G0, RR=R0, BB=B0, CC=C0, TT=T0, MM=M0, SS=S0)
  hh_pars[16]<-f_values[i] # set fishing pressure
  P2_output<-lsoda(c(Grazers=G0, Generalists=R0, Browsers=B0,
                     Coral=C0, Turf=T0, Macroalgae=M0),
                 P2_tseq, P2_Model, hh_pars)
  P2_output_new<-as.data.frame(P2_output)
  P2_output_new$Space = 1 - P2_output_new$Coral - P2_output_new$Turf - P2_output_new$Macroalgae
  P2_output_new$Algae = P2_output_new$Turf + P2_output_new$Macroalgae
  P2_output_new$Herbivores = P2_output_new$Grazers + P2_output_new$Generalists + P2_output_new$Browsers
  
  
  Exp_Hysteresis_output_real$Fishing[i]<-hh_pars[16]
  Exp_Hysteresis_output_real$Initial_Coral[i]<-C0
  Exp_Hysteresis_output_real$Final_Coral[i]<-tail(P2_output_new$Coral,1)
  Exp_Hysteresis_output_real$Final_Turf[i]<-tail(P2_output_new$Turf,1)
  Exp_Hysteresis_output_real$Final_Macroalgae[i]<-tail(P2_output_new$Macroalgae,1)
  Exp_Hysteresis_output_real$Final_Algae[i]<-tail(P2_output_new$Algae,1)
  Exp_Hysteresis_output_real$Final_Grazers[i]<-tail(P2_output_new$Grazers,1)
  Exp_Hysteresis_output_real$Final_Generalists[i]<-tail(P2_output_new$Generalists,1)
  Exp_Hysteresis_output_real$Final_Browsers[i]<-tail(P2_output_new$Browsers,1)
  Exp_Hysteresis_output_real$Final_Herbivores[i]<-tail(P2_output_new$Herbivores,1)
  Exp_Hysteresis_output_real$Final_Space[i]<-tail(P2_output_new$Space,1)
}




# Reversing the simulation

#f_values<-seq(0,1,by=0.005)
f_values_2<-rev(seq(0,1,by=0.005))
P2_tseq<-seq(0,1000,by=0.1)

#tseq<-seq(0,100,by=0.1)

## set up a data frame to store the results I want
Exp_Hysteresis_output_real_rev<-data.frame(f_values_2)

# Set up for loop to run lsoda with different initial conditions & different fishing pressures
for(i in 1:length(f_values_2)){
  if(i==1){
    G0<-tail(Exp_Hysteresis_output_real$Final_Grazers,1)
    R0<-tail(Exp_Hysteresis_output_real$Final_Generalists,1)
    B0<-tail(Exp_Hysteresis_output_real$Final_Browsers,1)
    C0<-tail(Exp_Hysteresis_output_real$Final_Coral,1)
    T0<-tail(Exp_Hysteresis_output_real$Final_Turf,1)
    M0<-tail(Exp_Hysteresis_output_real$Final_Macroalgae,1)
    S0<-tail(Exp_Hysteresis_output_real$Final_Space,1)
    
    # G0<-0.3
    # R0<-0.3
    # B0<-0.3
    # C0<-0.75
    # T0<-0.05
    # M0<-0.05
    # S0 <- 1 - T0 - C0 - M0
    }
  else{
    G0<-tail(P2_output_new$Grazers,1)
    R0<-tail(P2_output_new$Generalists,1)
    B0<-tail(P2_output_new$Browsers,1)
    C0<-tail(P2_output_new$Coral,1)
    T0<-tail(P2_output_new$Turf,1)
    M0<-tail(P2_output_new$Macroalgae,1)
    S0<-tail(P2_output_new$Space,1)
  }
  P2_state_vars<-c(GG=G0, RR=R0, BB=B0, CC=C0, TT=T0, MM=M0, SS=S0)
  hh_pars[16]<-f_values_2[i] # set fishing pressure
  P2_output<-lsoda(c(Grazers=G0, Generalists=R0, Browsers=B0,
                     Coral=C0, Turf=T0, Macroalgae=M0),
                 P2_tseq, P2_Model, hh_pars)
  P2_output_new<-as.data.frame(P2_output)
  P2_output_new$Space = 1 - P2_output_new$Coral - P2_output_new$Turf - P2_output_new$Macroalgae
  P2_output_new$Algae = P2_output_new$Turf + P2_output_new$Macroalgae
  P2_output_new$Herbivores = P2_output_new$Grazers + P2_output_new$Generalists + P2_output_new$Browsers
  
  
  Exp_Hysteresis_output_real_rev$Fishing[i]<-hh_pars[16]
  Exp_Hysteresis_output_real_rev$Initial_Coral[i]<-C0
  Exp_Hysteresis_output_real_rev$Final_Coral[i]<-tail(P2_output_new$Coral,1)
  Exp_Hysteresis_output_real_rev$Final_Turf[i]<-tail(P2_output_new$Turf,1)
  Exp_Hysteresis_output_real_rev$Final_Macroalgae[i]<-tail(P2_output_new$Macroalgae,1)
  Exp_Hysteresis_output_real_rev$Final_Algae[i]<-tail(P2_output_new$Algae,1)
  Exp_Hysteresis_output_real_rev$Final_Grazers[i]<-tail(P2_output_new$Grazers,1)
  Exp_Hysteresis_output_real_rev$Final_Generalists[i]<-tail(P2_output_new$Generalists,1)
  Exp_Hysteresis_output_real_rev$Final_Browsers[i]<-tail(P2_output_new$Browsers,1)
  Exp_Hysteresis_output_real_rev$Final_Herbivores[i]<-tail(P2_output_new$Herbivores,1)
  Exp_Hysteresis_output_real_rev$Final_Space[i]<-tail(P2_output_new$Space,1)
}

```


## Expanded Model Part 2a: High Browsers Scenario
# B0<-0.6
# R0<-0.15
# G0<-0.15

```{r Expanded Hysteresis High Browsers}

# Initial conditions for High Browsers Scenario
# B0<-0.6
# R0<-0.15
# G0<-0.15

# Set up a for loop to run lsoda for each fishing pressure
# Need to start each new run with where the system ENDED after the last run / loop

f_values<-seq(0,1,by=0.005)
P2_tseq<-seq(0,1000,by=0.1)

#tseq<-seq(0,100,by=0.1)

## set up a data frame to store the results I want
Browsers_Exp_Hyst_output<-data.frame(f_values)

# Set up for loop to run lsoda with different initial conditions & different fishing pressures
for(i in 1:length(f_values)){
  if(i==1){
    B0<-0.6
    R0<-0.15
    G0<-0.15
    C0<-0.75
    T0<-0.05
    M0<-0.05
    S0 <- 1 - T0 - C0 - M0
    }
  else{
    G0<-tail(P2_output_new$Grazers,1)
    R0<-tail(P2_output_new$Generalists,1)
    B0<-tail(P2_output_new$Browsers,1)
    C0<-tail(P2_output_new$Coral,1)
    T0<-tail(P2_output_new$Turf,1)
    M0<-tail(P2_output_new$Macroalgae,1)
    S0<-tail(P2_output_new$Space,1)
  }
  P2_state_vars<-c(GG=G0, RR=R0, BB=B0, CC=C0, TT=T0, MM=M0, SS=S0)
  hh_pars[16]<-f_values[i] # set fishing pressure
  P2_output<-lsoda(c(Grazers=G0, Generalists=R0, Browsers=B0,
                     Coral=C0, Turf=T0, Macroalgae=M0),
                 P2_tseq, P2_Model, hh_pars)
  P2_output_new<-as.data.frame(P2_output)
  P2_output_new$Space = 1 - P2_output_new$Coral - P2_output_new$Turf - P2_output_new$Macroalgae
  P2_output_new$Algae = P2_output_new$Turf + P2_output_new$Macroalgae
  P2_output_new$Herbivores = P2_output_new$Grazers + P2_output_new$Generalists + P2_output_new$Browsers
  
  
  Browsers_Exp_Hyst_output$Fishing[i]<-hh_pars[16]
  Browsers_Exp_Hyst_output$Initial_Coral[i]<-C0
  Browsers_Exp_Hyst_output$Final_Coral[i]<-tail(P2_output_new$Coral,1)
  Browsers_Exp_Hyst_output$Final_Turf[i]<-tail(P2_output_new$Turf,1)
  Browsers_Exp_Hyst_output$Final_Macroalgae[i]<-tail(P2_output_new$Macroalgae,1)
  Browsers_Exp_Hyst_output$Final_Algae[i]<-tail(P2_output_new$Algae,1)
  Browsers_Exp_Hyst_output$Final_Grazers[i]<-tail(P2_output_new$Grazers,1)
  Browsers_Exp_Hyst_output$Final_Generalists[i]<-tail(P2_output_new$Generalists,1)
  Browsers_Exp_Hyst_output$Final_Browsers[i]<-tail(P2_output_new$Browsers,1)
  Browsers_Exp_Hyst_output$Final_Herbivores[i]<-tail(P2_output_new$Herbivores,1)
  Browsers_Exp_Hyst_output$Final_Space[i]<-tail(P2_output_new$Space,1)
}




# Reversing the simulation

#f_values<-seq(0,1,by=0.005)
f_values_2<-rev(seq(0,1,by=0.005))
P2_tseq<-seq(0,1000,by=0.1)

#tseq<-seq(0,100,by=0.1)

## set up a data frame to store the results I want
Browsers_Exp_Hyst_output_rev<-data.frame(f_values_2)

# Set up for loop to run lsoda with different initial conditions & different fishing pressures
for(i in 1:length(f_values_2)){
  if(i==1){
    G0<-tail(Browsers_Exp_Hyst_output$Final_Grazers,1)
    R0<-tail(Browsers_Exp_Hyst_output$Final_Generalists,1)
    B0<-tail(Browsers_Exp_Hyst_output$Final_Browsers,1)
    C0<-tail(Browsers_Exp_Hyst_output$Final_Coral,1)
    T0<-tail(Browsers_Exp_Hyst_output$Final_Turf,1)
    M0<-tail(Browsers_Exp_Hyst_output$Final_Macroalgae,1)
    S0<-tail(Browsers_Exp_Hyst_output$Final_Space,1)
    
    # B0<-0.6
    # R0<-0.15
    # G0<-0.15
    # C0<-0.75
    # T0<-0.05
    # M0<-0.05
    # S0 <- 1 - T0 - C0 - M0
    }
  else{
    G0<-tail(P2_output_new$Grazers,1)
    R0<-tail(P2_output_new$Generalists,1)
    B0<-tail(P2_output_new$Browsers,1)
    C0<-tail(P2_output_new$Coral,1)
    T0<-tail(P2_output_new$Turf,1)
    M0<-tail(P2_output_new$Macroalgae,1)
    S0<-tail(P2_output_new$Space,1)
  }
  P2_state_vars<-c(GG=G0, RR=R0, BB=B0, CC=C0, TT=T0, MM=M0, SS=S0)
  hh_pars[16]<-f_values_2[i] # set fishing pressure
  P2_output<-lsoda(c(Grazers=G0, Generalists=R0, Browsers=B0,
                     Coral=C0, Turf=T0, Macroalgae=M0),
                 P2_tseq, P2_Model, hh_pars)
  P2_output_new<-as.data.frame(P2_output)
  P2_output_new$Space = 1 - P2_output_new$Coral - P2_output_new$Turf - P2_output_new$Macroalgae
  P2_output_new$Algae = P2_output_new$Turf + P2_output_new$Macroalgae
  P2_output_new$Herbivores = P2_output_new$Grazers + P2_output_new$Generalists + P2_output_new$Browsers
  
  
  Browsers_Exp_Hyst_output_rev$Fishing[i]<-hh_pars[16]
  Browsers_Exp_Hyst_output_rev$Initial_Coral[i]<-C0
  Browsers_Exp_Hyst_output_rev$Final_Coral[i]<-tail(P2_output_new$Coral,1)
  Browsers_Exp_Hyst_output_rev$Final_Turf[i]<-tail(P2_output_new$Turf,1)
  Browsers_Exp_Hyst_output_rev$Final_Macroalgae[i]<-tail(P2_output_new$Macroalgae,1)
  Browsers_Exp_Hyst_output_rev$Final_Algae[i]<-tail(P2_output_new$Algae,1)
  Browsers_Exp_Hyst_output_rev$Final_Grazers[i]<-tail(P2_output_new$Grazers,1)
  Browsers_Exp_Hyst_output_rev$Final_Generalists[i]<-tail(P2_output_new$Generalists,1)
  Browsers_Exp_Hyst_output_rev$Final_Browsers[i]<-tail(P2_output_new$Browsers,1)
  Browsers_Exp_Hyst_output_rev$Final_Herbivores[i]<-tail(P2_output_new$Herbivores,1)
  Browsers_Exp_Hyst_output_rev$Final_Space[i]<-tail(P2_output_new$Space,1)
}

```



## Expanded Model Part 2b: High Generalists Scenario
# B0<-0.15
# R0<-0.6
# G0<-0.15

```{r Expanded Hysteresis High Generalists}

# Initial conditions for High Generalists Scenario
# B0<-0.15
# R0<-0.6
# G0<-0.15

# Set up a for loop to run lsoda for each fishing pressure
# Need to start each new run with where the system ENDED after the last run / loop

f_values<-seq(0,1,by=0.005)
P2_tseq<-seq(0,1000,by=0.1)

#tseq<-seq(0,100,by=0.1)

## set up a data frame to store the results I want
Generalists_Exp_Hyst_output<-data.frame(f_values)

# Set up for loop to run lsoda with different initial conditions & different fishing pressures
for(i in 1:length(f_values)){
  if(i==1){
    B0<-0.15
    R0<-0.6
    G0<-0.15
    C0<-0.75
    T0<-0.05
    M0<-0.05
    S0 <- 1 - T0 - C0 - M0
    }
  else{
    G0<-tail(P2_output_new$Grazers,1)
    R0<-tail(P2_output_new$Generalists,1)
    B0<-tail(P2_output_new$Browsers,1)
    C0<-tail(P2_output_new$Coral,1)
    T0<-tail(P2_output_new$Turf,1)
    M0<-tail(P2_output_new$Macroalgae,1)
    S0<-tail(P2_output_new$Space,1)
  }
  P2_state_vars<-c(GG=G0, RR=R0, BB=B0, CC=C0, TT=T0, MM=M0, SS=S0)
  hh_pars[16]<-f_values[i] # set fishing pressure
  P2_output<-lsoda(c(Grazers=G0, Generalists=R0, Browsers=B0,
                     Coral=C0, Turf=T0, Macroalgae=M0),
                 P2_tseq, P2_Model, hh_pars)
  P2_output_new<-as.data.frame(P2_output)
  P2_output_new$Space = 1 - P2_output_new$Coral - P2_output_new$Turf - P2_output_new$Macroalgae
  P2_output_new$Algae = P2_output_new$Turf + P2_output_new$Macroalgae
  P2_output_new$Herbivores = P2_output_new$Grazers + P2_output_new$Generalists + P2_output_new$Browsers
  
  
  Generalists_Exp_Hyst_output$Fishing[i]<-hh_pars[16]
  Generalists_Exp_Hyst_output$Initial_Coral[i]<-C0
  Generalists_Exp_Hyst_output$Final_Coral[i]<-tail(P2_output_new$Coral,1)
  Generalists_Exp_Hyst_output$Final_Turf[i]<-tail(P2_output_new$Turf,1)
  Generalists_Exp_Hyst_output$Final_Macroalgae[i]<-tail(P2_output_new$Macroalgae,1)
  Generalists_Exp_Hyst_output$Final_Algae[i]<-tail(P2_output_new$Algae,1)
  Generalists_Exp_Hyst_output$Final_Grazers[i]<-tail(P2_output_new$Grazers,1)
  Generalists_Exp_Hyst_output$Final_Generalists[i]<-tail(P2_output_new$Generalists,1)
  Generalists_Exp_Hyst_output$Final_Browsers[i]<-tail(P2_output_new$Browsers,1)
  Generalists_Exp_Hyst_output$Final_Herbivores[i]<-tail(P2_output_new$Herbivores,1)
  Generalists_Exp_Hyst_output$Final_Space[i]<-tail(P2_output_new$Space,1)
}




# Reversing the simulation

#f_values<-seq(0,1,by=0.005)
f_values_2<-rev(seq(0,1,by=0.005))
P2_tseq<-seq(0,1000,by=0.1)

#tseq<-seq(0,100,by=0.1)

## set up a data frame to store the results I want
Generalists_Exp_Hyst_output_rev<-data.frame(f_values_2)

# Set up for loop to run lsoda with different initial conditions & different fishing pressures
for(i in 1:length(f_values_2)){
  if(i==1){
    G0<-tail(Generalists_Exp_Hyst_output$Final_Grazers,1)
    R0<-tail(Generalists_Exp_Hyst_output$Final_Generalists,1)
    B0<-tail(Generalists_Exp_Hyst_output$Final_Browsers,1)
    C0<-tail(Generalists_Exp_Hyst_output$Final_Coral,1)
    T0<-tail(Generalists_Exp_Hyst_output$Final_Turf,1)
    M0<-tail(Generalists_Exp_Hyst_output$Final_Macroalgae,1)
    S0<-tail(Generalists_Exp_Hyst_output$Final_Space,1)
    
    # B0<-0.15
    # R0<-0.6
    # G0<-0.15
    # C0<-0.75
    # T0<-0.05
    # M0<-0.05
    # S0 <- 1 - T0 - C0 - M0
    }
  else{
    G0<-tail(P2_output_new$Grazers,1)
    R0<-tail(P2_output_new$Generalists,1)
    B0<-tail(P2_output_new$Browsers,1)
    C0<-tail(P2_output_new$Coral,1)
    T0<-tail(P2_output_new$Turf,1)
    M0<-tail(P2_output_new$Macroalgae,1)
    S0<-tail(P2_output_new$Space,1)
  }
  P2_state_vars<-c(GG=G0, RR=R0, BB=B0, CC=C0, TT=T0, MM=M0, SS=S0)
  hh_pars[16]<-f_values_2[i] # set fishing pressure
  P2_output<-lsoda(c(Grazers=G0, Generalists=R0, Browsers=B0,
                     Coral=C0, Turf=T0, Macroalgae=M0),
                 P2_tseq, P2_Model, hh_pars)
  P2_output_new<-as.data.frame(P2_output)
  P2_output_new$Space = 1 - P2_output_new$Coral - P2_output_new$Turf - P2_output_new$Macroalgae
  P2_output_new$Algae = P2_output_new$Turf + P2_output_new$Macroalgae
  P2_output_new$Herbivores = P2_output_new$Grazers + P2_output_new$Generalists + P2_output_new$Browsers
  
  
  Generalists_Exp_Hyst_output_rev$Fishing[i]<-hh_pars[16]
  Generalists_Exp_Hyst_output_rev$Initial_Coral[i]<-C0
  Generalists_Exp_Hyst_output_rev$Final_Coral[i]<-tail(P2_output_new$Coral,1)
  Generalists_Exp_Hyst_output_rev$Final_Turf[i]<-tail(P2_output_new$Turf,1)
  Generalists_Exp_Hyst_output_rev$Final_Macroalgae[i]<-tail(P2_output_new$Macroalgae,1)
  Generalists_Exp_Hyst_output_rev$Final_Algae[i]<-tail(P2_output_new$Algae,1)
  Generalists_Exp_Hyst_output_rev$Final_Grazers[i]<-tail(P2_output_new$Grazers,1)
  Generalists_Exp_Hyst_output_rev$Final_Generalists[i]<-tail(P2_output_new$Generalists,1)
  Generalists_Exp_Hyst_output_rev$Final_Browsers[i]<-tail(P2_output_new$Browsers,1)
  Generalists_Exp_Hyst_output_rev$Final_Herbivores[i]<-tail(P2_output_new$Herbivores,1)
  Generalists_Exp_Hyst_output_rev$Final_Space[i]<-tail(P2_output_new$Space,1)
}

```


## Expanded Model Part 2c: High Grazers Scenario
# B0<-0.15
# R0<-0.15
# G0<-0.6

```{r Expanded Hysteresis High Grazers}

# Initial conditions for High Grazers Scenario
# B0<-0.15
# R0<-0.15
# G0<-0.6


# Set up a for loop to run lsoda for each fishing pressure
# Need to start each new run with where the system ENDED after the last run / loop

f_values<-seq(0,1,by=0.005)
P2_tseq<-seq(0,1000,by=0.1)

## set up a data frame to store the results I want
Grazers_Exp_Hyst_output<-data.frame(f_values)

# Set up for loop to run lsoda with different initial conditions & different fishing pressures
for(i in 1:length(f_values)){
  if(i==1){
    B0<-0.15
    R0<-0.15
    G0<-0.6
    C0<-0.75
    T0<-0.05
    M0<-0.05
    S0 <- 1 - T0 - C0 - M0
    }
  else{
    G0<-tail(P2_output_new$Grazers,1)
    R0<-tail(P2_output_new$Generalists,1)
    B0<-tail(P2_output_new$Browsers,1)
    C0<-tail(P2_output_new$Coral,1)
    T0<-tail(P2_output_new$Turf,1)
    M0<-tail(P2_output_new$Macroalgae,1)
    S0<-tail(P2_output_new$Space,1)
  }
  P2_state_vars<-c(GG=G0, RR=R0, BB=B0, CC=C0, TT=T0, MM=M0, SS=S0)
  hh_pars[16]<-f_values[i] # set fishing pressure
  P2_output<-lsoda(c(Grazers=G0, Generalists=R0, Browsers=B0,
                     Coral=C0, Turf=T0, Macroalgae=M0),
                 P2_tseq, P2_Model, hh_pars)
  P2_output_new<-as.data.frame(P2_output)
  P2_output_new$Space = 1 - P2_output_new$Coral - P2_output_new$Turf - P2_output_new$Macroalgae
  P2_output_new$Algae = P2_output_new$Turf + P2_output_new$Macroalgae
  P2_output_new$Herbivores = P2_output_new$Grazers + P2_output_new$Generalists + P2_output_new$Browsers
  
  
  Grazers_Exp_Hyst_output$Fishing[i]<-hh_pars[16]
  Grazers_Exp_Hyst_output$Initial_Coral[i]<-C0
  Grazers_Exp_Hyst_output$Final_Coral[i]<-tail(P2_output_new$Coral,1)
  Grazers_Exp_Hyst_output$Final_Turf[i]<-tail(P2_output_new$Turf,1)
  Grazers_Exp_Hyst_output$Final_Macroalgae[i]<-tail(P2_output_new$Macroalgae,1)
  Grazers_Exp_Hyst_output$Final_Algae[i]<-tail(P2_output_new$Algae,1)
  Grazers_Exp_Hyst_output$Final_Grazers[i]<-tail(P2_output_new$Grazers,1)
  Grazers_Exp_Hyst_output$Final_Generalists[i]<-tail(P2_output_new$Generalists,1)
  Grazers_Exp_Hyst_output$Final_Browsers[i]<-tail(P2_output_new$Browsers,1)
  Grazers_Exp_Hyst_output$Final_Herbivores[i]<-tail(P2_output_new$Herbivores,1)
  Grazers_Exp_Hyst_output$Final_Space[i]<-tail(P2_output_new$Space,1)
}




# Reversing the simulation

#f_values<-seq(0,1,by=0.005)
f_values_2<-rev(seq(0,1,by=0.005))
P2_tseq<-seq(0,1000,by=0.1)


## set up a data frame to store the results I want
Grazers_Exp_Hyst_output_rev<-data.frame(f_values_2)

# Set up for loop to run lsoda with different initial conditions & different fishing pressures
for(i in 1:length(f_values_2)){
  if(i==1){
    G0<-tail(Grazers_Exp_Hyst_output$Final_Grazers,1)
    R0<-tail(Grazers_Exp_Hyst_output$Final_Generalists,1)
    B0<-tail(Grazers_Exp_Hyst_output$Final_Browsers,1)
    C0<-tail(Grazers_Exp_Hyst_output$Final_Coral,1)
    T0<-tail(Grazers_Exp_Hyst_output$Final_Turf,1)
    M0<-tail(Grazers_Exp_Hyst_output$Final_Macroalgae,1)
    S0<-tail(Grazers_Exp_Hyst_output$Final_Space,1)
    # 
    # B0<-0.15
    # R0<-0.15
    # G0<-0.6
    # C0<-0.75
    # T0<-0.05
    # M0<-0.05
    # S0 <- 1 - T0 - C0 - M0
    }
  else{
    G0<-tail(P2_output_new$Grazers,1)
    R0<-tail(P2_output_new$Generalists,1)
    B0<-tail(P2_output_new$Browsers,1)
    C0<-tail(P2_output_new$Coral,1)
    T0<-tail(P2_output_new$Turf,1)
    M0<-tail(P2_output_new$Macroalgae,1)
    S0<-tail(P2_output_new$Space,1)
  }
  P2_state_vars<-c(GG=G0, RR=R0, BB=B0, CC=C0, TT=T0, MM=M0, SS=S0)
  hh_pars[16]<-f_values_2[i] # set fishing pressure
  P2_output<-lsoda(c(Grazers=G0, Generalists=R0, Browsers=B0,
                     Coral=C0, Turf=T0, Macroalgae=M0),
                 P2_tseq, P2_Model, hh_pars)
  P2_output_new<-as.data.frame(P2_output)
  P2_output_new$Space = 1 - P2_output_new$Coral - P2_output_new$Turf - P2_output_new$Macroalgae
  P2_output_new$Algae = P2_output_new$Turf + P2_output_new$Macroalgae
  P2_output_new$Herbivores = P2_output_new$Grazers + P2_output_new$Generalists + P2_output_new$Browsers
  
  
  Grazers_Exp_Hyst_output_rev$Fishing[i]<-hh_pars[16]
  Grazers_Exp_Hyst_output_rev$Initial_Coral[i]<-C0
  Grazers_Exp_Hyst_output_rev$Final_Coral[i]<-tail(P2_output_new$Coral,1)
  Grazers_Exp_Hyst_output_rev$Final_Turf[i]<-tail(P2_output_new$Turf,1)
  Grazers_Exp_Hyst_output_rev$Final_Macroalgae[i]<-tail(P2_output_new$Macroalgae,1)
  Grazers_Exp_Hyst_output_rev$Final_Algae[i]<-tail(P2_output_new$Algae,1)
  Grazers_Exp_Hyst_output_rev$Final_Grazers[i]<-tail(P2_output_new$Grazers,1)
  Grazers_Exp_Hyst_output_rev$Final_Generalists[i]<-tail(P2_output_new$Generalists,1)
  Grazers_Exp_Hyst_output_rev$Final_Browsers[i]<-tail(P2_output_new$Browsers,1)
  Grazers_Exp_Hyst_output_rev$Final_Herbivores[i]<-tail(P2_output_new$Herbivores,1)
  Grazers_Exp_Hyst_output_rev$Final_Space[i]<-tail(P2_output_new$Space,1)
}

```



## Configuring dataframes to be able to plot them all together easily with ggplot

```{r}

## Need to change the name of the first column in this data frame so all of the column names match up in the two data frames I am rbinding below
colnames(Exp_Hysteresis_output_real_rev)[1]<-"f_values"
colnames(Browsers_Exp_Hyst_output_rev)[1]<-"f_values"
colnames(Generalists_Exp_Hyst_output_rev)[1]<-"f_values"
colnames(Grazers_Exp_Hyst_output_rev)[1]<-"f_values"


# Row bind the various data frames in order to plot by them
Exp_Hysteresis_output_real$Id="Forward"
Exp_Hysteresis_output_real_rev$Id="Reverse"
Browsers_Exp_Hyst_output$Id="Forward"
Browsers_Exp_Hyst_output_rev$Id="Reverse"
Generalists_Exp_Hyst_output$Id="Forward"
Generalists_Exp_Hyst_output_rev$Id="Reverse"
Grazers_Exp_Hyst_output$Id="Forward"
Grazers_Exp_Hyst_output_rev$Id="Reverse"


# Add another column to identify which model is which for plotting in separate plots
Exp_Hysteresis_output_real$Type="E) Herbivore groups even"
Exp_Hysteresis_output_real_rev$Type="E) Herbivore groups even"
Browsers_Exp_Hyst_output$Type="G) Browser-dominated"
Browsers_Exp_Hyst_output_rev$Type="G) Browser-dominated"
Generalists_Exp_Hyst_output$Type="F) Generalist-dominated"
Generalists_Exp_Hyst_output_rev$Type="F) Generalist-dominated"
Grazers_Exp_Hyst_output$Type="H) Grazer-dominated"
Grazers_Exp_Hyst_output_rev$Type="H) Grazer-dominated"



# Row bind the various scenarios together
exp_hysteresis_all=rbind(Exp_Hysteresis_output_real, Exp_Hysteresis_output_real_rev,
                         Browsers_Exp_Hyst_output, Browsers_Exp_Hyst_output_rev,
                         Generalists_Exp_Hyst_output, Generalists_Exp_Hyst_output_rev,
                         Grazers_Exp_Hyst_output, Grazers_Exp_Hyst_output_rev)


# export simulation results to .csv file
write_csv(exp_hysteresis_all, file = "../../output/analyses/fig5/hysteresis_all.csv")

```


## Read .csv file produced from above code (to avoid having to rerun analyses)
```{r}

exp_hysteresis_all <- read_csv(file = "../../output/analyses/fig5/hysteresis_all.csv")

```





# Plotting the figures

```{r}

# Reorder factor levels to control order in figure 5. Generalists first, then browsers, then grazers.
exp_hysteresis_all$Type<-factor(exp_hysteresis_all$Type, levels=c("E) Herbivore groups even","F) Generalist-dominated","G) Browser-dominated","H) Grazer-dominated"))



# Save figure as a PDF file
pdf("../../output/figures/Fig_5B.pdf", width=2.5, height=8.5)

#quartz()
ggplot(data=exp_hysteresis_all, aes(x=Fishing, Final_Coral, group=Id, color=Id)) +
    geom_line(aes(size=Id)) +
    scale_color_manual(labels=c("Forward","Reverse"), values=c("red","black")) + 
    theme_classic(base_size=14, base_family = "Times") + 
    theme(axis.title=element_text(size=16, face="bold")) +
    scale_size_manual(values=c(2,1)) + 
    xlim(0,1) + 
    ylim(0,1) + 
    ylab("Coral Cover") +
    xlab("Fishing Pressure") +
    theme(legend.title=element_blank(),
          legend.position = c(0.75,0.965),
          legend.text=element_text(size=9),
          legend.background = element_rect(fill = "transparent")) +
    facet_wrap(~Type,nrow = 4) +
    theme(strip.text.x = element_text(size = 11))

# dev.off()

```

