---
title: "S14_ASS-sensitivity-analyses"
author: "Shayna A. Sura"
date: "2025-06-15"
output: pdf_document
---


```{r setup, include=FALSE}

library(deSolve)
library(reshape2)
library(viridis)
library(gridExtra)
library(tidyverse) # includes and loads the packages listed below
# library(readr)
# library(tidyr)
# library(dplyr)
# library(ggplot2)
# library(lubridate)

library(here) # helps with paths for files
library(purrr) # vectorized coding approaches for faster analyses
library(scales)
library(lemon) #for facet_rep_grid function for plotting
library(progress)  # for progress bar

```




# Our Model Set up
```{r source model code and parameters}

source("0.2_full_model.R")

```


#### parameter values used for model analyses for reference

```{r}

# #Generate a vector of parameter values - for our full / expanded model
# hh_pars<-c(bc<-0.3, bt<-0.8, bm<-0.5,     #expansion of current benthic cover
#            ic<-0.05, it<-0.05, im<-0,     #import of propagules
#            dc<-0.1,                       #coral mortality
#            r<-1,                          #herbivore growth rate
#            gt<-2, gm<-1,                  #algae mortality
#            etaT<-0, etaM<-1,              #algae handling time
#            alphaT<-0.25, alphaM<-0.5,     #competitive effect on coral
#            sigma<-0.6,                    #relationship between coral & herbivores
#            f<-0.5,                        #fishing pressure
#            gamma<-0.1)                    #transition from turf to macroalgae


```


# BROWSER-DOMINATED SCENARIO

# Alternative Stable States (ASS) Sensitivity Analyses 1
## Grazing rate on turf and macroalgae (gT and gM values)

```{r}

# Step 1 - Define Time Sequence and Input Ranges

# Time sequence for the model
P2_tseq <- seq(0, 1000, by = 0.1)

# Coral cover and fishing pressure combinations
f_values <- seq(0, 1, by = 0.01)
coral_initials <- seq(0, 0.85, 0.01)

# Grid of initial coral and fishing pressure
high_browsers_1 <- expand.grid(Initial_Coral = coral_initials, Fishing_Pressure = f_values)



# Step 2 - Prepare Parameter Combinations & Batching

# Create all (gt, gm) combinations where gt >= gm
param_grid <- expand.grid(gt = 0:8, gm = 0:8) %>%
  filter(gt >= gm)

# Define batch size and split param_grid
batch_size <- 2  # Adjust based on your machine
n_batches <- ceiling(nrow(param_grid) / batch_size)

# Create list of parameter batches
param_batches <- split(param_grid, rep(1:n_batches, each = batch_size, length.out = nrow(param_grid)))



# Step 3 - Define the Model Run Function
run_model <- function(initial_coral, fishing_pressure, gt, gm) {
  C0 <- initial_coral
  B0 <- 0.6
  R0 <- 0.15
  G0 <- 0.15
  S0 <- 0.15
  M0 <- (1 - C0 - S0) / 2
  T0 <- (1 - C0 - S0) / 2

  # Update the parameters — modify these indices if needed
  hh_pars_mod <- hh_pars
  hh_pars_mod[9] <- gt  # grazing mortality of turf
  hh_pars_mod[10] <- gm  # grazing mortality of macroalgae
  hh_pars_mod[16] <- fishing_pressure  # Fishing pressure

  # Run model
  zz_output <- lsoda(c(Grazers = G0, Generalists = R0, Browsers = B0,
                       Coral = C0, Turf = T0, Macroalgae = M0),
                     P2_tseq, P2_Model, hh_pars_mod)

  final_coral <- tail(as.data.frame(zz_output)$Coral, 1)
  return(final_coral)
}



# Step 4 - Run the batches
# Create progress bar
pb <- progress_bar$new(
  format = "Processing batch :current/:total [:bar] :percent in :elapsed ETA: :eta",
  total = n_batches,
  clear = FALSE,
  width = 60
)



results_all <- list()

for (i in seq_along(param_batches)) {
  pb$tick()  # Update progress bar
  
  batch <- param_batches[[i]]
  
  # Inner progress bar for (gt, gm) combos in this batch
  inner_pb <- progress_bar$new(
    format = "  gt/gm combo :current/:total [:bar] :percent in :elapsed ETA: :eta",
    total = nrow(batch),
    clear = FALSE,
    width = 60
  )
  
  
  # use map2_dfr to directly bind all the results into a single data frame
  batch_results <- map2_dfr(batch$gt, batch$gm, function(gt_val, gm_val) {
    inner_pb$tick()
    high_browsers_1 %>%
      mutate(Final_Coral = pmap_dbl(list(Initial_Coral, Fishing_Pressure),
                                    ~run_model(..1, ..2, gt_val, gm_val)),
             gt = gt_val,
             gm = gm_val)
  })
  
  results_all[[i]] <- batch_results
  # write.csv(batch_results, paste0("model_results_batch_", i, ".csv"), row.names = FALSE)
  
  # Save to output/analyses/supplement2/
  write.csv(batch_results,
            file = file.path("../output", "analyses", "supplement2", paste0("model_results_batch_", i, ".csv")),
            row.names = FALSE)
}




# Step 5 - Combine Final Results
gT_gM_all <- bind_rows(results_all)

# # Optional: write the full result
# write.csv(final_results, "model_results_all_batches.csv", row.names = FALSE)


```

# Write simulation results to .csv file

```{r}
# export complete simulation results to .csv file

write_csv(final_results, "../output/analyses/supplement2/gT_gM_results_all_batches.csv")

```


# Read in .csv file produced from above code (to avoid having to rerun analyses)
```{r}

gT_gM_all <- read_csv(file = "../../output/analyses/supplement2/gT_gM_results_all_batches")

```


# Plotting Results

```{r}

final_results <- gT_gM_all %>%
  mutate(
    gt_label = paste0("gT = ", gt),
    gm_label = paste0("gM = ", gm)
  )


# Define the custom color scale
custom_colors <- colorRampPalette(c("#FCF0D1", "#FAE8B7", "#FAC8AF", "#F9A7A6", "#F9879E", "#F86696", "#F8468D", "#f20089", "#e500a4", "#db00b6", "#b5179e", "#7209b7"))


# Create PDF
pdf("../output/figures/fig_S19_v1.pdf", width = 12, height = 10)

ggplot(data = final_results, aes(Fishing_Pressure, Initial_Coral)) +
  geom_tile(aes(fill = Final_Coral)) +
  theme_classic(base_size=14,base_family = "Times") + 
  theme(axis.title=element_text(size=16,face="bold")) +
  scale_fill_gradientn(colors = custom_colors(50), limits=c(0,0.8)) +
  scale_colour_gradientn(colors = custom_colors(50), limits=c(0,0.8)) +
  scale_x_continuous("Fishing Pressure",
                     expand = c(0, 0),
                     breaks = c(0,0.25,0.5,0.75,1),
                     labels = c(0,0.25,0.5,0.75,1)) +
  scale_y_continuous("Initial Coral Cover",
                     expand = c(0, 0),
                     breaks = c(0,0.2,0.4,0.6,0.8),
                     labels = c(0,0.2,0.4,0.6,0.8)) +
  guides(fill = guide_colorbar(title.position = "top",
                               title.hjust = 0.5,
                               label.hjust = 0.5,
                               barheight = unit(6, "lines"),
                               barwidth = unit(1, "lines"),
                               draw.ulim = FALSE,
                               draw.llim = FALSE,
                               frame.colour = "black",
                               ticks.colour = "black",
                               label.position = "right",
                               label.theme = element_text(size = 8),
                               title = "Final\nCoral\nCover",
                               title.theme = element_text(size = 11))) +
  facet_rep_grid(gt_label ~ gm_label) +
  theme(strip.text.x = element_text(size = 11))

dev.off()

```



# Browser-Dominated ASS Sensitivity Analyses 2
## Competitive effects of Turf and Macroalgae on Coral (alphaT and alphaM values)


```{r}

# Step 1 - Define Time Sequence and Input Ranges

# Time sequence for the model
P2_tseq <- seq(0, 1000, by = 0.1)

# Coral cover and fishing pressure combinations
f_values <- seq(0, 1, by = 0.02)
coral_initials <- seq(0, 0.85, 0.02)

# Grid of initial coral and fishing pressure
high_browsers_1 <- expand.grid(Initial_Coral = coral_initials, Fishing_Pressure = f_values)



# Step 2 - Prepare Parameter Combinations & Batching

# Create all (alphaT, alphaM) combinations where alphaM >= alphaT
alphaT_values <- seq(0.1, 0.7, by=0.1)
alphaM_values <- seq(0.1, 0.7, by=0.1)

alpha_initials <- expand.grid(alphaT = alphaT_values, alphaM = alphaM_values)

# Filter out rows where the alphaT values are greater than alphaM values - keep rows where alphaM >= alphaT
alpha_initials <- alpha_initials %>% 
  filter(alphaM >= alphaT)

param_grid <- alpha_initials


# Define batch size and split param_grid
batch_size <- 10  # Adjust based on your machine
n_batches <- ceiling(nrow(param_grid) / batch_size)

# Create list of parameter batches
param_batches <- split(param_grid, rep(1:n_batches, each = batch_size, length.out = nrow(param_grid)))



# Step 3 - Define the Model Run Function
run_model <- function(initial_coral, fishing_pressure, gt, gm) {
  C0 <- initial_coral
  B0 <- 0.6
  R0 <- 0.15
  G0 <- 0.15
  S0 <- 0.15
  M0 <- (1 - C0 - S0) / 2
  T0 <- (1 - C0 - S0) / 2

  # Update the parameters — modify these indices if needed
  hh_pars_mod <- hh_pars
  hh_pars_mod[13] <- alphaT  # set the alphaT values
  hh_pars_mod[14] <- alphaM  # set the alphaM values
  hh_pars_mod[16] <- fishing_pressure  # Fishing pressure

  # Run model
  zz_output <- lsoda(c(Grazers = G0, Generalists = R0, Browsers = B0,
                       Coral = C0, Turf = T0, Macroalgae = M0),
                     P2_tseq, P2_Model, hh_pars_mod)

  final_coral <- tail(as.data.frame(zz_output)$Coral, 1)
  return(final_coral)
}



# Step 4 - Run the batches
# Create progress bar
pb <- progress_bar$new(
  format = "Processing batch :current/:total [:bar] :percent in :elapsed ETA: :eta",
  total = n_batches,
  clear = FALSE,
  width = 60
)



results_all <- list()

for (i in seq_along(param_batches)) {
  pb$tick()  # Update progress bar
  
  batch <- param_batches[[i]]
  
  # Inner progress bar for (alphaT, alphaM) combos in this batch
  inner_pb <- progress_bar$new(
    format = "  alphaT/alphaM combo :current/:total [:bar] :percent in :elapsed ETA: :eta",
    total = nrow(batch),
    clear = FALSE,
    width = 60
  )
  
  
  # use map2_dfr to directly bind all the results into a single data frame
  batch_results <- map2_dfr(batch$alphaT, batch$alphaM, function(alphaT_val, alphaM_val) {
    inner_pb$tick()
    high_browsers_1 %>%
      mutate(Final_Coral = pmap_dbl(list(Initial_Coral, Fishing_Pressure),
                                    ~run_model(..1, ..2, alphaT_val, alphaM_val)),
             alphaT = alphaT_val,
             alphaM = alphaM_val)
  })
  
  results_all[[i]] <- batch_results
  
  # Save to output/analyses/supplement2/
  write.csv(batch_results,
            file = file.path("../output", "analyses", "supplement2", paste0("alphaT_alphaM_results_batch_", i, ".csv")),
            row.names = FALSE)
}




# Step 5 - Combine Final Results
alphaT_alphaM_all <- bind_rows(results_all)



```

# Write simulation results to .csv file

```{r}
# export complete simulation results to .csv file

write_csv(alphaT_alphaM_all, "../output/analyses/supplement2/alphaT_alphaM_results_all_batches.csv")

```


# Read in .csv file produced from above code (to avoid having to rerun analyses)
```{r}

alphaT_alphaM_all <- read_csv(file = "../../output/analyses/supplement2/alphaT_alphaM_results_all_batches")

```


# Plotting Results

```{r}

final_results <- alphaT_alphaM_all %>%
  mutate(
    alphaT_label = paste0("alphaT = ", alphaT),
    alphaM_label = paste0("alphaM = ", alphaM)
  )


# Define the custom color scale
custom_colors <- colorRampPalette(c("#FCF0D1", "#FAE8B7", "#FAC8AF", "#F9A7A6", "#F9879E", "#F86696", "#F8468D", "#f20089", "#e500a4", "#db00b6", "#b5179e", "#7209b7"))


# Create PDF
pdf("../output/figures/fig_S20_v1.pdf", width = 9, height = 12)

ggplot(data = final_results, aes(Fishing_Pressure, Initial_Coral)) +
  geom_tile(aes(fill = Final_Coral)) +
  theme_classic(base_size=14,base_family = "Times") + 
  theme(axis.title=element_text(size=16,face="bold")) +
  scale_fill_gradientn(colors = custom_colors(50), limits=c(0,0.8)) +
  scale_colour_gradientn(colors = custom_colors(50), limits=c(0,0.8)) +
  scale_x_continuous("Fishing Pressure",
                     expand = c(0, 0),
                     breaks = c(0,0.25,0.5,0.75,1),
                     labels = c(0,0.25,0.5,0.75,1)) +
  scale_y_continuous("Initial Coral Cover",
                     expand = c(0, 0),
                     breaks = c(0,0.2,0.4,0.6,0.8),
                     labels = c(0,0.2,0.4,0.6,0.8)) +
  guides(fill = guide_colorbar(title.position = "top",
                               title.hjust = 0.5,
                               label.hjust = 0.5,
                               barheight = unit(6, "lines"),
                               barwidth = unit(1, "lines"),
                               draw.ulim = FALSE,
                               draw.llim = FALSE,
                               frame.colour = "black",
                               ticks.colour = "black",
                               label.position = "right",
                               label.theme = element_text(size = 8),
                               title = "Final\nCoral\nCover",
                               title.theme = element_text(size = 11))) +
  facet_rep_grid(alphaT_label ~ alphaM_label) +
  theme(strip.text.x = element_text(size = 11))

dev.off()

```



# Browser-Dominated ASS Sensitivity Analyses 3
## Import of Turf and Coral Propagules (iT and iC values)


```{r}

# Step 1 - Define Time Sequence and Input Ranges

# Time sequence for the model
P2_tseq <- seq(0, 1000, by = 0.1)

# Coral cover and fishing pressure combinations
f_values <- seq(0, 1, by = 0.02)
coral_initials <- seq(0, 0.85, 0.02)

# Grid of initial coral and fishing pressure
high_browsers_1 <- expand.grid(Initial_Coral = coral_initials, Fishing_Pressure = f_values)



# Step 2 - Prepare Parameter Combinations & Batching

# Create all (iT, iC) combinations
iT_values <- seq(0, 0.3, by=0.05)
iC_values <- seq(0, 0.3, by=0.05)

iTiC_initials <- expand.grid(iT = iT_values, iC = iC_values)

# # Filter out rows where the alphaT values are greater than alphaM values - keep rows where alphaM >= alphaT
# alpha_initials <- alpha_initials %>% 
#   filter(alphaM >= alphaT)

param_grid <- iTiC_initials


# Define batch size and split param_grid
batch_size <- 2  # Adjust based on your machine
n_batches <- ceiling(nrow(param_grid) / batch_size)

# Create list of parameter batches
param_batches <- split(param_grid, rep(1:n_batches, each = batch_size, length.out = nrow(param_grid)))



# Step 3 - Define the Model Run Function
run_model <- function(initial_coral, fishing_pressure, iT, iC) {
  C0 <- initial_coral
  B0 <- 0.6
  R0 <- 0.15
  G0 <- 0.15
  S0 <- 0.15
  M0 <- (1 - C0 - S0) / 2
  T0 <- (1 - C0 - S0) / 2

  # Update the parameters — modify these indices if needed
  hh_pars_mod <- hh_pars
  hh_pars_mod[5] <- iT  # set the iT values
  hh_pars_mod[4] <- iC  # set the iC values
  hh_pars_mod[16] <- fishing_pressure  # Fishing pressure

  # Run model
  zz_output <- lsoda(c(Grazers = G0, Generalists = R0, Browsers = B0,
                       Coral = C0, Turf = T0, Macroalgae = M0),
                     P2_tseq, P2_Model, hh_pars_mod)

  final_coral <- tail(as.data.frame(zz_output)$Coral, 1)
  return(final_coral)
}



# Step 4 - Run the batches
# Create progress bar
pb <- progress_bar$new(
  format = "Processing batch :current/:total [:bar] :percent in :elapsed ETA: :eta",
  total = n_batches,
  clear = FALSE,
  width = 60
)



results_all <- list()

for (i in seq_along(param_batches)) {
  pb$tick()  # Update progress bar
  
  batch <- param_batches[[i]]
  
  # Inner progress bar for (iT, iC) combos in this batch
  inner_pb <- progress_bar$new(
    format = "  iT/iC combo :current/:total [:bar] :percent in :elapsed ETA: :eta",
    total = nrow(batch),
    clear = FALSE,
    width = 60
  )
  
  
  # use map2_dfr to directly bind all the results into a single data frame
  batch_results <- map2_dfr(batch$iT, batch$iC, function(iT_val, iC_val) {
    inner_pb$tick()
    high_browsers_1 %>%
      mutate(Final_Coral = pmap_dbl(list(Initial_Coral, Fishing_Pressure),
                                    ~run_model(..1, ..2, iT_val, iC_val)),
             iT = iT_val,
             iC = iC_val)
  })
  
  results_all[[i]] <- batch_results
  
  # Save to output/analyses/supplement2/
  write.csv(batch_results,
            file = file.path("../output", "analyses", "supplement2", paste0("browsers_iT_iC_results_batch_", i, ".csv")),
            row.names = FALSE)
}




# Step 5 - Combine Final Results
browsers_iT_iC_all <- bind_rows(results_all)



```

# Write simulation results to .csv file

```{r}
# export complete simulation results to .csv file

write_csv(browsers_iT_iC_all, "../output/analyses/supplement2/browsers_iT_iC_results_all_batches.csv")

```


# Read in .csv file produced from above code (to avoid having to rerun analyses)
```{r}

browsers_iT_iC_all <- read_csv(file = "../../output/analyses/supplement2/browsers_iT_iC_results_all_batches")

```


# Plotting Results

```{r}

final_results <- browsers_iT_iC_all %>%
  mutate(
    iT_label = paste0("iT = ", iT),
    iC_label = paste0("iC = ", iC)
  )


# Define the custom color scale
custom_colors <- colorRampPalette(c("#FCF0D1", "#FAE8B7", "#FAC8AF", "#F9A7A6", "#F9879E", "#F86696", "#F8468D", "#f20089", "#e500a4", "#db00b6", "#b5179e", "#7209b7"))


# Create PDF
pdf("../output/figures/fig_S23_browsers_iTiC_v1.pdf", width = 12, height = 10)

ggplot(data = final_results, aes(Fishing_Pressure, Initial_Coral)) +
  geom_tile(aes(fill = Final_Coral)) +
  theme_classic(base_size=14,base_family = "Times") + 
  theme(axis.title=element_text(size=16,face="bold")) +
  scale_fill_gradientn(colors = custom_colors(50), limits=c(0,1)) +
  scale_colour_gradientn(colors = custom_colors(50), limits=c(0,1)) +
  scale_x_continuous("Fishing Pressure",
                     expand = c(0, 0),
                     breaks = c(0,0.25,0.5,0.75,1),
                     labels = c(0,0.25,0.5,0.75,1)) +
  scale_y_continuous("Initial Coral Cover",
                     expand = c(0, 0),
                     breaks = c(0,0.2,0.4,0.6,0.8),
                     labels = c(0,0.2,0.4,0.6,0.8)) +
  guides(fill = guide_colorbar(title.position = "top",
                               title.hjust = 0.5,
                               label.hjust = 0.5,
                               barheight = unit(6, "lines"),
                               barwidth = unit(1, "lines"),
                               draw.ulim = FALSE,
                               draw.llim = FALSE,
                               frame.colour = "black",
                               ticks.colour = "black",
                               label.position = "right",
                               label.theme = element_text(size = 8),
                               title = "Final\nCoral\nCover",
                               title.theme = element_text(size = 11))) +
  facet_rep_grid(iT_label ~ iC_label) +
  theme(strip.text.x = element_text(size = 11))

dev.off()

```






# Browser-Dominated ASS Sensitivity Analyses 4
## Expansion of turf and macroalgae (betaT and betaM)

```{r}

# Step 1 - Define Time Sequence and Input Ranges

# Time sequence for the model
P2_tseq <- seq(0, 1000, by = 0.1)

# Coral cover and fishing pressure combinations
f_values <- seq(0, 1, by = 0.02)
coral_initials <- seq(0, 0.85, 0.02)

# Grid of initial coral and fishing pressure
high_browsers_1 <- expand.grid(Initial_Coral = coral_initials, Fishing_Pressure = f_values)



# Step 2 - Prepare Parameter Combinations & Batching

# Create all (betaT, betaM) combinations
betaT_values <- seq(0.3, 0.9, by=0.1)
betaM_values <- seq(0.3, 0.9, by=0.1)

beta_initials <- expand.grid(betaT = betaT_values, betaM = betaM_values)


# Filter to keep rows where the betaT values are greater than betaM values
beta_initials <- beta_initials %>% 
  filter(betaT >= betaM)

param_grid <- beta_initials


# Define batch size and split param_grid
batch_size <- 2  # Adjust based on your machine
n_batches <- ceiling(nrow(param_grid) / batch_size)

# Create list of parameter batches
param_batches <- split(param_grid, rep(1:n_batches, each = batch_size, length.out = nrow(param_grid)))



# Step 3 - Define the Model Run Function
run_model <- function(initial_coral, fishing_pressure, betaT, betaM) {
  C0 <- initial_coral
  B0 <- 0.6
  R0 <- 0.15
  G0 <- 0.15
  S0 <- 0.15
  M0 <- (1 - C0 - S0) / 2
  T0 <- (1 - C0 - S0) / 2

  # Update the parameters — modify these indices if needed
  hh_pars_mod <- hh_pars
  hh_pars_mod[2] <- betaT  # set the betaT values
  hh_pars_mod[3] <- betaM  # set the betaM values
  hh_pars_mod[16] <- fishing_pressure  # Fishing pressure

  # Run model
  zz_output <- lsoda(c(Grazers = G0, Generalists = R0, Browsers = B0,
                       Coral = C0, Turf = T0, Macroalgae = M0),
                     P2_tseq, P2_Model, hh_pars_mod)

  final_coral <- tail(as.data.frame(zz_output)$Coral, 1)
  return(final_coral)
}



# Step 4 - Run the batches
# Create progress bar
pb <- progress_bar$new(
  format = "Processing batch :current/:total [:bar] :percent in :elapsed ETA: :eta",
  total = n_batches,
  clear = FALSE,
  width = 60
)



results_all <- list()

for (i in seq_along(param_batches)) {
  pb$tick()  # Update progress bar
  
  batch <- param_batches[[i]]
  
  # Inner progress bar for (iT, iC) combos in this batch
  inner_pb <- progress_bar$new(
    format = "  betaT/betaM combo :current/:total [:bar] :percent in :elapsed ETA: :eta",
    total = nrow(batch),
    clear = FALSE,
    width = 60
  )
  
  
  # use map2_dfr to directly bind all the results into a single data frame
  batch_results <- map2_dfr(batch$betaT, batch$betaM, function(betaT_val, betaM_val) {
    inner_pb$tick()
    high_browsers_1 %>%
      mutate(Final_Coral = pmap_dbl(list(Initial_Coral, Fishing_Pressure),
                                    ~run_model(..1, ..2, betaT_val, betaM_val)),
             betaT = betaT_val,
             betaM = betaM_val)
  })
  
  results_all[[i]] <- batch_results
  
  # Save to output/analyses/supplement2/
  write.csv(batch_results,
            file = file.path("../output", "analyses", "supplement2", paste0("browsers_betaT_betaM_results_batch_", i, ".csv")),
            row.names = FALSE)
}




# Step 5 - Combine Final Results
browsers_betaT_betaM_all <- bind_rows(results_all)



```

# Write simulation results to .csv file

```{r}
# export complete simulation results to .csv file

write_csv(browsers_betaT_betaM_all, "../output/analyses/supplement2/browsers_betaT_betaM_results_all_batches.csv")

```


# Read in .csv file produced from above code (to avoid having to rerun analyses)
```{r}

browsers_betaT_betaM_all <- read_csv(file = "../../output/analyses/supplement2/browsers_betaT_betaM_results_all_batches")

```


# Plotting Results

```{r}

final_results <- browsers_betaT_betaM_all %>%
  mutate(
    betaT_label = paste0("betaT = ", betaT),
    betaM_label = paste0("betaM = ", betaM)
  )


# Define the custom color scale
custom_colors <- colorRampPalette(c("#FCF0D1", "#FAE8B7", "#FAC8AF", "#F9A7A6", "#F9879E", "#F86696", "#F8468D", "#f20089", "#e500a4", "#db00b6", "#b5179e", "#7209b7"))


# Create PDF
pdf("../output/figures/fig_S25_browsers_betaTbetaM_v1.pdf", width = 12, height = 10)

ggplot(data = final_results, aes(Fishing_Pressure, Initial_Coral)) +
  geom_tile(aes(fill = Final_Coral)) +
  theme_classic(base_size=14,base_family = "Times") + 
  theme(axis.title=element_text(size=16,face="bold")) +
  scale_fill_gradientn(colors = custom_colors(50), limits=c(0,0.8)) +
  scale_colour_gradientn(colors = custom_colors(50), limits=c(0,0.8)) +
  scale_x_continuous("Fishing Pressure",
                     expand = c(0, 0),
                     breaks = c(0,0.25,0.5,0.75,1),
                     labels = c(0,0.25,0.5,0.75,1)) +
  scale_y_continuous("Initial Coral Cover",
                     expand = c(0, 0),
                     breaks = c(0,0.2,0.4,0.6,0.8),
                     labels = c(0,0.2,0.4,0.6,0.8)) +
  guides(fill = guide_colorbar(title.position = "top",
                               title.hjust = 0.5,
                               label.hjust = 0.5,
                               barheight = unit(6, "lines"),
                               barwidth = unit(1, "lines"),
                               draw.ulim = FALSE,
                               draw.llim = FALSE,
                               frame.colour = "black",
                               ticks.colour = "black",
                               label.position = "right",
                               label.theme = element_text(size = 8),
                               title = "Final\nCoral\nCover",
                               title.theme = element_text(size = 11))) +
  facet_rep_grid(betaT_label ~ betaM_label) +
  theme(strip.text.x = element_text(size = 11))

dev.off()

```







# Browser-Dominated ASS Sensitivity Analyses 5
## transition probability of turf to macroalgae (gamma values) versus initial turf cover


```{r}

# Step 1 - Define Time Sequence and Input Ranges

# Time sequence for the model
P2_tseq <- seq(0, 1000, by = 0.1)

# Coral cover and fishing pressure combinations
f_values <- seq(0, 1, by = 0.02)
coral_initials <- seq(0, 0.85, 0.02)

# Grid of initial coral and fishing pressure
high_browsers_1 <- expand.grid(Initial_Coral = coral_initials, Fishing_Pressure = f_values)



# Step 2 - Prepare Parameter Combinations & Batching


# Create all parameter combinations (not necessary for gamma)
# betaT_values <- seq(0.3, 0.9, by=0.1)
# betaM_values <- seq(0.3, 0.9, by=0.1)
gamma_values <- seq(0, 0.6, by=0.05)

gamma_initials <- expand.grid(gamma = gamma_values)


param_grid <- gamma_initials


# Define batch size and split param_grid
batch_size <- 2  # Adjust based on your machine
n_batches <- ceiling(nrow(param_grid) / batch_size)

# Create list of parameter batches
param_batches <- split(param_grid, rep(1:n_batches, each = batch_size, length.out = nrow(param_grid)))



# Step 3 - Define the Model Run Function
run_model <- function(initial_coral, fishing_pressure, gamma) {
  C0 <- initial_coral
  B0 <- 0.6
  R0 <- 0.15
  G0 <- 0.15
  S0 <- 0.15
  M0 <- (1 - C0 - S0) / 2
  T0 <- (1 - C0 - S0) / 2

  # Update the parameters — modify these indices if needed
  hh_pars_mod <- hh_pars
  hh_pars_mod[16] <- fishing_pressure  # Fishing pressure
  hh_pars_mod[17] <- gamma  # set the gamma values

  # Run model
  zz_output <- lsoda(c(Grazers = G0, Generalists = R0, Browsers = B0,
                       Coral = C0, Turf = T0, Macroalgae = M0),
                     P2_tseq, P2_Model, hh_pars_mod)

  final_coral <- tail(as.data.frame(zz_output)$Coral, 1)
  return(final_coral)
}



# Step 4 - Run the batches
# Create progress bar
pb <- progress_bar$new(
  format = "Processing batch :current/:total [:bar] :percent in :elapsed ETA: :eta",
  total = n_batches,
  clear = FALSE,
  width = 60
)



results_all <- list()

for (i in seq_along(param_batches)) {
  pb$tick()  # Update progress bar
  
  batch <- param_batches[[i]]
  
  # Inner progress bar for gamma values in this batch
  inner_pb <- progress_bar$new(
    format = "  gamma :current/:total [:bar] :percent in :elapsed ETA: :eta",
    total = nrow(batch),
    clear = FALSE,
    width = 60
  )
  
  
  # use map2_dfr to directly bind all the results into a single data frame
  batch_results <- map_dfr(batch$gamma, function(gamma_val) {
    inner_pb$tick()
    high_browsers_1 %>%
      mutate(Final_Coral = pmap_dbl(list(Initial_Coral, Fishing_Pressure),
                                    ~run_model(..1, ..2, gamma_val)),
             gamma = gamma_val)
  })
  
  results_all[[i]] <- batch_results
  
  # Save to output/analyses/supplement2/
  write.csv(batch_results,
            file = file.path("../output", "analyses", "supplement2", paste0("browsers_gamma_results_batch_", i, ".csv")),
            row.names = FALSE)
}




# Step 5 - Combine Final Results
browsers_gamma_all <- bind_rows(results_all)



```

# Write simulation results to .csv file

```{r}
# export complete simulation results to .csv file

write_csv(browsers_gamma_all, "../output/analyses/supplement2/browsers_gamma_results_all_batches.csv")

```


# Read in .csv file produced from above code (to avoid having to rerun analyses)
```{r}

browsers_gamma_all <- read_csv(file = "../../output/analyses/supplement2/browsers_gamma_results_all_batches")

```


# Plotting Results

```{r}

final_results <- browsers_gamma_all %>%
  mutate(
    gamma_label = paste0("gamma = ", gamma)
  )


# Define the custom color scale
custom_colors <- colorRampPalette(c("#FCF0D1", "#FAE8B7", "#FAC8AF", "#F9A7A6", "#F9879E", "#F86696", "#F8468D", "#f20089", "#e500a4", "#db00b6", "#b5179e", "#7209b7"))


# Create PDF
pdf("../output/figures/fig_S27_browsers_gamma_v1.pdf", width = 12, height = 10)

ggplot(data = final_results, aes(Fishing_Pressure, Initial_Coral)) +
  geom_tile(aes(fill = Final_Coral)) +
  theme_classic(base_size=14,base_family = "Times") + 
  theme(axis.title=element_text(size=16,face="bold")) +
  scale_fill_gradientn(colors = custom_colors(50), limits=c(0,0.8)) +
  scale_colour_gradientn(colors = custom_colors(50), limits=c(0,0.8)) +
  scale_x_continuous("Fishing Pressure",
                     expand = c(0, 0),
                     breaks = c(0,0.25,0.5,0.75,1),
                     labels = c(0,0.25,0.5,0.75,1)) +
  scale_y_continuous("Initial Coral Cover",
                     expand = c(0, 0),
                     breaks = c(0,0.2,0.4,0.6,0.8),
                     labels = c(0,0.2,0.4,0.6,0.8)) +
  guides(fill = guide_colorbar(title.position = "top",
                               title.hjust = 0.5,
                               label.hjust = 0.5,
                               barheight = unit(6, "lines"),
                               barwidth = unit(1, "lines"),
                               draw.ulim = FALSE,
                               draw.llim = FALSE,
                               frame.colour = "black",
                               ticks.colour = "black",
                               label.position = "right",
                               label.theme = element_text(size = 8),
                               title = "Final\nCoral\nCover",
                               title.theme = element_text(size = 11))) +
  facet_rep_wrap(~gamma_label, ncol = 3) +
  theme(strip.text.x = element_text(size = 11))

dev.off()

```





