---
title: "Supplemental Figure S2 - Bistability for Recreated vdL ('basic') model"
author: "Shayna A. Sura"
date: "07/13/2024 - July 13, 2024"
output: pdf_document
---


```{r setup, echo=FALSE}

library(deSolve)
library(reshape2)
library(viridis)
library(gridExtra)
library(tidyverse) # includes and loads the packages listed below
# library(readr)
# library(tidyr)
# library(dplyr)
# library(ggplot2)
# library(lubridate)

library(here) # helps with paths for files
library(purrr) # vectorized coding approaches for faster analyses
library(scales)


```


# Recreation of van de Leemput (vdL) et al. (2016) model set up (aka 'basic' model)
```{r source model code and parameters}

source("0.1_basic_model.R")

```


## Basic Model Bistability - vectorized approach for evaluating
```{r}
## Basic Model

tseq <- seq(0, 1000, by=0.1)

f_values <- seq(0, 1, by = 0.01)
coral_initials <- seq(0, 0.85, 0.01)

basic_1 <- expand.grid(coral_initials,f_values)
colnames(basic_1) <- c("Initial_Coral","Fishing_Pressure")


# Function to run the model and extract the final coral value
run_model <- function(initial_coral, fishing_pressure) {
  C0 <- initial_coral
  H0<-0.9
  S0<-0.15
  A0<-1-C0-S0

  
  # Update fishing pressure in parameters
  pars[11] <- fishing_pressure
  
  # Run the model
  dd_output <- lsoda(c(Herbivores=H0,Coral=C0,Algae=A0), tseq, Basic_Model, pars)

  
  # Extract the final coral value
  final_coral <- tail(as.data.frame(dd_output)$Coral, 1)
  return(final_coral)
}

basic_1 <- basic_1 %>%
  mutate(Final_Coral = pmap_dbl(list(Initial_Coral, Fishing_Pressure), run_model))

# basic_1

```


### Export model simulation results as .csv file 
```{r}

# export simulation results to .csv file
write_csv(basic_1, file = "../../output/analyses/supplement/bistability-basic_1.csv")

```


### Read in .csv file containing results from model simulation (to avoid having to rerun the above analysis).
```{r}

basic_1 <- read_csv(file = "../../output/analyses/supplement/bistability-basic_1.csv")

```


### Determine the range of fishing pressure values for which bistability exists.
```{r}

## Determine which fishing pressure values the coral reef system exhibits bistability depending upon the initial coral cover conditions.
basic_C0_0 <- subset(basic_1,subset = basic_1$Initial_Coral == 0)
basic_C0_0.85 <- subset(basic_1,subset = basic_1$Initial_Coral == 0.85)

for(i in 1:nrow(basic_C0_0)){
  basic_C0_0$bistability[i] <- format(round(basic_C0_0[i,3], 7), nsmall = 7) != 
                     format(round(basic_C0_0.85[i,3], 7), nsmall = 7)
}


## Find the fishing pressure values where the system can exhibit bistability
min(basic_C0_0$Fishing_Pressure[which(basic_C0_0$bistability==TRUE)])
max(basic_C0_0$Fishing_Pressure[which(basic_C0_0$bistability==TRUE)])
basic_C0_0$Fishing_Pressure[which(basic_C0_0$bistability==TRUE)]
## bistability between 0.33 - 0.51

```


### Make a figure of the results
```{r}

custom_colors <- colorRampPalette(c("#FCF0D1", "#FAE8B7", "#FAC8AF", "#F9A7A6", "#F9879E", "#F86696", "#F8468D", "#f20089", "#e500a4", "#db00b6", "#b5179e", "#7209b7"))


# Save a PDF file of the figure
pdf("../../output/figures/fig_S2.pdf",width=4,height=3)

ggplot(basic_1, aes(Fishing_Pressure, Initial_Coral)) +
  geom_tile(aes(fill = Final_Coral)) +
  theme_classic(base_size=12,base_family = "Times") + 
  theme(axis.title=element_text(size=14,face="bold")) +
  labs(fill = "Final\nCoral\nCover") +
  scale_fill_gradientn(colors = custom_colors(50), limits=c(0,0.8)) +
  scale_colour_gradientn(colors = custom_colors(50), limits=c(0,0.8)) +
  scale_x_continuous("Fishing Pressure",
                     expand = c(0, 0),
                     breaks = c(0,0.25,0.5,0.75,1),
                     labels = c(0,0.25,0.5,0.75,1)) +
  scale_y_continuous("Initial Coral Cover",
                     expand = c(0, 0),
                     breaks = c(0,0.2,0.4,0.6,0.8),
                     labels = c(0,0.2,0.4,0.6,0.8))


```





