---
title: "Supplemental Figure S9 - Bistability & Hysteresis"
author: "Shayna A. Sura"
date: "07/13/2024 - July 13, 2024"
output: pdf_document
---

```{r setup, echo=FALSE}

library(deSolve)
library(reshape2)
library(viridis)
library(gridExtra)
library(tidyverse) # includes and loads the packages listed below
# library(readr)
# library(tidyr)
# library(dplyr)
# library(ggplot2)
# library(lubridate)

library(here) # helps with paths for files
library(purrr)
library(future)
library(furrr)
library(scales)

```


# Our Model Set up
```{r source model code and parameters}

source("0.2_full_model.R")

```



# Collapsed Model - Bistability Evaluation

## For loops over different initial coral cover for various levels of fishing pressure using the expanded model but with the parameters and initial conditions that allow it to collapse to the basic model
```{r, eval=FALSE}
#change eval to TRUE if want to run these model simulations versus reading in the output data

#generate a series of times at which you want the ODE solver to output population sizes
P2_tseq<-seq(0,1000,by=0.1)


# set fishing pressure values to evaluate
f_values<-seq(0,1,by=0.01)

# set initial coral cover conditions to evaluate
coral_initials<-seq(0,0.85,0.01)

# combine the values of fishing pressure and coral cover to evaluate
collapsed_1<-expand.grid(coral_initials,f_values)
colnames(collapsed_1)<-c("Initial_Coral","Fishing_Pressure")


for(i in 1:length(collapsed_1$Initial_Coral)){
    C0<-collapsed_1$Initial_Coral[i]
    B0<-0.45
    R0<-0
    G0<-0.45
#    C0<-0.75
    S0<-0.15
    M0<-(1-C0-S0)/2
    T0<-(1-C0-S0)/2
    P2_pars[16]<-collapsed_1$Fishing_Pressure[i]   #set the fishing pressure
    zz_output<-lsoda(c(Grazers =G0, Generalists =R0, Browsers =B0,
                   Coral = C0,Turf = T0,Macroalgae=M0),
                 P2_tseq, P2_Model, P2_pars)
    zz_output_new<-as.data.frame(zz_output)
    collapsed_1$Final_Coral[i]<-tail(zz_output_new$Coral,1)
}

```



### Write .csv file containing results from model simulation
```{r}

# export simulation results to .csv file
write_csv(collapsed_1, file = "../../output/analyses/supplement/bistability-collapsed_1.csv")

```



### Read in .csv file containing results from model simulation (to avoid having to rerun the above analysis).
```{r}

collapsed_1 <- read_csv(file = "../../output/analyses/supplement/bistability-collapsed_1.csv")

```


### Determine the range of fishing pressure values for which bistability exists.
```{r}

## Determine which fishing pressure values the coral reef system exhibits bistability depending upon the initial coral cover conditions.
coll_C0_0<-subset(collapsed_1,subset = collapsed_1$Initial_Coral == 0)
coll_C0_0.85<-subset(collapsed_1,subset = collapsed_1$Initial_Coral == 0.85)

for(i in 1:nrow(coll_C0_0)){
  coll_C0_0$bistability[i]<-format(round(coll_C0_0[i,3], 7), nsmall = 7) != 
                     format(round(coll_C0_0.85[i,3], 7), nsmall = 7)
}


## Find the fishing pressure values where the system can exhibit bistability
min(coll_C0_0$Fishing_Pressure[which(coll_C0_0$bistability==TRUE)])
max(coll_C0_0$Fishing_Pressure[which(coll_C0_0$bistability==TRUE)])
coll_C0_0$Fishing_Pressure[which(coll_C0_0$bistability==TRUE)]
## bistability between 0.33 - 0.51
```


### Make a figure of the results.
```{r}


# custom_colors <- colorRampPalette(c("#FAE8B7", "#FAC8AF", "#F9A7A6", "#F9879E", "#F86696", "#F8468D", "#f20089", "#e500a4", "#db00b6", "#b5179e", "#7209b7"))

custom_colors <- colorRampPalette(c("#FCF0D1", "#FAE8B7", "#FAC8AF", "#F9A7A6", "#F9879E", "#F86696", "#F8468D", "#f20089", "#e500a4", "#db00b6", "#b5179e", "#7209b7"))


# Save a PDF file of the figure
pdf("../../output/figures/fig_S9_A.pdf", width=4, height=3.25)

ggplot(collapsed_1, aes(Fishing_Pressure, Initial_Coral)) +
  geom_tile(aes(fill = Final_Coral)) +
  labs(fill = "Final\nCoral\nCover") +
  scale_fill_gradientn(colors = custom_colors(50), limits=c(0,0.9)) +
  scale_colour_gradientn(colors = custom_colors(50), limits=c(0,0.9)) +
  scale_x_continuous("Fishing Pressure",
                     expand = c(0, 0),
                     breaks = c(0,0.25,0.5,0.75,1),
                     labels = c(0,0.25,0.5,0.75,1)) +
  scale_y_continuous("Initial Coral Cover",
                     expand = c(0, 0),
                     breaks = c(0,0.2,0.4,0.6,0.8),
                     labels = c(0,0.2,0.4,0.6,0.8)) +
  theme_classic(base_size=12,base_family = "Times") +
  ggtitle("A) Collapsed") +
  theme(plot.title=element_text(size=16, face="bold", hjust=0.5)) +
  theme(axis.title=element_text(size=14,face="bold"))


# dev.off()


```







# Hysteresis for 'collapsed' model

```{r}
# Set up a for loop to run lsoda for each fishing pressure
# Need to start each new run with where the system ENDED after the last run / loop

f_values <- seq(0, 1, by=0.005)
P2_tseq <- seq(0, 1000, by=0.1)


## set up a data frame to store the results I want
Exp_Hysteresis_output<-data.frame(f_values)

# Set up for loop to run lsoda with different initial conditions & different fishing pressures
for(i in 1:length(f_values)){
  if(i==1){
    G0<-0.45
    R0<-0
    B0<-0.45
    C0<-0.75
    T0<-0.05
    M0<-0.05
    S0 <- 1 - T0 - C0 - M0
    }
  else{
    G0<-tail(P2_output_new$Grazers,1)
    R0<-tail(P2_output_new$Generalists,1)
    B0<-tail(P2_output_new$Browsers,1)
    C0<-tail(P2_output_new$Coral,1)
    T0<-tail(P2_output_new$Turf,1)
    M0<-tail(P2_output_new$Macroalgae,1)
    S0<-tail(P2_output_new$Space,1)
  }
  P2_state_vars<-c(GG=G0, RR=R0, BB=B0, CC=C0, TT=T0, MM=M0, SS=S0)
  P2_pars[16]<-f_values[i] # set fishing pressure
  P2_output<-lsoda(c(Grazers=G0, Generalists=R0, Browsers=B0,
                     Coral=C0, Turf=T0, Macroalgae=M0),
                 P2_tseq, P2_Model, P2_pars)
  P2_output_new<-as.data.frame(P2_output)
  P2_output_new$Space = 1 - P2_output_new$Coral - P2_output_new$Turf - P2_output_new$Macroalgae
  P2_output_new$Algae = P2_output_new$Turf + P2_output_new$Macroalgae
  P2_output_new$Herbivores = P2_output_new$Grazers + P2_output_new$Generalists + P2_output_new$Browsers
  
  
  Exp_Hysteresis_output$Fishing[i]<-P2_pars[16]
  Exp_Hysteresis_output$Initial_Coral[i]<-C0
  Exp_Hysteresis_output$Final_Coral[i]<-tail(P2_output_new$Coral,1)
  Exp_Hysteresis_output$Final_Turf[i]<-tail(P2_output_new$Turf,1)
  Exp_Hysteresis_output$Final_Macroalgae[i]<-tail(P2_output_new$Macroalgae,1)
  Exp_Hysteresis_output$Final_Algae[i]<-tail(P2_output_new$Algae,1)
  Exp_Hysteresis_output$Final_Grazers[i]<-tail(P2_output_new$Grazers,1)
  Exp_Hysteresis_output$Final_Generalists[i]<-tail(P2_output_new$Generalists,1)
  Exp_Hysteresis_output$Final_Browsers[i]<-tail(P2_output_new$Browsers,1)
  Exp_Hysteresis_output$Final_Herbivores[i]<-tail(P2_output_new$Herbivores,1)
  Exp_Hysteresis_output$Final_Space[i]<-tail(P2_output_new$Space,1)
}

```



## Running the simulations backwards now
```{r}

# Reversing the simulation

#f_values<-seq(0,1,by=0.005)
f_values_2<-rev(seq(0,1,by=0.005))
P2_tseq<-seq(0,1000,by=0.1)


## set up a data frame to store the results I want
Exp_Hysteresis_output_Rev<-data.frame(f_values_2)

# Set up for loop to run lsoda with different initial conditions & different fishing pressures
for(i in 1:length(f_values_2)){
  if(i==1){
    G0<-tail(Exp_Hysteresis_output$Final_Grazers,1)
    R0<-tail(Exp_Hysteresis_output$Final_Generalists,1)
    B0<-tail(Exp_Hysteresis_output$Final_Browsers,1)
    C0<-tail(Exp_Hysteresis_output$Final_Coral,1)
    T0<-tail(Exp_Hysteresis_output$Final_Turf,1)
    M0<-tail(Exp_Hysteresis_output$Final_Macroalgae,1)
    S0<-tail(Exp_Hysteresis_output$Final_Space,1)
    
    # G0<-0.45
    # R0<-0
    # B0<-0.45
    # C0<-0.75
    # T0<-0.05
    # M0<-0.05
    # S0 <- 1 - T0 - C0 - M0
    }
  else{
    G0<-tail(P2_output_new$Grazers,1)
    R0<-tail(P2_output_new$Generalists,1)
    B0<-tail(P2_output_new$Browsers,1)
    C0<-tail(P2_output_new$Coral,1)
    T0<-tail(P2_output_new$Turf,1)
    M0<-tail(P2_output_new$Macroalgae,1)
    S0<-tail(P2_output_new$Space,1)
  }
  P2_state_vars<-c(GG=G0, RR=R0, BB=B0, CC=C0, TT=T0, MM=M0, SS=S0)
  P2_pars[16]<-f_values_2[i] # set fishing pressure
  P2_output<-lsoda(c(Grazers=G0, Generalists=R0, Browsers=B0,
                     Coral=C0, Turf=T0, Macroalgae=M0),
                 P2_tseq, P2_Model, P2_pars)
  P2_output_new<-as.data.frame(P2_output)
  P2_output_new$Space = 1 - P2_output_new$Coral - P2_output_new$Turf - P2_output_new$Macroalgae
  P2_output_new$Algae = P2_output_new$Turf + P2_output_new$Macroalgae
  P2_output_new$Herbivores = P2_output_new$Grazers + P2_output_new$Generalists + P2_output_new$Browsers
  
  
  Exp_Hysteresis_output_Rev$Fishing[i]<-P2_pars[16]
  Exp_Hysteresis_output_Rev$Initial_Coral[i]<-C0
  Exp_Hysteresis_output_Rev$Final_Coral[i]<-tail(P2_output_new$Coral,1)
  Exp_Hysteresis_output_Rev$Final_Turf[i]<-tail(P2_output_new$Turf,1)
  Exp_Hysteresis_output_Rev$Final_Macroalgae[i]<-tail(P2_output_new$Macroalgae,1)
  Exp_Hysteresis_output_Rev$Final_Algae[i]<-tail(P2_output_new$Algae,1)
  Exp_Hysteresis_output_Rev$Final_Grazers[i]<-tail(P2_output_new$Grazers,1)
  Exp_Hysteresis_output_Rev$Final_Generalists[i]<-tail(P2_output_new$Generalists,1)
  Exp_Hysteresis_output_Rev$Final_Browsers[i]<-tail(P2_output_new$Browsers,1)
  Exp_Hysteresis_output_Rev$Final_Herbivores[i]<-tail(P2_output_new$Herbivores,1)
  Exp_Hysteresis_output_Rev$Final_Space[i]<-tail(P2_output_new$Space,1)
}

```



```{r}
## Change the name of the first column in this data frame so all of the column names match up in the two data frames I am rbinding below
colnames(Exp_Hysteresis_output)[1]<-"f_values"
colnames(Exp_Hysteresis_output_Rev)[1]<-"f_values"


# Row bind the various data frames in order to plot by them
Exp_Hysteresis_output$Id="Forward"
Exp_Hysteresis_output_Rev$Id="Reverse"

collapsed_1_hysteresis <- rbind(Exp_Hysteresis_output, Exp_Hysteresis_output_Rev)

# export simulation results to .csv file
write_csv(collapsed_1_hysteresis, file = "../../output/analyses/supplement/collapsed_1_hysteresis.csv")

```



## Read .csv file produced from above code (to avoid having to rerun analyses)
```{r}

collapsed_1_hysteresis <- read_csv(file = "../../output/analyses/supplement/collapsed_1_hysteresis.csv")

```



```{r}

# Save figure as a PDF file
pdf("../../output/figures/fig_S9_B.pdf", width=3, height=3.25)

#quartz()
ggplot(data=collapsed_1_hysteresis, aes(x=Fishing, Final_Coral, group=Id, color=Id)) +
    geom_line(aes(size=Id)) +
    scale_color_manual(labels=c("Forward","Reverse"), values=c("red","black")) + 
    theme_classic(base_size=14,base_family = "Times") + 
    theme(axis.title=element_text(size=16,face="bold")) +
    scale_size_manual(values=c(2,1)) + 
    xlim(0,1) + 
    ylim(0,1) + 
    ylab("Coral Cover") +
    xlab("Fishing Pressure") +
    ggtitle("B) Collapsed") +
    theme(plot.title=element_text(size=16,face="bold",hjust=0.5)) +
    theme(legend.title=element_blank(), legend.position = c(0.7,0.9),
          legend.text=element_text(size=11),
          legend.background = element_rect(fill = "transparent")) + 
    theme(strip.text.x = element_text(size = 11)) 


```



