---
title: "NEW_Time_Series_December_2021"
author: "Shayna Sura"
date: "12/9/2021 - December 9, 2021"
output: pdf_document
---

## Creating some time series showing scenarios that end up with different final conditions - e.g., high final coral cover vs. high final macroalgal cover vs. high final turf cover...

# Expanded Model

```{r Expanded Model Set up}
#These were the initial conditions for the basic model when I first ran that...
# H0<-0.9
# C0<-0.75
# M0<-0.1


G0<-0.3
R0<-0.3
B0<-0.3
C0<-0.75
T0<-0.05
M0<-0.05
S0 <- 1 - T0 - C0 - M0

P2_state_vars<-c(GG=G0, RR=R0, BB=B0, CC=C0, TT=T0, MM=M0, SS=S0)

#generate a series of times at which you want the ODE solver to output population sizes
P2_tseq<-seq(0,1000,by=0.1)

#Generate a vector of parameter values
P2_pars<-c(bc<-0.3,
           bt<-0.8,      #use the same value as bm from basic model
           bm<-0.8,      #use the same value as bm from basic model
           ic<-0.05,
           it<-0.025,    #need two of these, one for turf and one for macroalgae
           im<-0.025,    #need two of these, one for turf and one for macroalgae
           dc<-0.1,
           r<-1,
           # gt<-1,       #need two of these, one for turf and one for macroalgae
           # gm<-1,       #need two of these, one for turf and one for macroalgae
           gt<-2,       #need two of these, one for turf and one for macroalgae
           gm<-2,       #need two of these, one for turf and one for macroalgae
           etaT<-1,     #need two of these, one for turf and one for macroalgae
           etaM<-1,     #need two of these, one for turf and one for macroalgae
           alphaT<-0.5,
           alphaM<-0.5,
           sigma<-0.6,
           f<-0.1,
           gamma<-0)

P2_Model<-function(P2_tseq,P2_state_vars,P2_pars){
  GG <- P2_state_vars[1]
  RR <- P2_state_vars[2]
  BB <- P2_state_vars[3]
  CC <- P2_state_vars[4]
  TT <- P2_state_vars[5]
  MM <- P2_state_vars[6]
  SS <- 1 - CC - TT - MM
  
  bc <- P2_pars[1]
  bt <- P2_pars[2]
  bm <- P2_pars[3]
  ic <- P2_pars[4]
  it <- P2_pars[5]
  im <- P2_pars[6]
  dc <- P2_pars[7]
  r <- P2_pars[8]
  gt <- P2_pars[9]
  gm <- P2_pars[10]
  etaT <- P2_pars[11]
  etaM <- P2_pars[12]
  alphaT <- P2_pars[13]
  alphaM <- P2_pars[14]
  sigma <- P2_pars[15]
  f <- P2_pars[16]
  gamma <- P2_pars[17]
  
  dG_dt <-r*GG*(1 - ((GG+RR+BB) / ((1-sigma) + sigma*CC))) - f*GG
  dR_dt <-r*RR*(1 - ((GG+RR+BB) / ((1-sigma) + sigma*CC))) - f*RR
  dB_dt <-r*BB*(1 - ((GG+RR+BB) / ((1-sigma) + sigma*CC))) - f*BB
  dC_dt <- (ic + bc*CC)*SS*(1-(alphaT*TT+alphaM*MM)) - dc*CC
  dT_dt <- (it + bt*TT)*(SS) - (gamma*TT) - (((gt*GG*TT) / (gt*etaT*TT+1)) + ((gt*RR*TT)/(gt*etaT*TT+gm*etaM*MM+1)))
  dM_dt <- (im + bm*MM)*(SS) + (gamma*TT) - (((gm*BB*MM) / (gm*etaM*MM+1)) + ((gm*RR*MM)/(gt*etaT*TT+gm*etaM*MM+1)))


  return(list(c(dG <- dG_dt,
                dR <- dR_dt,
                dB <- dB_dt,
                dC <- dC_dt,
                dT <- dT_dt,
                dM <- dM_dt)))
}

P2_output<-lsoda(c(Grazers =G0, Generalists =R0, Browsers =B0,
                   Coral = C0,Turf = T0,Macroalgae=M0),
                 P2_tseq, P2_Model, P2_pars)
P2_output=as.data.frame(P2_output)

#head(P2_output)
#tail(P2_output)

P2_output$Space= 1 - P2_output$Coral - P2_output$Turf - P2_output$Macroalgae
P2_output$Herbivores = P2_output$Grazers+P2_output$Generalists+P2_output$Browsers
P2_output$Algae = P2_output$Turf+P2_output$Macroalgae


```



## Expanded Model Initial Conditions & Parameters

```{r}
#Generate a vector of parameter values
hh_pars<-c(bc<-0.3, bt<-0.8,bm<-0.5,      #expansion of current benthic cover
           ic<-0.05, it<-0.05, im<-0,     #import of propagules
           dc<-0.1,                       #coral mortality
           r<-1,                          #herbivore growth rate
#           gt<-1, gm<-0.5,                #algae mortality - used previously before changing our model equations
           gt<-2, gm<-1,                #algae mortality
           etaT<-0, etaM<-1,              #algae handling time
           alphaT<-0.25, alphaM<-0.5,     #competitive effect on coral
           sigma<-0.6,                    #relationship between coral & herbivores
           f<-0.5,                        #fishing pressure
           gamma<-0.1)                    #transition from turf to macroalgae

```


## Scenarios to examine over time
# Use the initial conditions from our Q1 analyses

```{r}

# General Initial conditions
G0<-0.3
R0<-0.3
B0<-0.3
C0<-0.75
T0<-0.1
M0<-0.0
S0 <- 1 - T0 - C0 - M0


# Initial conditions from Q2
C0<-0.15
M0<-0.0
T0<-0.7
S0<-1-C0-M0-T0
#Q2 examines varying initial herbivore abundances


## Scenario 1 - Final Turf Cover is High
#What initial conditions do we want to examine?
C0<-0.15
M0<-0.0
T0<-0.7
S0<-1-C0-M0-T0

#herbivore initial abundances
G0<-0.1
R0<-0
B0<-0.8

#set fishing pressure to 0
hh_pars[16] = 0

sc_1<-lsoda(c(Grazers =G0, Generalists =R0, Browsers =B0,
                   Coral = C0, Turf = T0, Macroalgae=M0),
                   P2_tseq, P2_Model, hh_pars)
sc_1=as.data.frame(sc_1)
sc_1$Space= 1 - sc_1$Coral - sc_1$Turf - sc_1$Macroalgae
sc_1$Herbivores = sc_1$Grazers+sc_1$Generalists+sc_1$Browsers
sc_1$Algae = sc_1$Turf+sc_1$Macroalgae

```


## Scenario 2 - Final Macroalgal Cover is High

```{r Scenario 2}

## Scenario 2 - Final Macroalgal Cover is High
#What initial conditions do we want to examine?
C0<-0.15
M0<-0.0
T0<-0.7
S0<-1-C0-M0-T0

#herbivore initial abundances
G0<-0.8
R0<-0
B0<-0.1

#set fishing pressure to 0
hh_pars[16] = 0

sc_2<-lsoda(c(Grazers =G0, Generalists =R0, Browsers =B0,
                   Coral = C0, Turf = T0, Macroalgae=M0),
                   P2_tseq, P2_Model, hh_pars)
sc_2=as.data.frame(sc_2)
sc_2$Space= 1 - sc_2$Coral - sc_2$Turf - sc_2$Macroalgae
sc_2$Herbivores = sc_2$Grazers+sc_2$Generalists+sc_2$Browsers
sc_2$Algae = sc_2$Turf+sc_2$Macroalgae

```


## Scenario 3 - Final Coral Cover is High

```{r Scenario 3}

## Scenario 3 - Final Coral Cover is High
#What initial conditions do we want to examine?
C0<-0.15
M0<-0.0
T0<-0.7
S0<-1-C0-M0-T0

#herbivore initial abundances
G0<-0.45
R0<-0
B0<-0.45

#set fishing pressure to 0
hh_pars[16] = 0

sc_3<-lsoda(c(Grazers =G0, Generalists =R0, Browsers =B0,
                   Coral = C0, Turf = T0, Macroalgae=M0),
                   P2_tseq, P2_Model, hh_pars)
sc_3=as.data.frame(sc_3)
sc_3$Space= 1 - sc_3$Coral - sc_3$Turf - sc_3$Macroalgae
sc_3$Herbivores = sc_3$Grazers+sc_3$Generalists+sc_3$Browsers
sc_3$Algae = sc_3$Turf+sc_3$Macroalgae

```


```{r Making Figures}
# Need to reduce the number of data points to plot so the points are actually visible
## subset time points at which to actually plot output....

group1_times<-seq(0,1000,by=10)
group2_times<-seq(7,1000,by=10)
group3_times<-seq(3,1000,by=10)
group4_times<-seq(0,1000,by=22)
group5_times<-seq(7,1000,by=22)
group6_times<-seq(14,1000,by=22)


#Panel A response variables
panelA_1<-subset(sc_1,sc_1$time %in% group1_times) #coral, algae
panelA_2<-subset(sc_1,sc_1$time %in% group2_times) #herbivores, turf
panelA_3<-subset(sc_1,sc_1$time %in% group3_times) #macroalgae
panelA_4<-subset(sc_1,sc_1$time %in% group4_times) #generalists
panelA_5<-subset(sc_1,sc_1$time %in% group5_times) #browsers
panelA_6<-subset(sc_1,sc_1$time %in% group6_times) #grazers


#Panel B response variables
panelB_1<-subset(sc_2,sc_2$time %in% group1_times) #coral, algae
panelB_2<-subset(sc_2,sc_2$time %in% group2_times) #herbivores, turf
panelB_3<-subset(sc_2,sc_2$time %in% group3_times) #macroalgae
panelB_4<-subset(sc_2,sc_2$time %in% group4_times) #generalists
panelB_5<-subset(sc_2,sc_2$time %in% group5_times) #browsers
panelB_6<-subset(sc_2,sc_2$time %in% group6_times) #grazers


#Panel C response variables
panelC_1<-subset(sc_3,sc_3$time %in% group1_times) #coral, algae
panelC_2<-subset(sc_3,sc_3$time %in% group2_times) #herbivores, turf
panelC_3<-subset(sc_3,sc_3$time %in% group3_times) #macroalgae
panelC_4<-subset(sc_3,sc_3$time %in% group4_times) #generalists
panelC_5<-subset(sc_3,sc_3$time %in% group5_times) #browsers
panelC_6<-subset(sc_3,sc_3$time %in% group6_times) #grazers



#Making the figures

pdf("Fig_7_v1.pdf",width=3.75, height=7)


par(mfrow=c(3,1),
    mar=c(4,5,2.5,2),
    family = "Times")

#quartz()
plot(panelA_2$time, panelA_2$Herbivores,
     pch=15,
     col = "blue",
     xlab="Time",
     ylab="Cover / Abundance",
     ylim=c(0,1),
     xlim=c(0,400),
     cex.lab=1.5,
     cex.axis=1.3,
     main = "Final Turf Cover High",
     cex.main=1.6)
points(panelA_1$time, panelA_1$Algae, col="lightgreen", pch=15,cex=1)
points(panelA_1$time, panelA_1$Coral, col="red", pch=15)
# points(group4_1$time, group4_1$Generalists, col="hotpink", pch=15,cex=0.75)
# points(group4_1$time, group4_1$Generalists, col="gray", pch=15,cex=0.75)
points(panelA_4$time, panelA_4$Generalists, col="deeppink2", pch=20,cex=1.2)
points(panelA_5$time, panelA_5$Browsers, col="purple",bg="purple", pch=20,cex=1.2)
points(panelA_6$time, panelA_6$Grazers, col="orange",bg="orange", pch=20,cex=1.2)
points(panelA_2$time, panelA_2$Turf, col="yellow",bg="yellow", pch=24,cex=0.75)
points(panelA_3$time, panelA_3$Macroalgae, col="darkgreen",bg="darkgreen", pch=25,cex=0.75)
legend(x=75,y=1.06,
       # x=75,y=1.04,
       c("Herbivores","Algae","Coral", "Generalists","Browsers","Grazers","Turf","Macroalgae"),
       pch=c(15,15,15,20,20,20,24,25),
       col=c("blue","lightgreen","red","deeppink2","purple","orange","yellow","darkgreen"),
       pt.bg=c("blue","lightgreen","red","deeppink2","purple","orange","yellow","darkgreen"),
       ncol=3,
       bty = "n",   ## remove box around legend
       cex=0.85,
       pt.cex = c(1,1,1,1.2,1.2,1.2,0.75,0.75))


plot(panelB_2$time, panelB_2$Herbivores,
     pch=15,
     col = "blue",
     xlab="Time",
     ylab="Cover / Abundance",
     ylim=c(0,1),
     xlim=c(0,400),
     cex.lab=1.5,
     cex.axis=1.3,
     main = "Final Macroalgal Cover High",
     cex.main=1.6)
points(panelB_1$time, panelB_1$Algae, col="lightgreen", pch=15,cex=1)
points(panelB_1$time, panelB_1$Coral, col="red", pch=15)
points(panelB_4$time, panelB_4$Generalists, col="deeppink2", pch=20,cex=1.2)
points(panelB_5$time, panelB_5$Browsers, col="purple",bg="purple", pch=20,cex=1.2)
points(panelB_6$time, panelB_6$Grazers, col="orange",bg="orange", pch=20,cex=1.2)
points(panelB_2$time, panelB_2$Turf, col="yellow",bg="yellow", pch=24,cex=0.75)
points(panelB_3$time, panelB_3$Macroalgae, col="darkgreen",bg="darkgreen", pch=25,cex=0.75)



plot(panelC_2$time, panelC_2$Herbivores,
     pch=15,
     col = "blue",
     xlab="Time",
     ylab="Cover / Abundance",
     ylim=c(0,1),
     xlim=c(0,400),
     cex.lab=1.5,
     cex.axis=1.3,
     main = "Final Coral Cover High",
     cex.main=1.6)
points(panelC_1$time, panelC_1$Algae, col="lightgreen", pch=15,cex=1)
points(panelC_1$time, panelC_1$Coral, col="red", pch=15)
points(panelC_4$time, panelC_4$Generalists, col="deeppink2", pch=20,cex=1.2)
points(panelC_5$time, panelC_5$Browsers, col="purple",bg="purple", pch=20,cex=1.2)
points(panelC_6$time, panelC_6$Grazers, col="orange",bg="orange", pch=20,cex=1.2)
points(panelC_2$time, panelC_2$Turf, col="yellow",bg="yellow", pch=24,cex=0.75)
points(panelC_3$time, panelC_3$Macroalgae, col="darkgreen",bg="darkgreen", pch=25,cex=0.75)


dev.off()

```






