---
title: "NEW_Basic_v_Exp_Model"
output: pdf_document
---

```{r setup, include=FALSE}

library(deSolve)
library(ggplot2)
library(reshape2)
library(viridis)
library(gridExtra)

```

## Basic Model

To add a new chunk of R code, do option+command+i
```{r Basic Model,echo=TRUE}

#Set initial conditions for state variables
H0<-0.9
C0<-0.75
A0<-0.1
S0 <- 1 - C0 - A0

state_vars<-c(HH=H0, CC=C0, AA=A0, SS=S0)

#generate a series of times at which you want the ODE solver to output population sizes
#tseq<-seq(0,100,by=0.1)
tseq<-seq(0,1000,by=0.1)

#Generate a vector of parameter values
pars<-c(bc<-0.3,
        ba<- 0.8,
        ic<-0.05,
        ia<-0.05,
        dc<-0.1,
        r<-1,
        g<-1,
        eta<-1,
        alpha<-0.5,
        sigma<-0.6,
        f<-0.1)

Basic_Model<-function(tseq,state_vars,pars){
  HH <- state_vars[1]
  CC <- state_vars[2]
  AA <- state_vars[3]
  SS <- 1 - CC - AA
  
  bc <- pars[1]
  ba <- pars[2]
  ic <- pars[3]
  ia <- pars[4]
  dc <- pars[5]
  r <- pars[6]
  g <- pars[7]
  eta <- pars[8]
  alpha <- pars[9]
  sigma <- pars[10]
  f <- pars[11]
  
  dC_dt <- (ic + bc*CC)*SS*(1-alpha*AA)- dc*CC
  dA_dt <-(ia + ba*AA)*SS - (g*HH*AA / (g*eta*AA+1))
  dH_dt <-r*HH*(1 - (HH / ((1-sigma) + sigma*CC))) - f*HH

  return(list(c(dH<- dH_dt,
                dC <- dC_dt,
                dA <- dA_dt)))
}

Basic_M_output<-lsoda(c(Herbivores=H0,Coral=C0,Algae=A0), tseq, Basic_Model, pars)
Basic_M_output=as.data.frame(Basic_M_output)
Basic_M_output$Space= 1 - Basic_M_output$Coral - Basic_M_output$Algae

#head(Basic_M_output)
#tail(Basic_M_output)


## Run the model again with a higher fishing pressure f = 0.5
pars[11]=0.5
Basic_M_output_2<-lsoda(c(Herbivores=H0,Coral=C0,Algae=A0), tseq, Basic_Model, pars)
Basic_M_output_2=as.data.frame(Basic_M_output_2)


## Run the model again with an even higher fishing pressure f = 0.9
pars[11]=0.9
Basic_M_output_3<-lsoda(c(Herbivores=H0,Coral=C0,Algae=A0), tseq, Basic_Model, pars)
Basic_M_output_3=as.data.frame(Basic_M_output_3)


```


```{r Phase 2 Model}
#These were the initial conditions for the basic model when I first ran that...
# H0<-0.9
# C0<-0.75
# M0<-0.1

### Old assumptions of initial conditions to make previous model equations collapse to basic model
# G0<-0.3
# R0<-0.3
# B0<-0.3
# C0<-0.75
# T0<-0.05
# M0<-0.05
# S0 <- 1 - T0 - C0 - M0


G0<-0.45
R0<-0
B0<-0.45
C0<-0.75
T0<-0.05
M0<-0.05
S0 <- 1 - T0 - C0 - M0

# H0<-0.6
# C0<-0.5
# M0<-0.2
# S0 <- 1 - C0 - M0

P2_state_vars<-c(GG=G0, RR=R0, BB=B0, CC=C0, TT=T0, MM=M0, SS=S0)

#generate a series of times at which you want the ODE solver to output population sizes
#P2_tseq<-seq(0,100,by=0.1)
P2_tseq<-seq(0,1000,by=0.1)

#Generate a vector of parameter values
P2_pars<-c(bc<-0.3,
           bt<-0.8,      #use the same value as bm from basic model
           bm<-0.8,      #use the same value as bm from basic model
           ic<-0.05,
           it<-0.025,    #need two of these, one for turf and one for macroalgae
           im<-0.025,    #need two of these, one for turf and one for macroalgae
           dc<-0.1,
           r<-1,
           # gt<-1,       #need two of these, one for turf and one for macroalgae
           # gm<-1,       #need two of these, one for turf and one for macroalgae
           gt<-2,       #need two of these, one for turf and one for macroalgae
           gm<-2,       #need two of these, one for turf and one for macroalgae
           etaT<-1,     #need two of these, one for turf and one for macroalgae
           etaM<-1,     #need two of these, one for turf and one for macroalgae
           alphaT<-0.5,
           alphaM<-0.5,
           sigma<-0.6,
           f<-0.1,
           gamma<-0)

P2_Model<-function(P2_tseq,P2_state_vars,P2_pars){
  GG <- P2_state_vars[1]
  RR <- P2_state_vars[2]
  BB <- P2_state_vars[3]
  CC <- P2_state_vars[4]
  TT <- P2_state_vars[5]
  MM <- P2_state_vars[6]
  SS <- 1 - CC - TT - MM
  
  bc <- P2_pars[1]
  bt <- P2_pars[2]
  bm <- P2_pars[3]
  ic <- P2_pars[4]
  it <- P2_pars[5]
  im <- P2_pars[6]
  dc <- P2_pars[7]
  r <- P2_pars[8]
  gt <- P2_pars[9]
  gm <- P2_pars[10]
  etaT <- P2_pars[11]
  etaM <- P2_pars[12]
  alphaT <- P2_pars[13]
  alphaM <- P2_pars[14]
  sigma <- P2_pars[15]
  f <- P2_pars[16]
  gamma <- P2_pars[17]
  
  dG_dt <-r*GG*(1 - ((GG+RR+BB) / ((1-sigma) + sigma*CC))) - f*GG
  dR_dt <-r*RR*(1 - ((GG+RR+BB) / ((1-sigma) + sigma*CC))) - f*RR
  dB_dt <-r*BB*(1 - ((GG+RR+BB) / ((1-sigma) + sigma*CC))) - f*BB
  dC_dt <- (ic + bc*CC)*SS*(1-(alphaT*TT+alphaM*MM)) - dc*CC
  dT_dt <- (it + bt*TT)*(SS) - (gamma*TT) - (((gt*GG*TT) / (gt*etaT*TT+1)) + ((gt*RR*TT)/(gt*etaT*TT+gm*etaM*MM+1)))
  dM_dt <- (im + bm*MM)*(SS) + (gamma*TT) - (((gm*BB*MM) / (gm*etaM*MM+1)) + ((gm*RR*MM)/(gt*etaT*TT+gm*etaM*MM+1)))


  return(list(c(dG <- dG_dt,
                dR <- dR_dt,
                dB <- dB_dt,
                dC <- dC_dt,
                dT <- dT_dt,
                dM <- dM_dt)))
}

P2_output<-lsoda(c(Grazers =G0, Generalists =R0, Browsers =B0,
                   Coral = C0,Turf = T0,Macroalgae=M0),
                 P2_tseq, P2_Model, P2_pars)
P2_output=as.data.frame(P2_output)


P2_output$Space= 1 - P2_output$Coral - P2_output$Turf - P2_output$Macroalgae
P2_output$Herbivores = P2_output$Grazers+P2_output$Generalists+P2_output$Browsers
P2_output$Algae = P2_output$Turf+P2_output$Macroalgae



# Compare expanded model output to basic model output...
Herbs<-(round(P2_output$Herbivores,digits=4) == round(Basic_M_output$Herbivores,digits=4))
Herb.Trues<-sum(Herbs==TRUE)
#Herb.Trues
Algals<-(round(P2_output$Algae,digits=4) == round(Basic_M_output$Algae,digits=4))
Algals.Trues<-sum(Algals==TRUE)
#Algals.Trues
Coral<-(round(P2_output$Coral,digits=4) == round(Basic_M_output$Coral,digits=4))
Coral.Trues<-sum(Coral==TRUE)
Coral.Trues



## Run the model again with a higher fishing pressure f = 0.5
P2_pars[16]=0.5
P2_output_2<-lsoda(c(Grazers =G0, Generalists =R0, Browsers =B0,
                   Coral = C0,Turf = T0,Macroalgae=M0),
                 P2_tseq, P2_Model, P2_pars)
P2_output_2=as.data.frame(P2_output_2)
P2_output_2$Space= 1 - P2_output_2$Coral - P2_output_2$Turf - P2_output_2$Macroalgae
P2_output_2$Herbivores = P2_output_2$Grazers+P2_output_2$Generalists+P2_output_2$Browsers
P2_output_2$Algae = P2_output_2$Turf+P2_output_2$Macroalgae
#tail(P2_output_2)


## Run the model again with an even higher fishing pressure f = 0.9
P2_pars[16]=0.9
P2_output_3<-lsoda(c(Grazers =G0, Generalists =R0, Browsers =B0,
                   Coral = C0,Turf = T0,Macroalgae=M0),
                 P2_tseq, P2_Model, P2_pars)
P2_output_3=as.data.frame(P2_output_3)
P2_output_3$Space= 1 - P2_output_3$Coral - P2_output_3$Turf - P2_output_3$Macroalgae
P2_output_3$Herbivores = P2_output_3$Grazers+P2_output_3$Generalists+P2_output_3$Browsers
P2_output_3$Algae = P2_output_3$Turf+P2_output_3$Macroalgae
#tail(P2_output_3)


```





## Basic Model Plots over Time for Different Fishing Pressures
## Manuscript Figure 1c - or maybe moved into supplement later!

```{r Plots vs Time, fig.width = 8, fig.height = 6, dpi=300}

## subset time points at which to actually plot output....

# basic_times<-seq(0,1000,by=20)    ## miss the details happening in the early time steps when I plot it out for the full 1000 time steps - but in supplement, maybe?
# basic_times<-seq(0,200,by=2)
basic_times<-seq(0,200,by=2)
reduced_Basic<-subset(Basic_M_output,Basic_M_output$time %in% basic_times)
reduced_Basic_2<-subset(Basic_M_output_2,Basic_M_output_2$time %in% basic_times)
reduced_Basic_3<-subset(Basic_M_output_3,Basic_M_output_3$time %in% basic_times)


# p2_times<-seq(1,1000,by=20)    ## miss the details happening in the early time steps when I plot it out for the full 1000 time steps - but in supplement, maybe?
# p2_times<-seq(1,200,by=2)
p2_times<-seq(1,200,by=4)
reduced_p2<-subset(P2_output,P2_output$time %in% p2_times)
reduced_p2_2<-subset(P2_output_2,P2_output_2$time %in% p2_times)
reduced_p2_3<-subset(P2_output_3,P2_output_3$time %in% p2_times)


#quartz()

#pdf("Basic_v_Expanded.pdf",width=4, height=10)
pdf("Paper_Fig_1_c_v2.3.pdf",width=3.75, height=7)


par(mfrow=c(3,1),
    mar=c(4,5,2.5,2),
    family = "Times")

plot(reduced_Basic$time, reduced_Basic$Herbivores,
     pch = 15,
     col = "blue",
     xlab="Time",
     ylab="Cover / Abundance",
     ylim=c(0,1),
     xlim=c(0,200),
     cex.lab=1.5,
     cex.axis=1.3,
     main = "Fishing Pressure = 0.1",
     cex.main=1.6)
points(reduced_Basic$time, reduced_Basic$Algae, col="darkgreen", pch=15)
points(reduced_Basic$time, reduced_Basic$Coral, col="red", pch=15)
points(reduced_p2$time, reduced_p2$Herbivores, col="lightblue", pch=17)
points(reduced_p2$time, reduced_p2$Coral, col="pink", pch=17)
points(reduced_p2$time, reduced_p2$Algae, col="lightgreen", pch=17)
legend(x=120,y=0.65,
       c("Basic Herbivores","Collapsed Herbivores","Basic Algae","Collapsed Algae","Basic Coral","Collapsed Coral"),
       pch=c(15,17,15,17,15,17),
       col=c("blue","lightblue","darkgreen","lightgreen","red","pink"),
       cex=0.85)


plot(reduced_Basic_2$time, reduced_Basic_2$Herbivores,
     pch = 22,
     col = "blue",
     bg = "blue",
     xlab="Time",
     ylab="Cover / Abundance",
     ylim=c(0,1),
     xlim=c(0,200),
     cex.lab=1.5,
     cex.axis=1.3,
     main = "Fishing Pressure = 0.5",
     cex.main=1.6)
points(reduced_Basic_2$time, reduced_Basic_2$Algae, col="darkgreen", pch=22, bg = "darkgreen")
points(reduced_Basic_2$time, reduced_Basic_2$Coral, col="red", pch=22, bg = "red")
points(reduced_p2_2$time, reduced_p2_2$Herbivores, col="lightblue", pch=24, bg = "lightblue")
points(reduced_p2_2$time, reduced_p2_2$Coral, col="pink", pch=24, bg = "pink")
points(reduced_p2_2$time, reduced_p2_2$Algae, col="lightgreen", pch=24, bg = "lightgreen")


plot(reduced_Basic_3$time, reduced_Basic_3$Herbivores,
     pch = 22,
     col = "blue",
     bg = "blue",
     xlab="Time",
     ylab="Cover / Abundance",
     ylim=c(0,1),
     xlim=c(0,200),
     cex.lab=1.5,
     cex.axis=1.3,
     main = "Fishing Pressure = 0.9",
     cex.main=1.6)
points(reduced_Basic_3$time, reduced_Basic_3$Algae, col="darkgreen", pch=22, bg = "darkgreen")
points(reduced_Basic_3$time, reduced_Basic_3$Coral, col="red", pch=22, bg = "red")
points(reduced_p2_3$time, reduced_p2_3$Herbivores, col="lightblue", pch=24, bg = "lightblue")
points(reduced_p2_3$time, reduced_p2_3$Coral, col="pink", pch=24, bg = "pink")
points(reduced_p2_3$time, reduced_p2_3$Algae, col="lightgreen", pch=24, bg = "lightgreen")

dev.off()


```


## Expanded Model Initial Conditions & Parameters

```{r}
#Generate a vector of parameter values
hh_pars<-c(bc<-0.3, bt<-0.8,bm<-0.5,      #expansion of current benthic cover
           ic<-0.05, it<-0.05, im<-0,     #import of propagules
           dc<-0.1,                       #coral mortality
           r<-1,                          #herbivore growth rate
#           gt<-1, gm<-0.5,                #algae mortality - used previously before changing our model equations
           gt<-2, gm<-1,                #algae mortality
           etaT<-0, etaM<-1,              #algae handling time
           alphaT<-0.25, alphaM<-0.5,     #competitive effect on coral
           sigma<-0.6,                    #relationship between coral & herbivores
           f<-0.5,                        #fishing pressure
           gamma<-0.1)                    #transition from turf to macroalgae


```



## Sept. 2021 - This is now Figure 1 Panel c (instead of d)

## Making Figure 1 Panel d - showing the expanded model (with estimated parameter values instead of parameter values that allow the model to collapse to the basic model) over time


```{r}
## What am I using for the initial conditions for the Expanded Model? - Using what I have in my Table S2 from the manuscript...

G0<-0.3
R0<-0.3
B0<-0.3
C0<-0.75
T0<-0.1
M0<-0.0
S0 <- 1 - T0 - C0 - M0


#set fishing pressure to 0.1 for initial run
hh_pars[16] = 0.1
Exp_output<-lsoda(c(Grazers =G0, Generalists =R0, Browsers =B0,
                   Coral = C0,Turf = T0,Macroalgae=M0),
                 P2_tseq, P2_Model, hh_pars)
Exp_output=as.data.frame(Exp_output)
Exp_output$Space= 1 - Exp_output$Coral - Exp_output$Turf - Exp_output$Macroalgae
Exp_output$Herbivores = Exp_output$Grazers+Exp_output$Generalists+Exp_output$Browsers
Exp_output$Algae = Exp_output$Turf+Exp_output$Macroalgae


## Run the model again with a higher fishing pressure f = 0.5
hh_pars[16]=0.5
Exp_output_2<-lsoda(c(Grazers =G0, Generalists =R0, Browsers =B0,
                   Coral = C0,Turf = T0,Macroalgae=M0),
                 P2_tseq, P2_Model, hh_pars)
Exp_output_2=as.data.frame(Exp_output_2)
Exp_output_2$Space= 1 - Exp_output_2$Coral - Exp_output_2$Turf - Exp_output_2$Macroalgae
Exp_output_2$Herbivores = Exp_output_2$Grazers+Exp_output_2$Generalists+Exp_output_2$Browsers
Exp_output_2$Algae = Exp_output_2$Turf+Exp_output_2$Macroalgae
#tail(Exp_output_2)


## Run the model again with an even higher fishing pressure f = 0.9
hh_pars[16]=0.9
Exp_output_3<-lsoda(c(Grazers =G0, Generalists =R0, Browsers =B0,
                   Coral = C0,Turf = T0,Macroalgae=M0),
                 P2_tseq, P2_Model, hh_pars)
Exp_output_3=as.data.frame(Exp_output_3)
Exp_output_3$Space= 1 - Exp_output_3$Coral - Exp_output_3$Turf - Exp_output_3$Macroalgae
Exp_output_3$Herbivores = Exp_output_3$Grazers+Exp_output_3$Generalists+Exp_output_3$Browsers
Exp_output_3$Algae = Exp_output_3$Turf+Exp_output_3$Macroalgae
#tail(Exp_output_3)


```


## Plotting figure of expanded model over time for 3 different fishing pressure values
## Alternative version of above figure with points instead of lines
## See next code chunk for UPDATED version of Figure 1C - November 2, 2021

```{r}
# Need to reduce the number of data points to plot so the points are actually visible
## subset time points at which to actually plot output....

group1_times<-seq(0,200,by=6)
#which state variables do I want in group 1?
# Herbivores, Algae, Coral, Generalists
group1_1<-subset(Exp_output,Exp_output$time %in% group1_times)
group1_2<-subset(Exp_output_2,Exp_output$time %in% group1_times)
group1_3<-subset(Exp_output_3,Exp_output$time %in% group1_times)

#which state variables do I want in group 2?
#Grazers, Turf
group2_times<-seq(3,200,by=6)
group2_1<-subset(Exp_output,Exp_output$time %in% group2_times)
group2_2<-subset(Exp_output_2,Exp_output$time %in% group2_times)
group2_3<-subset(Exp_output_3,Exp_output$time %in% group2_times)


#which state variables do I want in group 3?
#Browsers, Macroalgae
group3_times<-seq(1,200,by=6)
group3_1<-subset(Exp_output,Exp_output$time %in% group3_times)
group3_2<-subset(Exp_output_2,Exp_output$time %in% group3_times)
group3_3<-subset(Exp_output_3,Exp_output$time %in% group3_times)


#Different times for the 3 different types of herbivores
group4_times<-seq(0,200,by=9)
group4_1<-subset(Exp_output,Exp_output$time %in% group4_times)
group4_2<-subset(Exp_output_2,Exp_output$time %in% group4_times)
group4_3<-subset(Exp_output_3,Exp_output$time %in% group4_times)

group5_times<-seq(3,200,by=9)
group5_1<-subset(Exp_output,Exp_output$time %in% group5_times)
group5_2<-subset(Exp_output_2,Exp_output$time %in% group5_times)
group5_3<-subset(Exp_output_3,Exp_output$time %in% group5_times)

group6_times<-seq(6,200,by=9)
group6_1<-subset(Exp_output,Exp_output$time %in% group6_times)
group6_2<-subset(Exp_output_2,Exp_output$time %in% group6_times)
group6_3<-subset(Exp_output_3,Exp_output$time %in% group6_times)


#Making the figures - see next code chunk for UPDATED figure

# pdf("Paper_Fig_1_d_v3.pdf",width=3.75, height=7)
# pdf("Fig_1D_v1.pdf",width=3.75, height=7)
pdf("Fig_1D_v2.pdf",width=3.75, height=7)


par(mfrow=c(3,1),
    mar=c(4,5,2.5,2),
    family = "Times")

#quartz()
plot(group2_1$time, group2_1$Herbivores,
     pch=15,
     col = "blue",
     xlab="Time",
     ylab="Cover / Abundance",
     ylim=c(0,1),
     xlim=c(0,200),
     cex.lab=1.5,
     cex.axis=1.3,
     main = "Fishing Pressure = 0.1",
     cex.main=1.6)
points(group2_1$time, group2_1$Algae, col="lightgreen", pch=15,cex=0.75)
points(group1_1$time, group1_1$Coral, col="red", pch=15)
# points(group4_1$time, group4_1$Generalists, col="hotpink", pch=15,cex=0.75)
points(group4_1$time, group4_1$Generalists, col="gray", pch=15,cex=0.75)
points(group5_1$time, group5_1$Browsers, col="purple",bg="purple", pch=24,cex=0.75)
points(group6_1$time, group6_1$Grazers, col="orange",bg="orange", pch=25,cex=0.75)
points(group2_1$time, group2_1$Turf, col="yellow",bg="yellow", pch=24,cex=0.75)
points(group3_1$time, group3_1$Macroalgae, col="darkgreen",bg="darkgreen", pch=25,cex=0.75)
legend(x=20,y=0.65,
       c("Herbivores","Algae","Coral", "Generalists","Browsers","Grazers","Turf","Macroalgae"),
       pch=c(15,15,15,15,24,25,24,25),
       col=c("blue","lightgreen","red","gray","purple","orange","yellow","darkgreen"),
       pt.bg=c("blue","lightgreen","red","gray","purple","orange","yellow","darkgreen"),
       ncol=3,
       cex=0.85)


plot(group2_2$time, group2_2$Herbivores,
     pch=15,
     col = "blue",
     xlab="Time",
     ylab="Cover / Abundance",
     ylim=c(0,1),
     xlim=c(0,200),
     cex.lab=1.5,
     cex.axis=1.3,
     main = "Fishing Pressure = 0.5",
     cex.main=1.6)
points(group2_2$time, group2_2$Algae, col="lightgreen", pch=15,cex=0.75)
points(group1_2$time, group1_2$Coral, col="red", pch=15)
# points(group4_2$time, group4_2$Generalists, col="hotpink", pch=15,cex=0.75)
points(group4_2$time, group4_2$Generalists, col="gray", pch=15,cex=0.75)
points(group5_2$time, group5_2$Browsers, col="purple",bg="purple", pch=24,cex=0.75)
points(group6_2$time, group6_2$Grazers, col="orange",bg="orange", pch=25,cex=0.75)
points(group2_2$time, group2_2$Turf, col="yellow",bg="yellow", pch=24,cex=0.75)
points(group3_2$time, group3_2$Macroalgae, col="darkgreen",bg="darkgreen", pch=25,cex=0.75)



plot(group2_3$time, group2_3$Herbivores,
     pch=15,
     col = "blue",
     xlab="Time",
     ylab="Cover / Abundance",
     ylim=c(0,1),
     xlim=c(0,200),
     cex.lab=1.5,
     cex.axis=1.3,
     main = "Fishing Pressure = 0.9",
     cex.main=1.6)
points(group2_3$time, group2_3$Algae, col="lightgreen", pch=15,cex=0.75)
points(group1_3$time, group1_3$Coral, col="red", pch=15)
# points(group4_3$time, group4_3$Generalists, col="hotpink", pch=15,cex=0.75)
points(group4_3$time, group4_3$Generalists, col="gray", pch=15,cex=0.75)
points(group5_3$time, group5_3$Browsers, col="purple",bg="purple", pch=24,cex=0.75)
points(group6_3$time, group6_3$Grazers, col="orange",bg="orange", pch=25,cex=0.75)
points(group2_3$time, group2_3$Turf, col="yellow",bg="yellow", pch=24,cex=0.75)
points(group3_3$time, group3_3$Macroalgae, col="darkgreen",bg="darkgreen", pch=25,cex=0.75)


dev.off()

```


### November 2, 2021 - modifying new Panel C for Figure 1
## Increase the time range shown to 1000 time units instead of only 200, but will only plot first 400

```{r}
# Need to reduce the number of data points to plot so the points are actually visible
## subset time points at which to actually plot output....

# group1_times<-seq(0,200,by=6)
# group1_times<-seq(0,1000,by=30)
group1_times<-seq(0,1000,by=10)
#which state variables do I want in group 1?
# Herbivores, Algae, Coral, Generalists
group1_1<-subset(Exp_output,Exp_output$time %in% group1_times)
group1_2<-subset(Exp_output_2,Exp_output$time %in% group1_times)
group1_3<-subset(Exp_output_3,Exp_output$time %in% group1_times)

#which state variables do I want in group 2?
#Grazers, Turf
# group2_times<-seq(3,200,by=6)
# group2_times<-seq(15,1000,by=30)
group2_times<-seq(7,1000,by=10)
group2_1<-subset(Exp_output,Exp_output$time %in% group2_times)
group2_2<-subset(Exp_output_2,Exp_output$time %in% group2_times)
group2_3<-subset(Exp_output_3,Exp_output$time %in% group2_times)


#which state variables do I want in group 3?
#Browsers, Macroalgae
# group3_times<-seq(1,200,by=6)
# group3_times<-seq(5,1000,by=30)
group3_times<-seq(3,1000,by=10)
group3_1<-subset(Exp_output,Exp_output$time %in% group3_times)
group3_2<-subset(Exp_output_2,Exp_output$time %in% group3_times)
group3_3<-subset(Exp_output_3,Exp_output$time %in% group3_times)


#Different times for the 3 different types of herbivores
# group4_times<-seq(0,200,by=9)
# group4_times<-seq(0,1000,by=45)
group4_times<-seq(0,1000,by=22)
group4_1<-subset(Exp_output,Exp_output$time %in% group4_times)
group4_2<-subset(Exp_output_2,Exp_output$time %in% group4_times)
group4_3<-subset(Exp_output_3,Exp_output$time %in% group4_times)

# group5_times<-seq(3,200,by=9)
# group5_times<-seq(15,1000,by=45)
group5_times<-seq(7,1000,by=22)
group5_1<-subset(Exp_output,Exp_output$time %in% group5_times)
group5_2<-subset(Exp_output_2,Exp_output$time %in% group5_times)
group5_3<-subset(Exp_output_3,Exp_output$time %in% group5_times)

# group6_times<-seq(6,200,by=9)
# group6_times<-seq(30,1000,by=45)
group6_times<-seq(14,1000,by=22)
group6_1<-subset(Exp_output,Exp_output$time %in% group6_times)
group6_2<-subset(Exp_output_2,Exp_output$time %in% group6_times)
group6_3<-subset(Exp_output_3,Exp_output$time %in% group6_times)


## List of times from above for easier referencing and copying...
# group1_times<-seq(0,1000,by=10)
# group2_times<-seq(7,1000,by=10)
# group3_times<-seq(3,1000,by=10)
# group4_times<-seq(0,1000,by=22)
# group5_times<-seq(7,1000,by=22)
# group6_times<-seq(14,1000,by=22)



## Making the figure

# pdf("Fig_new1C_v1.pdf",width=3.75,height=7)
# pdf("Fig_new1C_v2.pdf",width=3.75,height=7)
# pdf("Fig_new1C_v3.pdf",width=3.75,height=7)
pdf("Fig_new1C_v4.pdf",width=3.75,height=7)


par(mfrow=c(3,1),
    mar=c(4,5,2.5,2),
    family = "Times")

#quartz()
plot(group2_1$time, group2_1$Herbivores,
     pch=15,
     col = "blue",
     xlab="Time",
     ylab="Cover / Abundance",
     ylim=c(0,1),
     xlim=c(0,400),
     cex.lab=1.5,
     cex.axis=1.3,
     main = "Fishing Pressure = 0.1",
     cex.main=1.6)
# points(group2_1$time, group2_1$Algae, col="lightgreen", pch=15,cex=0.75)
points(group2_1$time, group2_1$Algae, col="lightgreen", pch=15,cex=1)
points(group1_1$time, group1_1$Coral, col="red", pch=15)
# points(group4_1$time, group4_1$Generalists, col="hotpink", pch=15,cex=0.75)
# points(group4_1$time, group4_1$Generalists, col="gray", pch=20,cex=0.75)
points(group4_1$time, group4_1$Generalists, col="deeppink2", pch=20,cex=1.2)
points(group5_1$time, group5_1$Browsers, col="purple",bg="purple", pch=20,cex=1.2)
points(group6_1$time, group6_1$Grazers, col="orange",bg="orange", pch=20,cex=1.2)
points(group2_1$time, group2_1$Turf, col="yellow",bg="yellow", pch=24,cex=0.75)
points(group3_1$time, group3_1$Macroalgae, col="darkgreen",bg="darkgreen", pch=25,cex=0.75)
legend(x=75,y=1.06,
       # x=75,y=0.65,
       c("Herbivores","Algae","Coral", "Generalists","Browsers","Grazers","Turf","Macroalgae"),
       pch=c(15,15,15,20,20,20,24,25),
       col=c("blue","lightgreen","red","deeppink2","purple","orange","yellow","darkgreen"),
       pt.bg=c("blue","lightgreen","red","deeppink2","purple","orange","yellow","darkgreen"),
       ncol=3,
       cex=0.85,
       bty = "n",   ## remove box around legend
       pt.cex = c(1,1,1,1.2,1.2,1.2,0.75,0.75))


plot(group2_2$time, group2_2$Herbivores,
     pch=15,
     col = "blue",
     xlab="Time",
     ylab="Cover / Abundance",
     ylim=c(0,1),
     xlim=c(0,400),
     cex.lab=1.5,
     cex.axis=1.3,
     main = "Fishing Pressure = 0.5",
     cex.main=1.6)
# points(group2_2$time, group2_2$Algae, col="lightgreen", pch=15,cex=0.75)
points(group2_2$time, group2_2$Algae, col="lightgreen", pch=15,cex=1)
points(group1_2$time, group1_2$Coral, col="red", pch=15)
# points(group4_2$time, group4_2$Generalists, col="hotpink", pch=15,cex=0.75)
points(group4_2$time, group4_2$Generalists, col="deeppink2", pch=20,cex=1.2)
points(group5_2$time, group5_2$Browsers, col="purple",bg="purple", pch=20,cex=1.2)
points(group6_2$time, group6_2$Grazers, col="orange",bg="orange", pch=20,cex=1.2)
points(group2_2$time, group2_2$Turf, col="yellow",bg="yellow", pch=24,cex=0.75)
points(group3_2$time, group3_2$Macroalgae, col="darkgreen",bg="darkgreen", pch=25,cex=0.75)



plot(group2_3$time, group2_3$Herbivores,
     pch=15,
     col = "blue",
     xlab="Time",
     ylab="Cover / Abundance",
     ylim=c(0,1),
     xlim=c(0,400),
     cex.lab=1.5,
     cex.axis=1.3,
     main = "Fishing Pressure = 0.9",
     cex.main=1.6)
# points(group2_3$time, group2_3$Algae, col="lightgreen", pch=15,cex=0.75)
points(group2_3$time, group2_3$Algae, col="lightgreen", pch=15,cex=1)
points(group1_3$time, group1_3$Coral, col="red", pch=15)
# points(group4_3$time, group4_3$Generalists, col="hotpink", pch=15,cex=0.75)
points(group4_3$time, group4_3$Generalists, col="deeppink2", pch=20,cex=1.2)
points(group5_3$time, group5_3$Browsers, col="purple",bg="purple", pch=20,cex=1.2)
points(group6_3$time, group6_3$Grazers, col="orange",bg="orange", pch=20,cex=1.2)
points(group2_3$time, group2_3$Turf, col="yellow",bg="yellow", pch=24,cex=0.75)
points(group3_3$time, group3_3$Macroalgae, col="darkgreen",bg="darkgreen", pch=25,cex=0.75)


dev.off()

```







## September 20, 2021 - Making new Panel d for Figure 1
### Showing results over time, but only use fishing pressure = 0.5, and instead show different herbivore community scenarios

```{r}
# Set initial conditions

G0<-0.3
R0<-0.3
B0<-0.3
C0<-0.75
T0<-0.1
M0<-0.0
S0 <- 1 - T0 - C0 - M0


#have 'even' herbivore communities initially
#set fishing pressure to 0.5 for all runs
G0<-0.3
R0<-0.3
B0<-0.3
hh_pars[16] = 0.5
F1d_even<-lsoda(c(Grazers =G0, Generalists =R0, Browsers =B0,
                   Coral = C0,Turf = T0,Macroalgae=M0),
                 P2_tseq, P2_Model, hh_pars)
F1d_even=as.data.frame(F1d_even)
F1d_even$Space= 1 - F1d_even$Coral - F1d_even$Turf - F1d_even$Macroalgae
F1d_even$Herbivores = F1d_even$Grazers+F1d_even$Generalists+F1d_even$Browsers
F1d_even$Algae = F1d_even$Turf+F1d_even$Macroalgae


## Run the model again with same fishing pressure f = 0.5, but generalist-dominated herbivore community
G0<-0.15
R0<-0.6
B0<-0.15
hh_pars[16]=0.5
F1d_genD<-lsoda(c(Grazers =G0, Generalists =R0, Browsers =B0,
                   Coral = C0,Turf = T0,Macroalgae=M0),
                 P2_tseq, P2_Model, hh_pars)
F1d_genD=as.data.frame(F1d_genD)
F1d_genD$Space= 1 - F1d_genD$Coral - F1d_genD$Turf - F1d_genD$Macroalgae
F1d_genD$Herbivores = F1d_genD$Grazers+F1d_genD$Generalists+F1d_genD$Browsers
F1d_genD$Algae = F1d_genD$Turf+F1d_genD$Macroalgae
#tail(F1d_genD)


## Run the model again with same fishing pressure f = 0.5, but grazer-dominated herbivore community
G0<-0.6
R0<-0.15
B0<-0.15
hh_pars[16]=0.5
F1d_grazD<-lsoda(c(Grazers =G0, Generalists =R0, Browsers =B0,
                   Coral = C0,Turf = T0,Macroalgae=M0),
                 P2_tseq, P2_Model, hh_pars)
F1d_grazD=as.data.frame(F1d_grazD)
F1d_grazD$Space= 1 - F1d_grazD$Coral - F1d_grazD$Turf - F1d_grazD$Macroalgae
F1d_grazD$Herbivores = F1d_grazD$Grazers+F1d_grazD$Generalists+F1d_grazD$Browsers
F1d_grazD$Algae = F1d_grazD$Turf+F1d_grazD$Macroalgae
#tail(F1d_grazD)



## Run the model again with same fishing pressure f = 0.5, but browers-dominated herbivore community
G0<-0.15
R0<-0.15
B0<-0.6
hh_pars[16]=0.5
F1d_browsD<-lsoda(c(Grazers =G0, Generalists =R0, Browsers =B0,
                   Coral = C0,Turf = T0,Macroalgae=M0),
                 P2_tseq, P2_Model, hh_pars)
F1d_browsD=as.data.frame(F1d_browsD)
F1d_browsD$Space= 1 - F1d_browsD$Coral - F1d_browsD$Turf - F1d_browsD$Macroalgae
F1d_browsD$Herbivores = F1d_browsD$Grazers+F1d_browsD$Generalists+F1d_browsD$Browsers
F1d_browsD$Algae = F1d_browsD$Turf+F1d_browsD$Macroalgae
#tail(F1d_browsD)

```

## Now plotting the figures

```{r}
# Need to reduce the number of data points to plot so the points are actually visible
## subset time points at which to actually plot output....

## List of times from Figure 1C above, so they match between panels C and D

group1_times<-seq(0,1000,by=10)
group2_times<-seq(7,1000,by=10)
group3_times<-seq(3,1000,by=10)
group4_times<-seq(0,1000,by=22)
group5_times<-seq(7,1000,by=22)
group6_times<-seq(14,1000,by=22)


#group1_times<-seq(0,200,by=6)
# group1_times<-seq(0,1000,by=30)
#which state variables do I want in group 1?
# Herbivores, Algae, Coral, Generalists
group1_1<-subset(F1d_genD,F1d_genD$time %in% group1_times)
group1_2<-subset(F1d_grazD,F1d_genD$time %in% group1_times)
group1_3<-subset(F1d_browsD,F1d_genD$time %in% group1_times)

#which state variables do I want in group 2?
#Grazers, Turf
#group2_times<-seq(3,200,by=6)
# group2_times<-seq(15,1000,by=30)
group2_1<-subset(F1d_genD,F1d_genD$time %in% group2_times)
group2_2<-subset(F1d_grazD,F1d_genD$time %in% group2_times)
group2_3<-subset(F1d_browsD,F1d_genD$time %in% group2_times)


#which state variables do I want in group 3?
#Browsers, Macroalgae
#group3_times<-seq(1,200,by=6)
# group3_times<-seq(5,1000,by=30)
group3_1<-subset(F1d_genD,F1d_genD$time %in% group3_times)
group3_2<-subset(F1d_grazD,F1d_genD$time %in% group3_times)
group3_3<-subset(F1d_browsD,F1d_genD$time %in% group3_times)


#Different times for the 3 different types of herbivores
#group4_times<-seq(0,200,by=9)
# group4_times<-seq(0,1000,by=45)
group4_1<-subset(F1d_genD,F1d_genD$time %in% group4_times)
group4_2<-subset(F1d_grazD,F1d_genD$time %in% group4_times)
group4_3<-subset(F1d_browsD,F1d_genD$time %in% group4_times)

#group5_times<-seq(3,200,by=9)
# group5_times<-seq(15,1000,by=45)
group5_1<-subset(F1d_genD,F1d_genD$time %in% group5_times)
group5_2<-subset(F1d_grazD,F1d_genD$time %in% group5_times)
group5_3<-subset(F1d_browsD,F1d_genD$time %in% group5_times)

#group6_times<-seq(6,200,by=9)
# group6_times<-seq(30,1000,by=45)
group6_1<-subset(F1d_genD,F1d_genD$time %in% group6_times)
group6_2<-subset(F1d_grazD,F1d_genD$time %in% group6_times)
group6_3<-subset(F1d_browsD,F1d_genD$time %in% group6_times)


#Making the figures

pdf("Fig_1D_v4.pdf",width=3.75, height=7)


par(mfrow=c(3,1),
    mar=c(4,5,2.5,2),
    family = "Times")

#quartz()
plot(group2_1$time, group2_1$Herbivores,
     pch=15,
     col = "blue",
     xlab="Time",
     ylab="Cover / Abundance",
     ylim=c(0,1),
     xlim=c(0,400),
     cex.lab=1.5,
     cex.axis=1.3,
     main = "Generalist-dominated community",
     cex.main=1.6)
points(group2_1$time, group2_1$Algae, col="lightgreen", pch=15,cex=1)
points(group1_1$time, group1_1$Coral, col="red", pch=15)
# points(group4_1$time, group4_1$Generalists, col="hotpink", pch=15,cex=0.75)
# points(group4_1$time, group4_1$Generalists, col="gray", pch=15,cex=0.75)
points(group4_1$time, group4_1$Generalists, col="deeppink2", pch=20,cex=1.2)
points(group5_1$time, group5_1$Browsers, col="purple",bg="purple", pch=20,cex=1.2)
points(group6_1$time, group6_1$Grazers, col="orange",bg="orange", pch=20,cex=1.2)
points(group2_1$time, group2_1$Turf, col="yellow",bg="yellow", pch=24,cex=0.75)
points(group3_1$time, group3_1$Macroalgae, col="darkgreen",bg="darkgreen", pch=25,cex=0.75)
legend(x=75,y=1.06,
       # x=75,y=1.04,
       c("Herbivores","Algae","Coral", "Generalists","Browsers","Grazers","Turf","Macroalgae"),
       pch=c(15,15,15,20,20,20,24,25),
       col=c("blue","lightgreen","red","deeppink2","purple","orange","yellow","darkgreen"),
       pt.bg=c("blue","lightgreen","red","deeppink2","purple","orange","yellow","darkgreen"),
       ncol=3,
       bty = "n",   ## remove box around legend
       cex=0.85,
       pt.cex = c(1,1,1,1.2,1.2,1.2,0.75,0.75))


plot(group2_2$time, group2_2$Herbivores,
     pch=15,
     col = "blue",
     xlab="Time",
     ylab="Cover / Abundance",
     ylim=c(0,1),
     xlim=c(0,400),
     cex.lab=1.5,
     cex.axis=1.3,
     main = "Grazer-dominated community",
     cex.main=1.6)
points(group2_2$time, group2_2$Algae, col="lightgreen", pch=15,cex=1)
points(group1_2$time, group1_2$Coral, col="red", pch=15)
points(group4_2$time, group4_2$Generalists, col="deeppink2", pch=20,cex=1.2)
points(group5_2$time, group5_2$Browsers, col="purple",bg="purple", pch=20,cex=1.2)
points(group6_2$time, group6_2$Grazers, col="orange",bg="orange", pch=20,cex=1.2)
points(group2_2$time, group2_2$Turf, col="yellow",bg="yellow", pch=24,cex=0.75)
points(group3_2$time, group3_2$Macroalgae, col="darkgreen",bg="darkgreen", pch=25,cex=0.75)



plot(group2_3$time, group2_3$Herbivores,
     pch=15,
     col = "blue",
     xlab="Time",
     ylab="Cover / Abundance",
     ylim=c(0,1),
     xlim=c(0,400),
     cex.lab=1.5,
     cex.axis=1.3,
     main = "Browser-dominated community",
     cex.main=1.6)
points(group2_3$time, group2_3$Algae, col="lightgreen", pch=15,cex=1)
points(group1_3$time, group1_3$Coral, col="red", pch=15)
points(group4_3$time, group4_3$Generalists, col="deeppink2", pch=20,cex=1.2)
points(group5_3$time, group5_3$Browsers, col="purple",bg="purple", pch=20,cex=1.2)
points(group6_3$time, group6_3$Grazers, col="orange",bg="orange", pch=20,cex=1.2)
points(group2_3$time, group2_3$Turf, col="yellow",bg="yellow", pch=24,cex=0.75)
points(group3_3$time, group3_3$Macroalgae, col="darkgreen",bg="darkgreen", pch=25,cex=0.75)


dev.off()




### OLD CODE FOR MAKING PRIOR VERSIONS OF FIGURES

# pdf("Paper_Fig_1_d_v3.pdf",width=3.75, height=7)
# pdf("Fig_1D_v1.pdf",width=3.75, height=7)
# pdf("Fig_1D_v2.pdf",width=3.75, height=7)
# pdf("Fig_1D_v3.pdf",width=3.75, height=7)


# par(mfrow=c(3,1),
#     mar=c(4,5,2.5,2),
#     family = "Times")
# 
# #quartz()
# plot(group2_1$time, group2_1$Herbivores,
#      pch=15,
#      col = "blue",
#      xlab="Time",
#      ylab="Cover / Abundance",
#      ylim=c(0,1),
# #     xlim=c(0,200),
#      xlim=c(0,1000),
#      cex.lab=1.5,
#      cex.axis=1.3,
#      main = "Generalist-dominated community",
#      cex.main=1.6)
# points(group2_1$time, group2_1$Algae, col="lightgreen", pch=15,cex=0.75)
# points(group1_1$time, group1_1$Coral, col="red", pch=15)
# # points(group4_1$time, group4_1$Generalists, col="hotpink", pch=15,cex=0.75)
# # points(group4_1$time, group4_1$Generalists, col="gray", pch=15,cex=0.75)
# points(group4_1$time, group4_1$Generalists, col="turquoise", pch=15,cex=0.75)
# points(group5_1$time, group5_1$Browsers, col="purple",bg="purple", pch=24,cex=0.75)
# points(group6_1$time, group6_1$Grazers, col="orange",bg="orange", pch=25,cex=0.75)
# points(group2_1$time, group2_1$Turf, col="yellow",bg="yellow", pch=24,cex=0.75)
# points(group3_1$time, group3_1$Macroalgae, col="darkgreen",bg="darkgreen", pch=25,cex=0.75)
# legend(x=200,y=1.04,
#        c("Herbivores","Algae","Coral", "Generalists","Browsers","Grazers","Turf","Macroalgae"),
#        pch=c(15,15,15,15,24,25,24,25),
#        col=c("blue","lightgreen","red","turquoise","purple","orange","yellow","darkgreen"),
#        pt.bg=c("blue","lightgreen","red","turquoise","purple","orange","yellow","darkgreen"),
#        ncol=3,
#        bty = "n",   ## remove box around legend
#        cex=0.85)
# 
# 
# plot(group2_2$time, group2_2$Herbivores,
#      pch=15,
#      col = "blue",
#      xlab="Time",
#      ylab="Cover / Abundance",
#      ylim=c(0,1),
# #     xlim=c(0,200),
#      xlim=c(0,1000),
#      cex.lab=1.5,
#      cex.axis=1.3,
#      main = "Grazer-dominated community",
#      cex.main=1.6)
# points(group2_2$time, group2_2$Algae, col="lightgreen", pch=15,cex=0.75)
# points(group1_2$time, group1_2$Coral, col="red", pch=15)
# # points(group4_2$time, group4_2$Generalists, col="hotpink", pch=15,cex=0.75)
# points(group4_2$time, group4_2$Generalists, col="turquoise", pch=15,cex=0.75)
# points(group5_2$time, group5_2$Browsers, col="purple",bg="purple", pch=24,cex=0.75)
# points(group6_2$time, group6_2$Grazers, col="orange",bg="orange", pch=25,cex=0.75)
# points(group2_2$time, group2_2$Turf, col="yellow",bg="yellow", pch=24,cex=0.75)
# points(group3_2$time, group3_2$Macroalgae, col="darkgreen",bg="darkgreen", pch=25,cex=0.75)
# 
# 
# 
# plot(group2_3$time, group2_3$Herbivores,
#      pch=15,
#      col = "blue",
#      xlab="Time",
#      ylab="Cover / Abundance",
#      ylim=c(0,1),
# #     xlim=c(0,200),
#      xlim=c(0,1000),
#      cex.lab=1.5,
#      cex.axis=1.3,
#      main = "Browser-dominated community",
#      cex.main=1.6)
# points(group2_3$time, group2_3$Algae, col="lightgreen", pch=15,cex=0.75)
# points(group1_3$time, group1_3$Coral, col="red", pch=15)
# # points(group4_3$time, group4_3$Generalists, col="hotpink", pch=15,cex=0.75)
# points(group4_3$time, group4_3$Generalists, col="turquoise", pch=15,cex=0.75)
# points(group5_3$time, group5_3$Browsers, col="purple",bg="purple", pch=24,cex=0.75)
# points(group6_3$time, group6_3$Grazers, col="orange",bg="orange", pch=25,cex=0.75)
# points(group2_3$time, group2_3$Turf, col="yellow",bg="yellow", pch=24,cex=0.75)
# points(group3_3$time, group3_3$Macroalgae, col="darkgreen",bg="darkgreen", pch=25,cex=0.75)
# 
# 
# dev.off()

```






