---
title: "NEW_Question_1_Analayses_Higher_Macroalgae"
output: pdf_document
---

```{r setup, include=FALSE}

library(deSolve)
library(ggplot2)
library(reshape2)
library(viridis)
library(gridExtra)
library(gtable)
library(grid)
library(lemon)

```




## Initially did all of the analyses with Open Space starting at 0.75, which Deron said is unrealistic, so going to redo these analyses with open space starting at 0.15.
## Did one set of these analyses with Turf starting much higher.
## This set of analyses will be Macroalgae starting much higher, to try and get at recovery following a phase shift.


# Figure S3 RECOVERY for manuscript - panel figure of how different initial conditions of herbivorous fish affect final coral cover under different levels of fishing pressure - STARTING WITH LOW INITIAL CORAL COVER TO TALK ABOUT RECOVERY!!!

### Generalists set to 0
### Only keeping those combinations where total H is equal to or less than 0.9
```{r Figure S2 Recovery}

GG_values<-seq(0,0.9,by=0.025)
BB_values<-seq(0,0.9,by=0.025)

f_values<-seq(0,0.7,by=0.1)    ## this is what is different from the main text figure - showing additional fishing pressure levels

qq_initials_0<-expand.grid(GG_values,BB_values,f_values)
qq_initials_0$RR_values<-rep(0, length(qq_initials_0[,1]))
final_qq_0<-subset(qq_initials_0,rowSums(qq_initials_0[,c(1,2,4)])<=0.9)
colnames(final_qq_0)<-c("Grazers","Browsers","Fishing_Pressure","Generalists")


## Currently using hh_pars in lsoda below!!!!


for(i in 1:length(final_qq_0$Grazers)){
  G0<-final_qq_0$Grazers[i]
  B0<-final_qq_0$Browsers[i]
  R0<-final_qq_0$Generalists[i]
#  C0<-0.35
  C0<-0.15
  # M0<-0.0
  M0<-0.6
  T0<-0.1
  # T0<-0.6
  S0<-1-C0-M0-T0
  hh_pars[16]<-final_qq_0$Fishing_Pressure[i]   #set the fishing pressure
  zz_output<-lsoda(c(Grazers =G0, Generalists =R0, Browsers =B0,
                   Coral = C0,Turf = T0,Macroalgae=M0),
                 P2_tseq, P2_Model, hh_pars)
  zz_output_new<-as.data.frame(zz_output)
  final_qq_0$Final_Coral[i]<-tail(zz_output_new$Coral,1)
  final_qq_0$Final_Turf[i]<-tail(zz_output_new$Turf,1)
  final_qq_0$Final_Macroalgae[i]<-tail(zz_output_new$Macroalgae,1)
  final_qq_0$Final_Grazers[i]<-tail(zz_output_new$Grazers,1)
  final_qq_0$Final_Browsers[i]<-tail(zz_output_new$Browsers,1)
  final_qq_0$Final_Generalists[i]<-tail(zz_output_new$Generalists,1)
}

```

## Figure S3 RECOVERY continuted

### Generalists set to 0.2
```{r Figure S3 High Macroalgae Generalists set to 0.2}
GG_values<-seq(0,0.9,by=0.025)
BB_values<-seq(0,0.9,by=0.025)

f_values<-seq(0,0.7,by=0.1)  ## this is what is different from the main text figure - showing additional fishing pressure levels

qq_initials_2<-expand.grid(GG_values,BB_values,f_values)
qq_initials_2$RR_values<-rep(0.2, length(qq_initials_2[,1]))
final_qq_2<-subset(qq_initials_2,rowSums(qq_initials_2[,c(1,2,4)])<=0.9)
colnames(final_qq_2)<-c("Grazers","Browsers","Fishing_Pressure","Generalists")


## Currently using hh_pars in lsoda below!!!!

for(i in 1:length(final_qq_2$Grazers)){
  G0<-final_qq_2$Grazers[i]
  B0<-final_qq_2$Browsers[i]
  R0<-final_qq_2$Generalists[i]
  # C0<-0.35
  C0<-0.15
  # M0<-0.0
  M0<-0.6
  T0<-0.1
  # T0<-0.6
  S0<-1-C0-M0-T0
  hh_pars[16]<-final_qq_2$Fishing_Pressure[i]   #set the fishing pressure
  zz_output<-lsoda(c(Grazers =G0, Generalists =R0, Browsers =B0,
                   Coral = C0,Turf = T0,Macroalgae=M0),
                 P2_tseq, P2_Model, hh_pars)
  zz_output_new<-as.data.frame(zz_output)
  final_qq_2$Final_Coral[i]<-tail(zz_output_new$Coral,1)
  final_qq_2$Final_Turf[i]<-tail(zz_output_new$Turf,1)
  final_qq_2$Final_Macroalgae[i]<-tail(zz_output_new$Macroalgae,1)
  final_qq_2$Final_Grazers[i]<-tail(zz_output_new$Grazers,1)
  final_qq_2$Final_Browsers[i]<-tail(zz_output_new$Browsers,1)
  final_qq_2$Final_Generalists[i]<-tail(zz_output_new$Generalists,1)
}
```

## Figure S3 RECOVERY continuted

### Generalists set to 0.4
```{r Figure S3 High Macroalgae Generalists set to 0.4}
GG_values<-seq(0,0.9,by=0.025)
BB_values<-seq(0,0.9,by=0.025)

f_values<-seq(0,0.7,by=0.1)  ## this is what is different from the main text figure - showing addition fishing pressure levels

qq_initials_4<-expand.grid(GG_values,BB_values,f_values)
qq_initials_4$RR_values<-rep(0.4, length(qq_initials_4[,1]))
final_qq_4<-subset(qq_initials_4,rowSums(qq_initials_4[,c(1,2,4)])<=0.9)
colnames(final_qq_4)<-c("Grazers","Browsers","Fishing_Pressure","Generalists")


## Currently using hh_pars in lsoda below!!!!

for(i in 1:length(final_qq_4$Grazers)){
  G0<-final_qq_4$Grazers[i]
  B0<-final_qq_4$Browsers[i]
  R0<-final_qq_4$Generalists[i]
  # C0<-0.35
  C0<-0.15
  # M0<-0.0
  M0<-0.6
  T0<-0.1
  # T0<-0.6
  S0<-1-C0-M0-T0
  hh_pars[16]<-final_qq_4$Fishing_Pressure[i]   #set the fishing pressure
  zz_output<-lsoda(c(Grazers =G0, Generalists =R0, Browsers =B0,
                   Coral = C0,Turf = T0,Macroalgae=M0),
                 P2_tseq, P2_Model, hh_pars)
  zz_output_new<-as.data.frame(zz_output)
  final_qq_4$Final_Coral[i]<-tail(zz_output_new$Coral,1)
  final_qq_4$Final_Turf[i]<-tail(zz_output_new$Turf,1)
  final_qq_4$Final_Macroalgae[i]<-tail(zz_output_new$Macroalgae,1)
  final_qq_4$Final_Grazers[i]<-tail(zz_output_new$Grazers,1)
  final_qq_4$Final_Browsers[i]<-tail(zz_output_new$Browsers,1)
  final_qq_4$Final_Generalists[i]<-tail(zz_output_new$Generalists,1)
}
```

## Figure S3 RECOVERY continuted - actually making the figure here!

### Plotting output
```{r}

# Row bind the various data frames in order to plot by them
final_qq_0$Id="Generalists = 0"
final_qq_2$Id="Generalists = 0.2"
final_qq_4$Id="Generalists = 0.4"
qqall=rbind(final_qq_0, final_qq_2, final_qq_4)

#Getting names for Fishing Pressure so can plot them....
qqall$Fishing_ID = qqall$Fishing_Pressure
qqall$Fishing_ID <- as.factor(qqall$Fishing_ID)
levels(qqall$Fishing_ID)
levels(qqall$Fishing_ID)[levels(qqall$Fishing_ID)=="0"]<-"Fishing\nPressure\n= 0"
levels(qqall$Fishing_ID)[levels(qqall$Fishing_ID)=="0.1"]<-"Fishing\nPressure\n= 0.1"
levels(qqall$Fishing_ID)[levels(qqall$Fishing_ID)=="0.2"]<-"Fishing\nPressure\n= 0.2"
levels(qqall$Fishing_ID)[levels(qqall$Fishing_ID)=="0.3"]<-"Fishing\nPressure\n= 0.3"
levels(qqall$Fishing_ID)[levels(qqall$Fishing_ID)=="0.4"]<-"Fishing\nPressure\n= 0.4"
levels(qqall$Fishing_ID)[levels(qqall$Fishing_ID)=="0.5"]<-"Fishing\nPressure\n= 0.5"
levels(qqall$Fishing_ID)[levels(qqall$Fishing_ID)=="0.6"]<-"Fishing\nPressure\n= 0.6"
levels(qqall$Fishing_ID)[levels(qqall$Fishing_ID)=="0.7"]<-"Fishing\nPressure\n= 0.7"
levels(qqall$Fishing_ID)


## library(lemon)


# pdf("Paper_Fig_S3_v2_abundance.pdf",width=6, height=12)
# pdf("Paper_Fig_S3_v3_C0.15.pdf",width=6, height=12)
# pdf("Paper_Fig_S3_v4_T0.6.pdf",width=6, height=12)
pdf("Paper_Fig_S3_v5_M0.6.pdf",width=6, height=12)

#quartz()
## Making this plot with facet_rep_grid instead of facet_wrap so can better label the rows and columns
ggplot(data=qqall, aes(Grazers, Browsers)) +
      geom_tile(aes(fill = Final_Coral)) +
      theme_classic(base_size=10,base_family="Times") +
      theme(axis.title=element_text(size=11,face="bold")) + 
      scale_x_continuous("Grazer Abundance",breaks = c(0,0.3,0.6,0.9),
                         labels = c(0,0.3,0.6,0.9),limits = c(0,0.9)) +
      scale_y_continuous("Browser Abundance",breaks = c(0,0.3,0.6,0.9),
                         labels = c(0,0.3,0.6,0.9),limits = c(0,0.9)) +
      labs(fill = "Final\nCoral\nCover") +
#      ggtitle(paste("Fishing Pressure = ",f_values[i])) + 
      scale_fill_viridis(option = "viridis",limits=c(0,0.8)) +
      scale_colour_viridis(option = "viridis",limits=c(0,0.8)) +
  facet_rep_grid(Fishing_ID~Id) +
  coord_capped_cart(bottom='both', left='both') +
  theme(strip.text.x = element_text(size = 11)) + 
  theme(strip.text.y = element_text(size = 11,angle = 0))

dev.off()


```



### Plotting a subset of the above scenarios for the MAIN TEXT FIGURE - Figure 2, which is showing the recovery following a disturbance
## Figure 2 for main text

```{r}

## Need to subset the qqall data frame for just fishing pressures of 0, 0.3, and 0.6

qqall_0f<-subset(qqall,Fishing_Pressure == 0)
qqall_0.3f<-subset(qqall,Fishing_Pressure == "0.3")
qqall_0.5f<-subset(qqall,Fishing_Pressure == "0.5")
# qqall_0.6f<-subset(qqall,Fishing_Pressure == "0.6")
# 
# qqall_small=rbind(qqall_0f, qqall_0.3f, qqall_0.6f)
qqall_small=rbind(qqall_0f, qqall_0.3f, qqall_0.5f)

#Getting names for Fishing Pressure so can plot them....
qqall_small$Fishing_ID <- as.factor(qqall_small$Fishing_ID)
qqall_small$Id <- as.factor(qqall_small$Id)


# levels(qqall_small$Fishing_ID)
# levels(qqall_small$Fishing_ID)[levels(qqall_small$Fishing_ID)=="0"]<-"Fishing\nPressure\n= 0"
# levels(qqall_small$Fishing_ID)[levels(qqall_small$Fishing_ID)=="0.3"]<-"Fishing\nPressure\n= 0.3"
# levels(qqall_small$Fishing_ID)[levels(qqall_small$Fishing_ID)=="0.6"]<-"Fishing\nPressure\n= 0.6"
# levels(qqall_small$Fishing_ID)


# pdf("Fig_2_NEW_abundance.pdf",width=7, height=5.7)
# pdf("Fig_2_NEW_abundance_v2.pdf",width=7, height=5.7)
# pdf("Fig_2_NEW_abundance_v3_T0.6.pdf",width=7, height=5.7)
pdf("Fig_2_NEW_abundance_v4_M0.6.pdf",width=7, height=5.7)

#quartz()
## Making this plot with facet_rep_grid instead of facet_wrap so can better label the rows and columns
ggplot(data=qqall_small, aes(Grazers, Browsers)) +
      geom_tile(aes(fill = Final_Coral)) +
      theme_classic(base_size=10,base_family="Times") +
      theme(axis.title=element_text(size=11,face="bold")) + 
      scale_x_continuous("Grazer Abundance",breaks = c(0,0.3,0.6,0.9),
                         labels = c(0,0.3,0.6,0.9),limits = c(0,0.9)) +
      scale_y_continuous("Browser Abundance",breaks = c(0,0.3,0.6,0.9),
                         labels = c(0,0.3,0.6,0.9),limits = c(0,0.9)) +
      labs(fill = "Final\nCoral\nCover") +
#      ggtitle(paste("Fishing Pressure = ",f_values[i])) + 
      scale_fill_viridis(option = "viridis",limits=c(0,0.8)) +
      scale_colour_viridis(option = "viridis",limits=c(0,0.8)) +
  facet_rep_grid(Fishing_ID~Id) +
  coord_capped_cart(bottom='both', left='both') +
  theme(strip.text.x = element_text(size = 11)) + 
  theme(strip.text.y = element_text(size = 11,angle = 0))

dev.off()


```




